### 2016-05-23 ms.tex
Added beginning of paper

\documentclass[aps,pre,twocolumn,letterpaper,floatfix,showpacs]{revtex4}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{afterpage}
\usepackage[hidelinks]{hyperref} 
\usepackage{epstopdf}
\begin{document}
\title{Atomify - a live LAMMPS visualizer}
%\author{A. Hafreager, S-A. Dragly, A. Malthe-S\oe renssen$^1$}
\email{anders.hafreager@fys.uio.no}
\author{Svenn-Arne Dragly $^{1}$} 
\author{Anders Malthe-S\o renssen $^1$}
\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract} 
Atomify is a new tool simplifying the workflow when working with LAMMPS. It combines script editing, running simulations and visualizing into one single application by running an instance of a LAMMPS object with direct access to the simulation data in memory. Live plotting of computes in LAMMPS can easily be shown by an easy-to-use GUI. High end hardware is able to run Atomify with live simulations of millions of atoms with a modern, high quality rendering technique. Atomify supports accelerated simulations with OpenMP, GPU and Xeon Phi. The program is built with Qt and is distributed as open-source software under the GPL license. 
\end{abstract}

\maketitle

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Molecular dynamics has become a standard technique for simulating atoms in a broad range of fields. It is used to understand how liquids, solids and gases behave in problems relevant for physics, chemistry and biology.

\section{Installation}
The installation of atomify can be done in many ways. The easiest ones are by using the App Store for your operating system (Ubuntu and Mac OSX currently supported). If you want to download and compile the software yourself, you will need Qt Creator (supporting Qt 5.7).
\subsection{Mac App Store}
Atomify is available as free software in the Mac App Store. 
\subsection{Homebrew on Mac}
brew install atomify

\subsection{Ubuntu}
sudo apt-get install atomify

\section{Application}
Atomify is a rather small code built on Qt. All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++. Simply put, Atomify runs an instance of a LAMMPS object enabling the user to visualize the current state of LAMMPS and interact with LAMMPS while the simulation is running.

\subsection{Communicating with LAMMPS}

\subsection{Live plotting}

\subsection{Rendering techniques}
Simulations of atoms are often visualized as spheres and cylinders. The spheres represent the atoms while the cylinders represent the bonds between the atoms. This way the molecular structure is much easier to see and understand. In popular visualization tools like VMD, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest. The problem with this rendering technique is that each sphere needs many triangles in order to look spherical. This significantly reduces the rendering performance. A common technique to overcome this problem is to use billboards. Billboards are planes made up by two triangles with surface normal parallel to the vector pointing towards the camera. By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic.

\subsubsection*{Sphere billboards}
Each sphere is visualized as two triangles making up a square large enough to cover all pixels the sphere needs.

\subsubsection*{Cylinder billboard}

\section{Conclusion}
We have

\subsection{Future work}
All parts of Atomify can easily be ported to the web using WebGL and Emscripten.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}

%\begin{thebibliography}{9}

%\bibitem[Groeneboom2014]{groeneboom2014} Groeneboom, N.~E., \& Dahle, H.\ 2014, \apj, 783, 138

%\end{thebibliography}

\end{document}

### 2016-05-23 ms.tex
Added pipeline

@@
 
+\subsubsection*{Pipeline}
+When rendering one often wants to modify the data from LAMMPS before it is visualized.
+Examples are periodic images of the simulation, slicing and coloring.
+We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
+
 \subsubsection*{Sphere billboards}

### 2016-10-10 ms.tex
Wrote better abstract and some introduction

@@
 \title{Atomify - a live LAMMPS visualizer}
-%\author{A. Hafreager, S-A. Dragly, A. Malthe-S\oe renssen$^1$}
-\email{anders.hafreager@fys.uio.no}
-\author{Svenn-Arne Dragly $^{1}$} 
-\author{Anders Malthe-S\o renssen $^1$}
+\author{Anders Hafreager$^1$}
+\author{Svenn-Arne Dragly$^{1}$} 
+\author{Anders Malthe-S\o renssen$^1$}
 \affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
@@
 \begin{abstract} 
-Atomify is a new tool simplifying the workflow when working with LAMMPS.
-It combines script editing, running simulations and visualizing into one single application by running an instance of a LAMMPS object with direct access to the simulation data in memory.
-Live plotting of computes in LAMMPS can easily be shown by an easy-to-use GUI.
-High end hardware is able to run Atomify with live simulations of millions of atoms with a modern, high quality rendering technique.
-Atomify supports accelerated simulations with OpenMP, GPU and Xeon Phi.
-The program is built with Qt and is distributed as open-source software under the GPL license.
+The typical workflow when developing LAMMPS scripts includes working with several programs.
+A text editor is needed to modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
+If physical quantities are computed, the data is often plotted with MATLAB or Python.
+This is a tedious process, especially for teaching purposes and for people who are new to LAMMPS.
+We here introduce Atomify; a high performance live visualizer for LAMMPS simulations, with stunning graphics able to simulate and render more than 250000 atoms with excellent frame rate on modern hardware.
+Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and computes, and an easy-to-use code editor in one single program.
+Direct access to the powerful machinery already built into LAMMPS allows easy access to advanced physical quantities.
+Atomify is open source software (GPL) written in C++, built on top of Qt.
 \end{abstract}
@@
 \section{Introduction}
-Molecular dynamics has become a standard technique for simulating atoms in a broad range of fields.
-It is used to understand how liquids, solids and gases behave in problems relevant for physics, chemistry and biology.
+Molecular dynamics has become a standard technique for simulating atoms and molecules in a broad range of fields.
+Over the years, increasingly sophisticated methods have been developed.
+With the large number of force fields, advanced techniques and GPU acceleration, implementing a good molecular dynamics program from scratch a challenging task.
+While many people at some point write their own code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}.
+Both of these codes has been developed for more than two decades and contains more than one million lines of code each.
 
-\section{Installation}
-The installation of atomify can be done in many ways.
-The easiest ones are by using the App Store for your operating system (Ubuntu and Mac OSX currently supported).
-If you want to download and compile the software yourself, you will need Qt Creator (supporting Qt 5.7).
-\subsection{Mac App Store}
-Atomify is available as free software in the Mac App Store. 
-\subsection{Homebrew on Mac}
-brew install atomify
+When
 
-\subsection{Ubuntu}
-sudo apt-get install atomify
+\section{Features}
 
-\section{Application}
+\section{Implementation}
 Atomify is a rather small code built on Qt.
@@
 
+\subsection{Data pipeline}
+When rendering one often wants to modify the data from LAMMPS before it is visualized.
+Examples are periodic images of the simulation, slicing and coloring.
+We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
+
 \subsection{Rendering techniques}
-Simulations of atoms are often visualized as spheres and cylinders.
+Simulations of atoms are often visualized using spheres and cylinders.
 The spheres represent the atoms while the cylinders represent the bonds between the atoms.
-This way the molecular structure is much easier to see and understand.
-In popular visualization tools like VMD, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest.
+This way the molecular structure is easy to understand.
+In many visualization tools, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest.
 The problem with this rendering technique is that each sphere needs many triangles in order to look spherical.
@@
 
-\subsubsection*{Pipeline}
-When rendering one often wants to modify the data from LAMMPS before it is visualized.
-Examples are periodic images of the simulation, slicing and coloring.
-We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
-
 \subsubsection*{Sphere billboards}
@@
 \subsubsection*{Cylinder billboard}
+
+\section{Case study}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{bibliography}
-
-%\begin{thebibliography}{9}
-
-%\bibitem[Groeneboom2014]{groeneboom2014} Groeneboom, N.~E., \& Dahle, H.\ 2014, \apj, 783, 138
-
-%\end{thebibliography}
+\bibliographystyle{plain}
+\bibliography{Remote}
 

### 2016-10-10 ms.tex
Wrote more introduction

@@
-\documentclass[aps,pre,twocolumn,letterpaper,floatfix,showpacs]{revtex4}
+\documentclass[aps,pre,twocolumn,letterpaper,floatfix]{revtex4}
 \usepackage{graphicx} 
@@
 
-When
+The work in this paper is focused on LAMMPS.
+Although the software is well-documented and enables the user to perform advanced simulations, it can be a demanding job to learn how to use it well.
+A LAMMPS simulation is defined by a series of commands which are executed one by one.
+Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
+These can in turn be saved to file for plotting and further analysis.
+Particle trajectories can be saved to a file and visualized by tools such as VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
+The lack of an intuitive GUI and visualization \footnote{which are listed in the non-features list on the web page: \url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat complicated.
+
+Atomify solves this problem by combining the script editing, simulating and visualization into one single application.
+It uses LAMMPS as a library and executes commands one by one.
+A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting.
 
@@
 \subsection{Future work}
+Atomify is far from finished. 
+A web version of Atomify is in development. 
 All parts of Atomify can easily be ported to the web using WebGL and Emscripten.

### 2016-10-10 ms.tex
Future work notes

@@
 A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting.
+The visualization is done using raytracing on billboards allowing rendering of millions of atoms with good framerate.
 
 \section{Features}
+
+\subsection{Script editor}
+\subsection{Visualization}
+\subsection{Live plotting}
 
@@
 \subsection{Future work}
-Atomify is far from finished. 
-A web version of Atomify is in development. 
-All parts of Atomify can easily be ported to the web using WebGL and Emscripten.
+Atomify is far from finished.\\
+A web version of Atomify is in development using WebGL and Emscripten. \\
+Geometry shaders \\
+Improved script editor with auto completion \\
+Moltemplate interface \\
 

### 2017-02-04 ms.tex
Wrote more

@@
 A text editor is needed to modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
-If physical quantities are computed, the data is often plotted with MATLAB or Python.
+If physical quantities are computed, the data is often plotted with MATLAB or Python, where additional scripts must be used.
 This is a tedious process, especially for teaching purposes and for people who are new to LAMMPS.
@@
 \section{Introduction}
-Molecular dynamics has become a standard technique for simulating atoms and molecules in a broad range of fields.
+Molecular dynamics (MD) has become a standard technique for simulating atoms and molecules in a broad range of fields.
 Over the years, increasingly sophisticated methods have been developed.
 With the large number of force fields, advanced techniques and GPU acceleration, implementing a good molecular dynamics program from scratch a challenging task.
-While many people at some point write their own code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}.
-Both of these codes has been developed for more than two decades and contains more than one million lines of code each.
+While many people at some point write their own MD code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}.
+Both of these codes have been developed for more than two decades and contains more than one million lines of code each.
 
@@
 Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
-These can in turn be saved to file for plotting and further analysis.
+A time evolution of these quantities can in turn be saved to file for plotting and further analysis.
 Particle trajectories can be saved to a file and visualized by tools such as VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
@@
 
-Atomify solves this problem by combining the script editing, simulating and visualization into one single application.
-It uses LAMMPS as a library and executes commands one by one.
-A synchronization step copies the relevant information from LAMMPS to the GPU for visualization and data plotting.
+Atomify solves this problem by combining the script editing, simulating, visualizing and analyzing into one single application.
+It uses LAMMPS as a library and synchronizes after each timestep, copying the relevant information from LAMMPS to the GPU for visualization and data plotting.
 The visualization is done using raytracing on billboards allowing rendering of millions of atoms with good framerate.
@@
 \section{Features}
+Atomify comes with many useful features in addition to the 
+\subsection{Script editor}
+The script editor is minimalistic with syntax highlighting for the LAMMPS scripting language and line numbers.
+It supports multiple open files and remembers which files you have open across working sessions.
+A simple Ctrl+R will restart the simulation with any changes you might have done.
+\subsection{Visualization}
 
-\subsection{Script editor}
-\subsection{Visualization}
 \subsection{Live plotting}
 
+\subsection{Property coloring}
+
 \section{Implementation}
-Atomify is a rather small code built on Qt.
+Atomify is built upon Qt.
 All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++.
@@
 \subsection{Communicating with LAMMPS}
+LAMMPS can be compiled as a library with most of its contents being accessable through either the library interface or public variables in all classes.
 
@@
 
-\subsection{Rendering techniques}
-Simulations of atoms are often visualized using spheres and cylinders.
+\section{Rendering techniques}
+Simulations of atoms are often visualized using spheres as atoms and cylinders.
 The spheres represent the atoms while the cylinders represent the bonds between the atoms.
-This way the molecular structure is easy to understand.
+This way, the molecular structure is easy to understand and interpret.
 In many visualization tools, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest.
-The problem with this rendering technique is that each sphere needs many triangles in order to look spherical.
+One problem with this rendering technique is that each sphere needs many, often hundreds, triangles in order to look spherical.
 This significantly reduces the rendering performance.
 A common technique to overcome this problem is to use billboards.
-Billboards are planes made up by two triangles with surface normal parallel to the vector pointing towards the camera.
-By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic.
+Billboards are planes, made up by two or four triangles\footnote{The spheres are using two triangles, whereas the cylinders use four.} with surface normals parallel to the vector pointing towards the camera.
+By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic, see Figure \ref{fig:final_billboards}.
 
-\subsubsection*{Sphere billboards}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Billboards can produce pixel perfect rendering of molecules. Here we see a water molecule being rendererd with two light sources showing specular reflection and diffuse light effects.}
+	\label{fig:final_billboards}
+\end{figure}
+
+\subsection{Sphere billboards}
 Each sphere is visualized as two triangles making up a square large enough to cover all pixels the sphere needs.
+To reduce the CPU workload, all 4 corner vertices of the square are placed at the exact position of the sphere.
+The radius and a vertex id is specified, so that the vertex shader can move the 4 vertices so that the plane is orthogonal to the view vector and is larger than the cross sectional area of the sphere of interest.
+This is illustrated in figure \ref{fig:billboards}.
 
-\subsubsection*{Cylinder billboard}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{spherebillboards.png}
+	\caption{Illustration of billboards.
+The circles are shown in the figure to show our target rendering.
+a) all 4 vertices are at the center of the sphere.
+b) the vertex shader moves each vertex so that the plane covers a larger cross sectional area than the sphere.
+c) the orientation of the plane is such that the normal vector of the plane is parallel to the view vector.
+}
+	\label{fig:billboards}
+\end{figure}
+
+\subsection{Cylinder billboards}
+The cylinders are a bit more difficult because of two reasons. 
+since they intersect with the spheres at the surface. This is solved by
 
 \section{Case study}
+% Rerun on large dataset
 
@@
 
+\section{Availability}
+
+\section{Acknowledgments}
+
 \bibliographystyle{plain}

### 2017-03-04 ms.tex
Updates to multiple sections
Update introduction.
Add conclusion.
Info about cylinder billboards.
Implementation details.
Add todos.

@@
 \begin{document}
+
 \title{Atomify - a live LAMMPS visualizer}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-The typical workflow when developing LAMMPS scripts includes working with several programs.
-A text editor is needed to modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
-If physical quantities are computed, the data is often plotted with MATLAB or Python, where additional scripts must be used.
-This is a tedious process, especially for teaching purposes and for people who are new to LAMMPS.
-We here introduce Atomify; a high performance live visualizer for LAMMPS simulations, with stunning graphics able to simulate and render more than 250000 atoms with excellent frame rate on modern hardware.
-Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and computes, and an easy-to-use code editor in one single program.
-Direct access to the powerful machinery already built into LAMMPS allows easy access to advanced physical quantities.
-Atomify is open source software (GPL) written in C++, built on top of Qt.
+%
+The typical workflow when developing LAMMPS scripts includes working with
+several programs.
+A text editor is needed to modify the scripts,
+the terminal to run the simulation, and programs like VMD or Ovito to visualize
+the system over time.
+If physical quantities are computed, the data is often plotted with MATLAB or
+Python, where additional scripts must be used.
+This is a tedious process, especially for teaching purposes and for people who
+are new to LAMMPS.
+We here introduce Atomify;
+a high performance live visualizer for LAMMPS simulations,
+with stunning graphics able to simulate and render more than 250000 atoms with
+excellent frame rate on modern hardware.
+Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and
+computes, and an easy-to-use code editor in one single program.
+Direct access to the powerful machinery already built into LAMMPS allows easy
+access to advanced physical quantities.
+Atomify is open-source software (GPL) written in C++ using the Qt framework.
+%
 \end{abstract}
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Molecular dynamics (MD) has become a standard technique for simulating atoms and molecules in a broad range of fields.
+%
+Molecular dynamics (MD) is a common technique for simulating the motion of atoms
+and molecules in a broad range of fields.
+% TODO does MD also include larger particles?
+% TODO which fields?
 Over the years, increasingly sophisticated methods have been developed.
-With the large number of force fields, advanced techniques and GPU acceleration, implementing a good molecular dynamics program from scratch a challenging task.
-While many people at some point write their own MD code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}.
-Both of these codes have been developed for more than two decades and contains more than one million lines of code each.
+% TODO what methods?
+With the large number of force fields, advanced techniques and GPU acceleration,
+implementing a good molecular dynamics simulation is a challenging task.
+There are many software packages for molecular dynamics modelling
+available
+\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.
+Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}
+have been developed for more than two decades and contain more than one million
+lines of code each.
 
 The work in this paper is focused on LAMMPS.
-Although the software is well-documented and enables the user to perform advanced simulations, it can be a demanding job to learn how to use it well.
-A LAMMPS simulation is defined by a series of commands which are executed one by one.
-Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
-A time evolution of these quantities can in turn be saved to file for plotting and further analysis.
-Particle trajectories can be saved to a file and visualized by tools such as VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
-The lack of an intuitive GUI and visualization \footnote{which are listed in the non-features list on the web page: \url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat complicated.
+Although the software is well-documented and enables the user to perform
+advanced simulations, it can be demanding to learn how to use it well.
+A LAMMPS simulation is defined by a series of commands which are executed one by
+one.
+Physical quantities such as energy, temperature and stress can be measured by
+adding \textit{computes}.
+The time evolution of these quantities can in turn be saved to file for plotting
+and further analysis.
+Particle trajectories can be saved to a file and visualized by tools such as
+VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
+The lack of an intuitive GUI and visualization \footnote{which are listed in the
+non-features list on the web page:
+\url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat
+complicated.
 
-Atomify solves this problem by combining the script editing, simulating, visualizing and analyzing into one single application.
-It uses LAMMPS as a library and synchronizes after each timestep, copying the relevant information from LAMMPS to the GPU for visualization and data plotting.
-The visualization is done using raytracing on billboards allowing rendering of millions of atoms with good framerate.
+Atomify solves combines script editing, simulation,
+visualization, and analysis in one single software application.
+It uses LAMMPS as a library and synchronizes after each timestep,
+copying the relevant information from LAMMPS to the graphics processing unit
+(GPU) for visualization and data plotting.
+The visualization is optimized for high performance by raytracing on billboards.
+This allows visualization of millions of atoms with good framerate on desktop
+computers.
 
 \section{Features}
-Atomify comes with many useful features in addition to the 
+
+The main features of Atomify are script editing,
+live visualization, and live plotting of computed quantities.
+These will be described in detail in the following paragraphs.
+In addition, Atomify comes packaged with multiple examples,
+many of which have been made by members of the LAMMPS community.
+These examples are easily explored within Atomify.
+
+% TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
+
 \subsection{Script editor}
-The script editor is minimalistic with syntax highlighting for the LAMMPS scripting language and line numbers.
-It supports multiple open files and remembers which files you have open across working sessions.
-A simple Ctrl+R will restart the simulation with any changes you might have done.
+
+Atomify provides a lightweight script editor with syntax highlighting and line
+numbers.
+% TODO add built-in help and autocompletion to Atomify and mention here
+Multiple files can be open at the same time and persist across working sessions.
+The script can easily be restarted by clicking the button in the GUI or using
+the default shortcut (Ctrl+R in Windows and Linux or Cmd+R in macOS).
+Any changes made to the script are immediately visualized in the simulation.
+
 \subsection{Visualization}
@@
 
+In LAMMPS, computes are physical quantities calculated based on the running
+simulation, such as energy, temperature, and stress.
+% TODO better word for measures?
+These are typically macroscopic measures derived from the microscopic
+interactions between the atoms.
+
+Atomify provides live visualization of the compute values using various plotting
+techniques.
+For instance, the temperature of the simulated system can be plotted as a
+function of time as seen in figure TODO.
+% TODO add figure
+
 \subsection{Property coloring}
 
+Measures of microscopic quantities can be visualized.
+Any property of the individual atoms and bonds can in principle be used to color
+the spheres and cylinders, respectively.
+% TODO describe how this works in the GUI
+
 \section{Implementation}
+
 Atomify is built upon Qt.
-All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++.
-Simply put, Atomify runs an instance of a LAMMPS object enabling the user to visualize the current state of LAMMPS and interact with LAMMPS while the simulation is running.
+All GUI is defined in QML whereas the backend of the program communicating with
+LAMMPS is written in C++.
+Simply put, Atomify runs an instance of a LAMMPS object enabling the user to
+visualize the current state of LAMMPS and interact with LAMMPS while the
+simulation is running.
 
 \subsection{Communicating with LAMMPS}
-LAMMPS can be compiled as a library with most of its contents being accessable through either the library interface or public variables in all classes.
+
+LAMMPS can be compiled as a library with most of its contents being accessable
+through either the library interface or public variables in all classes.
+LAMMPS provides a C++ API that can be used to access parts of the internal data
+in the simulation as well as for issuing commands to LAMMPS.
+Further, direct access to raw data in LAMMPS is available through the individual
+C++ classes.
 
@@
 
+Live plotting is implemented using Qt Charts and Qt Data Visualization,
+which are part of the Qt framework.
+The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
+visualization.
+
 \subsection{Data pipeline}
-When rendering one often wants to modify the data from LAMMPS before it is visualized.
-Examples are periodic images of the simulation, slicing and coloring.
-We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
+
+When rendering one often wants to modify the data
+from LAMMPS before it is visualized.
+Examples are periodic images of the simulation,
+slicing and coloring.
+We have been inspired by the pipeline used in Ovito where the data flows through
+several \textit{modifiers}, each modifying the visualization data before the
+data is converted to a format for the GPU.
 
 \section{Rendering techniques}
+
 Simulations of atoms are often visualized using spheres as atoms and cylinders.
-The spheres represent the atoms while the cylinders represent the bonds between the atoms.
+The spheres represent the atoms while the cylinders represent the bonds between
+the atoms.
 This way, the molecular structure is easy to understand and interpret.
-In many visualization tools, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest.
-One problem with this rendering technique is that each sphere needs many, often hundreds, triangles in order to look spherical.
-This significantly reduces the rendering performance.
+In many visualization tools, the spheres and cylinders are built up by many
+triangles connected so they form the geometrical object of interest.
+One problem with this rendering technique is that each sphere needs many,
+often hundreds, of triangles in order to look spherical.
 A common technique to overcome this problem is to use billboards.
-Billboards are planes, made up by two or four triangles\footnote{The spheres are using two triangles, whereas the cylinders use four.} with surface normals parallel to the vector pointing towards the camera.
-By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic, see Figure \ref{fig:final_billboards}.
+This significantly reduces the number of vertices sent from the CPU to the GPU,
+which in turn improves rendering performance.
+A sphere may consist of an arbitrary number of vertices,
+depending on the level of detail needed.
+A billboard will on the other hand consist of only 4 vertices and can be
+represented as a point on the CPU which is then expanded on the GPU using shader
+programming.
+By doing proper shading, the billboards can mimick the spheres and cylinders so
+they look realistic, see Figure \ref{fig:final_billboards}.
 
@@
 \subsection{Sphere billboards}
-Each sphere is visualized as two triangles making up a square large enough to cover all pixels the sphere needs.
-To reduce the CPU workload, all 4 corner vertices of the square are placed at the exact position of the sphere.
-The radius and a vertex id is specified, so that the vertex shader can move the 4 vertices so that the plane is orthogonal to the view vector and is larger than the cross sectional area of the sphere of interest.
+
+Each sphere is visualized as two triangles making up a square large enough to
+cover all pixels the sphere needs.
+To reduce the CPU workload, all 4 corner vertices of the square are placed at
+the exact position of the sphere.
+The radius and a vertex id is specified, so that the vertex shader can move the
+4 vertices so that the plane is orthogonal to the view vector and is larger than
+the cross sectional area of the sphere of interest.
 This is illustrated in figure \ref{fig:billboards}.
@@
 \subsection{Cylinder billboards}
-The cylinders are a bit more difficult because of two reasons. 
-since they intersect with the spheres at the surface. This is solved by
+%
+% TODO should we use the other terminology here rather than billboards, something about imposter visualization?
+To render bonds in the molecular structure, we have implemented a method that
+visualizes realistic cylinder shapes with billboards.
+Cylinders are more complicated to visualize with billboards because they have a
+more complex geometry.
+While spheres obviously are spherically symmetric and can be rendered the same
+way regardless of viewing angle, we need to take this into account when
+rendering cylinders.
+Furhter, the bonds need to intersect with the sphere surface in a way that
+needs to be handled by the cylinder rendering technique.
+
+The basic principle is however the same as for the spheres.
+We define the vertices needed on the CPU with the same position and add the
+necessary information about the cylinder to the vertex attributes.
+This information is then used in the vertex shader to draw the triangles of
+the billboard.
+Finally, ray tracing is used to draw the final cylinder shape based on top
+of this billboard.
+
+% TODO mention issue with end caps if this is relevant for the overlapping parts
+
+% TODO explain the details about billboard rendering?
 
@@
 \section{Conclusion}
-We have
+%
+We have presented Atomify, a software for live visualization of molecular
+dynamics simulations in LAMMPS.
+Atomify simplifies the workflow of researchers by combining script development,
+analysis and visualization in an intuitive user interface.
+The software can also be used to improve training of students using LAMMPS by
+providing immediate, visual feedback to script changes.
 

### 2017-03-04 ms.tex
Fix footnote

@@
 available
-\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.
+\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.}
 Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}

### 2017-03-04 ms.tex
Mention Atomify mobile

@@
 computers.
+
+A simplified version of Atomify is made available for mobile platforms (Android
+and iOS).
+This version of Atomify provides access to some of the examples and is intended
+for exploration of molecular dynamics simulations by students.
+It also works as a demonstration of the visualization capabilities of the
+desktop version of the software.
+The authors are optimistic that teachers can use the visualizations provided by
+Atomify to explain microscopic interactions underlying concepts in topics such
+as thermodynamics, geophysics, and biology.
 

### 2017-04-05 ms.tex
Add mention of Qt3D
Stuff

--- 2017-03-04 ms.tex
@@
 \usepackage{afterpage}
+\usepackage{todo}
 \usepackage[hidelinks]{hyperref} 
@@
 \begin{document}
-
 \title{Atomify - a live LAMMPS visualizer}
@@
 \author{Svenn-Arne Dragly$^{1}$}
-\author{Anders Malthe-S\o renssen$^1$}
 \affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract} 
-%
-The typical workflow when developing LAMMPS scripts includes working with
-several programs.
-A text editor is needed to modify the scripts,
-the terminal to run the simulation, and programs like VMD or Ovito to visualize
-the system over time.
-If physical quantities are computed, the data is often plotted with MATLAB or
-Python, where additional scripts must be used.
-This is a tedious process, especially for teaching purposes and for people who
-are new to LAMMPS.
-We here introduce Atomify;
-a high performance live visualizer for LAMMPS simulations,
-with stunning graphics able to simulate and render more than 250000 atoms with
-excellent frame rate on modern hardware.
-Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and
-computes, and an easy-to-use code editor in one single program.
-Direct access to the powerful machinery already built into LAMMPS allows easy
-access to advanced physical quantities.
-Atomify is open-source software (GPL) written in C++ using the Qt framework.
-%
+The typical workflow when developing LAMMPS scripts includes working with several programs.
+A text editor is needed to modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
+If physical quantities are computed, the data is often plotted with MATLAB or Python, where additional scripts must be used.
+This is a tedious process, especially for teaching purposes and for people who are new to LAMMPS.
+We here introduce Atomify; a high performance live visualizer for LAMMPS simulations, with stunning graphics able to simulate and render more than 250000 atoms with excellent frame rate on modern hardware.
+Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and computes, and an easy-to-use code editor in one single program.
+Direct access to the powerful machinery already built into LAMMPS allows easy access to advanced physical quantities.
+Atomify is open source software (GPL) written in C++, built on top of Qt.
 \end{abstract}
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-%
-Molecular dynamics (MD) is a common technique for simulating the motion of atoms
-and molecules in a broad range of fields.
-% TODO does MD also include larger particles?
-% TODO which fields?
+Molecular dynamics (MD) has become a standard technique for simulating atoms and molecules in a broad range of fields.
 Over the years, increasingly sophisticated methods have been developed.
-% TODO what methods?
-With the large number of force fields, advanced techniques and GPU acceleration,
-implementing a good molecular dynamics simulation is a challenging task.
-There are many software packages for molecular dynamics modelling
-available
-\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.
-Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}
-have been developed for more than two decades and contain more than one million
-lines of code each.
+With the large number of force fields, advanced techniques and GPU acceleration, implementing a good molecular dynamics program from scratch a challenging task.
+While many people at some point write their own MD code, most end up using one of the many available codes\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}} such as LAMMPS\cite{Plimpton1995Fast}, GROMACS\cite{Pronk2013}, NAMD\cite{Phillips2005Scalable}.
+These codes have been developed for more than two decades and contains more than one million lines of code each.
+\todo{check this}
 
 The work in this paper is focused on LAMMPS.
-Although the software is well-documented and enables the user to perform
-advanced simulations, it can be demanding to learn how to use it well.
-A LAMMPS simulation is defined by a series of commands which are executed one by
-one.
-Physical quantities such as energy, temperature and stress can be measured by
-adding \textit{computes}.
-The time evolution of these quantities can in turn be saved to file for plotting
-and further analysis.
-Particle trajectories can be saved to a file and visualized by tools such as
-VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
-The lack of an intuitive GUI and visualization \footnote{which are listed in the
-non-features list on the web page:
-\url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat
-complicated.
+Although the software is well-documented and enables the user to perform advanced simulations, it can be a demanding job to learn how to use it well.
+A LAMMPS simulation is performed by a series of commands which are executed one by one.
+Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
+A time evolution of these quantities can in turn be saved to file for plotting and further analysis.
+Particle trajectories can be saved to a file and visualized by tools such as VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
+The lack of an intuitive GUI and visualization \footnote{which are listed in the non-features list on the web page: \url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat complicated.
 
-Atomify solves combines script editing, simulation,
-visualization, and analysis in one single software application.
-It uses LAMMPS as a library and synchronizes after each timestep,
-copying the relevant information from LAMMPS to the graphics processing unit
-(GPU) for visualization and data plotting.
-The visualization is optimized for high performance by raytracing on billboards.
-This allows visualization of millions of atoms with good framerate on desktop
-computers.
+Atomify solves this problem by combining the script editing, simulating, visualizing and analyzing into one single application.
+It uses LAMMPS as a library and synchronizes after each timestep, copying the relevant information from LAMMPS to the GPU for visualization and data plotting.
+The visualization is done using raytracing on billboards allowing rendering of millions of atoms with good framerate.
+Atomify is designed with simplicity as main goal.
 
+\todo{Write about existing GUI software such as Materials Studio and MacroModel}
 \section{Features}
+Atomify comes with many useful features in addition to the 
+\subsection{Script editor}
+The script editor is minimalistic with line numbers and syntax highlighting for the LAMMPS scripting language.
+It supports multiple open files and remembers which files you have open across working sessions.
+A simple Ctrl+R will restart the simulation with any changes you might have done.
+\subsection{Visualization}
+Visualization of the atomic positions and the molecular structure is done using very efficient billboard rendering using OpenGL and Qt 3D.
 
-The main features of Atomify are script editing,
-live visualization, and live plotting of computed quantities.
-These will be described in detail in the following paragraphs.
-In addition, Atomify comes packaged with multiple examples,
-many of which have been made by members of the LAMMPS community.
-These examples are easily explored within Atomify.
+\subsection{Group and region highlighting}
 
-% TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
+\subsection{Live plotting and property coloring}
+LAMMPS can produce many different outputs using computes and variables.
+All computes, variables and fixes Time evolution of scalar quantities such as temperature, stress components and mean square displacement are
 
-\subsection{Script editor}
+If a compute or variable produces a per-atom quantity, it can be used to color the atoms on a color scale from the minimum finite value to the maximum finite value, see figure \ref{fig:property_coloring}.
 
-Atomify provides a lightweight script editor with syntax highlighting and line
-numbers.
-% TODO add built-in help and autocompletion to Atomify and mention here
-Multiple files can be open at the same time and persist across working sessions.
-The script can easily be restarted by clicking the button in the GUI or using
-the default shortcut (Ctrl+R in Windows and Linux or Cmd+R in macOS).
-Any changes made to the script are immediately visualized in the simulation.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{property_coloring.png}
+	\caption{Atomify can use any per-atom quantity to color the atoms through computes or variables.
+Here the atoms are colored using the velocity squared where the middle atoms have lower mass than the other atoms.
+}
+	\label{fig:property_coloring}
+\end{figure}
 
-\subsection{Visualization}
+\section{Implementation}
+Atomify is built upon Qt.
+All GUI is defined in QML whereas the backend of the program communicating with LAMMPS is written in c++.
+Simply put, Atomify runs an instance of a LAMMPS object enabling the user to visualize the current state of LAMMPS and interact with LAMMPS while the simulation is running.
+
+\subsection{Communicating with LAMMPS}
+LAMMPS can be compiled as a library with most of its contents being accessable through either the library interface or public variables in all classes.
 
@@
 
-In LAMMPS, computes are physical quantities calculated based on the running
-simulation, such as energy, temperature, and stress.
-% TODO better word for measures?
-These are typically macroscopic measures derived from the microscopic
-interactions between the atoms.
-
-Atomify provides live visualization of the compute values using various plotting
-techniques.
-For instance, the temperature of the simulated system can be plotted as a
-function of time as seen in figure TODO.
-% TODO add figure
-
-\subsection{Property coloring}
-
-Measures of microscopic quantities can be visualized.
-Any property of the individual atoms and bonds can in principle be used to color
-the spheres and cylinders, respectively.
-% TODO describe how this works in the GUI
-
-\section{Implementation}
-
-Atomify is built upon Qt.
-All GUI is defined in QML whereas the backend of the program communicating with
-LAMMPS is written in C++.
-Simply put, Atomify runs an instance of a LAMMPS object enabling the user to
-visualize the current state of LAMMPS and interact with LAMMPS while the
-simulation is running.
-
-\subsection{Communicating with LAMMPS}
-
-LAMMPS can be compiled as a library with most of its contents being accessable
-through either the library interface or public variables in all classes.
-LAMMPS provides a C++ API that can be used to access parts of the internal data
-in the simulation as well as for issuing commands to LAMMPS.
-Further, direct access to raw data in LAMMPS is available through the individual
-C++ classes.
-
-\subsection{Live plotting}
-
-Live plotting is implemented using Qt Charts and Qt Data Visualization,
-which are part of the Qt framework.
-The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
-visualization.
-
 \subsection{Data pipeline}
-
-When rendering one often wants to modify the data
-from LAMMPS before it is visualized.
-Examples are periodic images of the simulation,
-slicing and coloring.
-We have been inspired by the pipeline used in Ovito where the data flows through
-several \textit{modifiers}, each modifying the visualization data before the
-data is converted to a format for the GPU.
+When rendering one often wants to modify the data from LAMMPS before it is visualized.
+Examples are periodic images of the simulation, slicing and coloring.
+We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
 
 \section{Rendering techniques}
-
 Simulations of atoms are often visualized using spheres as atoms and cylinders.
-The spheres represent the atoms while the cylinders represent the bonds between
-the atoms.
+The spheres represent the atoms while the cylinders represent the bonds between the atoms.
 This way, the molecular structure is easy to understand and interpret.
-In many visualization tools, the spheres and cylinders are built up by many
-triangles connected so they form the geometrical object of interest.
-One problem with this rendering technique is that each sphere needs many,
-often hundreds, of triangles in order to look spherical.
+In many visualization tools, the spheres and cylinders are built up by many triangles connected so they form the geometrical object of interest.
+One problem with this rendering technique is that each sphere needs many, often hundreds, triangles in order to look spherical.
+This significantly reduces the rendering performance.
 A common technique to overcome this problem is to use billboards.
-This significantly reduces the number of vertices sent from the CPU to the GPU,
-which in turn improves rendering performance.
-A sphere may consist of an arbitrary number of vertices,
-depending on the level of detail needed.
-A billboard will on the other hand consist of only 4 vertices and can be
-represented as a point on the CPU which is then expanded on the GPU using shader
-programming.
-By doing proper shading, the billboards can mimick the spheres and cylinders so
-they look realistic, see Figure \ref{fig:final_billboards}.
+Billboards are planes, made up by two or four triangles\footnote{The spheres are using two triangles, whereas the cylinders use four.} with surface normals parallel to the vector pointing towards the camera.
+By doing proper shading, the billboards can mimick the spheres and cylinders so they look realistic, see Figure \ref{fig:final_billboards}.
 
@@
 	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Billboards can produce pixel perfect rendering of molecules. Here we see a water molecule being rendererd with two light sources showing specular reflection and diffuse light effects.}
+	\caption{Billboards can produce pixel perfect rendering of molecules.
+Here we see a water molecule being rendered as billboards with two light sources showing specular reflection and diffuse light effects.
+}
 	\label{fig:final_billboards}
@@
 \subsection{Sphere billboards}
-
-Each sphere is visualized as two triangles making up a square large enough to
-cover all pixels the sphere needs.
-To reduce the CPU workload, all 4 corner vertices of the square are placed at
-the exact position of the sphere.
-The radius and a vertex id is specified, so that the vertex shader can move the
-4 vertices so that the plane is orthogonal to the view vector and is larger than
-the cross sectional area of the sphere of interest.
+Each sphere is visualized as two triangles making up a square large enough to cover all pixels the sphere needs.
+To reduce the CPU workload, all 4 corner vertices of the square are placed at the exact position of the sphere.
+The radius and a vertex id is specified, so that the vertex shader can move the 4 vertices so that the plane is orthogonal to the view vector and is larger than the cross sectional area of the sphere of interest.
 This is illustrated in figure \ref{fig:billboards}.
@@
 \subsection{Cylinder billboards}
-%
-% TODO should we use the other terminology here rather than billboards, something about imposter visualization?
-To render bonds in the molecular structure, we have implemented a method that
-visualizes realistic cylinder shapes with billboards.
-Cylinders are more complicated to visualize with billboards because they have a
-more complex geometry.
-While spheres obviously are spherically symmetric and can be rendered the same
-way regardless of viewing angle, we need to take this into account when
-rendering cylinders.
-Furhter, the bonds need to intersect with the sphere surface in a way that
-needs to be handled by the cylinder rendering technique.
-
-The basic principle is however the same as for the spheres.
-We define the vertices needed on the CPU with the same position and add the
-necessary information about the cylinder to the vertex attributes.
-This information is then used in the vertex shader to draw the triangles of
-the billboard.
-Finally, ray tracing is used to draw the final cylinder shape based on top
-of this billboard.
-
-% TODO mention issue with end caps if this is relevant for the overlapping parts
-
-% TODO explain the details about billboard rendering?
+The cylinders are a bit more difficult because of two reasons. 
+since they intersect with the spheres at the surface. This is solved by
 
@@
 \section{Conclusion}
-%
-We have presented Atomify, a software for live visualization of molecular
-dynamics simulations in LAMMPS.
-Atomify simplifies the workflow of researchers by combining script development,
-analysis and visualization in an intuitive user interface.
-The software can also be used to improve training of students using LAMMPS by
-providing immediate, visual feedback to script changes.
+We have
 

### 2017-04-07 ms.tex
Added placeholders for figures

--- 2017-03-04 ms.tex
@@
 \usepackage{epstopdf}
+\usepackage{todo}
 \begin{document}
@@
 \footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.}
-Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}
-have been developed for more than two decades and contain more than one million
-lines of code each.
+Some packages, such as LAMMPS\cite{Plimpton1995Fast}, GROMACS\cite{Pronk2013}
+and NAMD\cite{Phillips2005Scalable} have been developed for more than two decades 
+and contain more than one million lines of code each.
 
@@
 advanced simulations, it can be demanding to learn how to use it well.
-A LAMMPS simulation is defined by a series of commands which are executed one by
+A LAMMPS simulation is performed by a series of commands which are executed one by
 one.
@@
 This allows visualization of millions of atoms with good framerate on desktop
-computers.
+computers. Atomify is designed with simplicity as main goal.
+
+TODO: Write about existing GUI software such as Materials Studio and MacroModel \\
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Oversikt over GUI}
+	\label{fig:gui}
+\end{figure}
+
 \section{Features}
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Workflow}
+	\label{fig:gui}
+\end{figure}
+
 % TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
@@
 \subsection{Script editor}
-
 Atomify provides a lightweight script editor with syntax highlighting and line
@@
 \subsection{Visualization}
+TODO: Color atoms based on property \\
+
+\subsection{Dashboard}
+TODO: Highlight groups/regions \\
+TODO: Show/hide groups/regions \\
+TODO: Rendering parameters \\
+TODO: Atomify commands \\
+TODO: Rendering parameters \\
+TODO: Plot compute/variable/fix \\
 
 \subsection{Live plotting}
+TODO: Histogram over per atom quantities \\
+TODO: Time evolution of quantity \\
+TODO: 2d ave/chunk binning \\
 
@@
 
-\subsection{Property coloring}
-
-Measures of microscopic quantities can be visualized.
-Any property of the individual atoms and bonds can in principle be used to color
-the spheres and cylinders, respectively.
-% TODO describe how this works in the GUI
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Features}
+	\label{fig:gui}
+\end{figure}
 
@@
 simulation is running.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Data pipeline (lammps -> atomify)}
+	\label{fig:gui}
+\end{figure}
 
@@
 
-\section{Case study}
+\section{Case study (Anders)}
 % Rerun on large dataset
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{Case study result}
+	\label{fig:gui}
+\end{figure}
 

### 2017-04-12 ms.tex
SA will do features
Add newline at end of file
Moved to revtex4-1. May break on Mac?
Fix revtex and add features

@@
 \subsection{Script editor}
+
 Atomify provides a lightweight script editor with syntax highlighting and line
@@
 
+Certain Atomify-commands can be added to the comments of a regular LAMMPS script
+to modify properties of the GUI.
+For instance, the color and size of the atoms can be set based on the type by
+the command \texttt{\#/atom}.
+To set the color to white and radius to 2.0 for particle type 1,
+the user can apply the command \texttt{\#/atom 1 2.0 \#ffffff}.
+The initial camera position can also be set similarily.
+For a full list of the available commands, see the Atomify documentation.
+
+TODO: Add link to documentation
+
 \subsection{Visualization}
-TODO: Color atoms based on property \\
+
+Atomify provides live visualization of particles in a simulation in its 3D view.
+The particles can be colored based on properties such as atom type,
+velocity, and force.
+The coloring scheme can be changed while the simulation is running by hovering
+the mouse cursor over groups in the dashboard.
+Light colors and strength can also be changed in the dashboard.
+This will be described in further detail in the following section.
 
 \subsection{Dashboard}
-TODO: Highlight groups/regions \\
-TODO: Show/hide groups/regions \\
-TODO: Rendering parameters \\
-TODO: Atomify commands \\
-TODO: Rendering parameters \\
-TODO: Plot compute/variable/fix \\
+
+It is possible to organize particles in groups and regions in LAMMPS.
+These are shown in the dashboard in Atomify, which also provides controls to
+highlight or hide specific groups or regions.
+To highlight a group or region, the user only needs to hover the name in the
+dashboard.
+The visibility icon can be clicked to hide a group or region.
+
+Parameters for rendering, such as the light strength and color,
+can be modified in the Rendering tab of the dashboard.
+See the above section about the script editor for information about how to
+modify the color of the particles.
+
+In LAMMPS, computes are values calculated based on properties of the running
+simulation.
+Variables are user defined expressions which can be used to combine values in
+calculations.
+Once defined in a LAMMPS script, these can be plotted as a function of time in
+Atomify.
+This is done by clicking the name of the variable or compute in the simulation
+tab.
+We will explore plots in further detail in the following section.
+
+TODO: fixes \\
 
@@
 LAMMPS is written in C++.
+High-performance visualization is achieved by implementing billboards in Qt3D.
 Simply put, Atomify runs an instance of a LAMMPS object enabling the user to

### 2017-05-07 ms.tex
Added gui figure
Changed key

@@
-\documentclass[aps,pre,twocolumn,letterpaper,floatfix]{revtex4}
+\documentclass[aps,pre,twocolumn,letterpaper,floatfix,nofootinbib]{revtex4}
 \usepackage{graphicx} 
@@
 \usepackage{todo}
+\usepackage{menukeys}
+
 \begin{document}
@@
 %
-Molecular dynamics (MD) is a common technique for simulating the motion of atoms
-and molecules in a broad range of fields.
+Molecular dynamics (MD) is a common technique for simulating the motion of atoms, molecules and larger particles in a broad range of fields such as physics, chemistry and biology \cite{flerefelt}.
 % TODO does MD also include larger particles?
@@
 implementing a good molecular dynamics simulation is a challenging task.
-There are many software packages for molecular dynamics modelling
-available
-\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.}
+There are many software packages for molecular modelling
+available\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
 Some packages, such as LAMMPS\cite{Plimpton1995Fast}, GROMACS\cite{Pronk2013}
@@
 VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
-The lack of an intuitive GUI and visualization \footnote{which are listed in the
-non-features list on the web page:
-\url{http://lammps.sandia.gov/non_features.html}} makes the workflow somewhat
+The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the web page:
+\url{http://lammps.sandia.gov/non_features.html}.} makes the workflow somewhat
 complicated.
@@
 (GPU) for visualization and data plotting.
-The visualization is optimized for high performance by raytracing on billboards.
+The visualization is optimized for high performance by raytracing billboards.
 This allows visualization of millions of atoms with good framerate on desktop
@@
 as thermodynamics, geophysics, and biology.
-
-\begin{figure}
+\begin{figure*}
 	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Oversikt over GUI}
+	\includegraphics[width=0.95\textwidth]{gui.png}
+	\caption{Overview of the Graphical User Interface (GUI) in Atomify.}
 	\label{fig:gui}
-\end{figure}
-
+\end{figure*}
 \section{Features}
@@
 The script can easily be restarted by clicking the button in the GUI or using
-the default shortcut (Ctrl+R in Windows and Linux or Cmd+R in macOS).
-Any changes made to the script are immediately visualized in the simulation.
+the default shortcut (\keys{Ctrl+R} in Windows and Linux or \keys{\cmd R} in macOS).
+This enables you to quickly do changes in the script and see the changes immediately.
 
 Certain Atomify-commands can be added to the comments of a regular LAMMPS script
-to modify properties of the GUI.
+to modify properties of the GUI. All these start with \keys{\texttt{\#}} so that
+LAMMPS ignores them as they are interpreted as comments.
 For instance, the color and size of the atoms can be set based on the type by
-the command \texttt{\#/atom}.
+the command \keys{\texttt{\#/atom}}.
 To set the color to white and radius to 2.0 for particle type 1,
-the user can apply the command \texttt{\#/atom 1 2.0 \#ffffff}.
+the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}. Certain built-in atom
+types have default values and can be accessed with \keys{\texttt{\#/atom 1 oxygen}} for simplicity.
 The initial camera position can also be set similarily.
@@
 
-\bibliographystyle{plain}
+% \bibliographystyle{plain}
 \bibliography{Remote}

### 2017-05-07 ms.tex
Changed key

@@
 The script can easily be restarted by clicking the button in the GUI or using
-the default shortcut (\keys{Ctrl+R} in Windows and Linux or \keys{\cmd R} in macOS).
+the default shortcut (\keys{Ctrl+R} in Windows and Linux or \keys{\cmd+R} in macOS).
 This enables you to quickly do changes in the script and see the changes immediately.

### 2017-05-07 ms.tex
Added flowchart

@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Workflow}
-	\label{fig:gui}
+	\includegraphics[width=0.5\textwidth]{flowchart.png}
+	\caption{The typical workflow when using LAMMPS.
+a) A LAMMPS script is written using a text editor.
+b) Simulation is performed from the terminal.
+c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
+Atomify simplifies the workflow by combining all steps into one application.
+}
+	\label{fig:flowchart}
 \end{figure}

### 2017-05-10 ms.tex
Added figure, wrote some more

@@
 \url{http://lammps.sandia.gov/non_features.html}.} makes the workflow somewhat
-complicated.
+complicated, see figure \ref{fig:flowchart}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{flowchart.png}
+	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
+a) A LAMMPS script is written using a text editor.
+b) Simulation is performed from the terminal.
+c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
+Atomify simplifies the workflow by combining all steps into a single application.
+}
+	\label{fig:flowchart}
+\end{figure}
 
@@
 computers. Atomify is designed with simplicity as main goal.
-
-TODO: Write about existing GUI software such as Materials Studio and MacroModel \\
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{flowchart.png}
-	\caption{The typical workflow when using LAMMPS.
-a) A LAMMPS script is written using a text editor.
-b) Simulation is performed from the terminal.
-c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
-Atomify simplifies the workflow by combining all steps into one application.
-}
-	\label{fig:flowchart}
-\end{figure}
-
 % TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
@@
 % TODO add built-in help and autocompletion to Atomify and mention here
-Multiple files can be open at the same time and persist across working sessions.
+Multiple files can be open at the same time and the state persist across working sessions.
 The script can easily be restarted by clicking the button in the GUI or using
@@
 The initial camera position can also be set similarily.
-For a full list of the available commands, see the Atomify documentation.
-
-TODO: Add link to documentation
+For a full list of the available commands, see the Atomify documentation\cite{atomifydocumentation}.
 
@@
 Atomify provides live visualization of particles in a simulation in its 3D view. 
-The particles can be colored based on properties such as atom type,
-velocity, and force.
+The particles can be colored based on any produced per-atom quantity in LAMMPS such as
+atom type, velocity, force or a variable formula.
 The coloring scheme can be changed while the simulation is running by hovering
@@
 In LAMMPS, computes are physical quantities calculated based on the running
-simulation, such as energy, temperature, and stress.
+simulation, such as energy, temperature and stress.
 % TODO better word for measures?
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Features}
+	\includegraphics[width=0.3\textwidth]{dashboard.png}
+	\caption{Dashboard}
 	\label{fig:gui}

### 2017-06-16 ms.tex
Update figure dummy texts

@@
 %
-The typical workflow when developing LAMMPS scripts includes working with
-several programs.
-A text editor is needed to modify the scripts,
-the terminal to run the simulation, and programs like VMD or Ovito to visualize
-the system over time.
+The typical LAMMPS workflow includes working with a text editor to modify
+scripts, the terminal to run simulations, and programs like VMD or Ovito to
+visualize trajectories.
 If physical quantities are computed, the data is often plotted with MATLAB or
@@
 a high performance live visualizer for LAMMPS simulations,
-with stunning graphics able to simulate and render more than 250000 atoms with
+with stunning graphics able to simulate and render more than 250,000 atoms with
 excellent frame rate on modern hardware.
-Atomify supports OpenMP acceleration, live plotting of LAMMPS variables and
-computes, and an easy-to-use code editor in one single program.
+Atomify supports OpenMP and GPU acceleration, live plotting of LAMMPS variables
+and computes, and an easy-to-use code editor in one single program.
 Direct access to the powerful machinery already built into LAMMPS allows easy
@@
 	\includegraphics[width=0.95\textwidth]{gui.png}
-	\caption{Overview of the Graphical User Interface (GUI) in Atomify.}
+	\caption{%
+    Overview of the Graphical User Interface (GUI) in Atomify.
+    The toolbar (1) provides changing
+    between editing, viewing and analyzing the running simulation,
+    in addition to playback controls.
+    The file browser (2) contain the list of open LAMMPS scripts or data files.
+    The text editor (3) provides code highlighting.
+    The viewport (4) shows the current simulation.
+    The simulation properties (5) shows the simulations details, gives access to 
+    LAMMPS objects such as groups, regions and computes, and the rendering
+    properties (6) lets you change the viewport settings, such as lighting and
+    draw mode.
+    TODO: Add numbers to figure.
+    }
 	\label{fig:gui}
@@
 Certain Atomify-commands can be added to the comments of a regular LAMMPS script
-to modify properties of the GUI. All these start with \keys{\texttt{\#}} so that
-LAMMPS ignores them as they are interpreted as comments.
+to modify properties of the GUI.
+All these start with \keys{\texttt{\#}} so that LAMMPS ignores them as they are
+interpreted as comments.
 For instance, the color and size of the atoms can be set based on the type by
@@
 To set the color to white and radius to 2.0 for particle type 1,
-the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}. Certain built-in atom
-types have default values and can be accessed with \keys{\texttt{\#/atom 1 oxygen}} for simplicity.
+the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}.
+Certain built-in atom types have default values and can be accessed with
+\keys{\texttt{\#/atom 1 oxygen}} for simplicity.
 The initial camera position can also be set similarily.
-For a full list of the available commands, see the Atomify documentation\cite{atomifydocumentation}.
+For a full list of the available commands, see the Atomify
+documentation\cite{atomifydocumentation}.
 
@@
 
-In LAMMPS, computes are values calculated based on properties of the running
-simulation.
+In LAMMPS, computes are computations performed on a group of atoms.
 Variables are user defined expressions which can be used to combine values in
@@
 
-TODO: fixes \\
+Any operations that is applied to the system in a LAMMPS timestep or
+minimization step is called a ``fix''.
+These fixes are defined in the LAMMPS script using the ``fix'' keyword.
+Atomify registers all defined fixes and lists these in the dashboard.
 
@@
 	\caption{Dashboard}
-	\label{fig:gui}
+	\label{fig:dashboard}
 \end{figure}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Data pipeline (lammps -> atomify)}
-	\label{fig:gui}
-\end{figure}
-
 \subsection{Communicating with LAMMPS}
@@
 
-\subsection{Live plotting}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/data-pipeline.pdf}
+	\caption{Rendering in Atomify is based on modifying the data from LAMMPS
+    by coloring, producing periodic images, and generating bonds between atoms.
+    The data is extracted from LAMMPS using the library API and by accessing
+    the core classes.}
+	\label{fig:data-pipeline}
+\end{figure}
 
-Live plotting is implemented using Qt Charts and Qt Data Visualization,
-which are part of the Qt framework.
-The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
-visualization.
-
-\subsection{Data pipeline}
-
-When rendering one often wants to modify the data
-from LAMMPS before it is visualized.
+The data pipeline from LAMMPS to rendering in Atomify is illustrated in figure
+\ref{fig:data-pipeline}.
+When rendering one often wants to modify the data from LAMMPS before it is
+visualized.
 Examples are periodic images of the simulation,
@@
 
-\section{Rendering techniques}
+\subsection{Rendering techniques}
 
@@
 
+The simple case study showed how Atomify can be used for quick iteration in
+
 \subsection{Future work}
@@
 
-% \bibliographystyle{plain}
+\section{Disclosure}
+
+Svenn-Arne Dragly is employed part-time by The Qt Company.
+
 \bibliography{Remote}

### 2017-06-16 ms.tex
Merge

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{TODO: Overview of workflow, going from script, to simulation, to analyzing data, to results}
+	\label{fig:gui}
+\end{figure}
+
 % TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
@@
 Certain Atomify-commands can be added to the comments of a regular LAMMPS script
-to modify properties of the GUI.
-All these start with \keys{\texttt{\#}} so that LAMMPS ignores them as they are
-interpreted as comments.
+to modify properties of the GUI. All these start with \keys{\texttt{\#}} so that
+LAMMPS ignores them as they are interpreted as comments.
 For instance, the color and size of the atoms can be set based on the type by
@@
 To set the color to white and radius to 2.0 for particle type 1,
-the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}.
-Certain built-in atom types have default values and can be accessed with
-\keys{\texttt{\#/atom 1 oxygen}} for simplicity.
+the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}. Certain built-in atom
+types have default values and can be accessed with \keys{\texttt{\#/atom 1 oxygen}} for simplicity.
 The initial camera position can also be set similarily.
-For a full list of the available commands, see the Atomify
-documentation\cite{atomifydocumentation}.
+For a full list of the available commands, see the Atomify documentation\cite{atomifydocumentation}.
 
@@
 	\caption{Dashboard}
-	\label{fig:dashboard}
+	\label{fig:gui}
 \end{figure}
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{final_billboard.png}
+	\caption{TODO: How data flows from LAMMPS to Atomify, technically}
+	\label{fig:gui}
+\end{figure}
+
 \subsection{Communicating with LAMMPS}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/data-pipeline.pdf}
-	\caption{Rendering in Atomify is based on modifying the data from LAMMPS
-    by coloring, producing periodic images, and generating bonds between atoms.
-    The data is extracted from LAMMPS using the library API and by accessing
-    the core classes.}
-	\label{fig:data-pipeline}
-\end{figure}
+\subsection{Live plotting}
 
-The data pipeline from LAMMPS to rendering in Atomify is illustrated in figure
-\ref{fig:data-pipeline}.
-When rendering one often wants to modify the data from LAMMPS before it is
-visualized.
+Live plotting is implemented using Qt Charts and Qt Data Visualization,
+which are part of the Qt framework.
+The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
+visualization.
+
+\subsection{Data pipeline}
+
+When rendering one often wants to modify the data
+from LAMMPS before it is visualized.
 Examples are periodic images of the simulation,
@@
 
-\subsection{Rendering techniques}
+\section{Rendering techniques}
 
@@
 
-The simple case study showed how Atomify can be used for quick iteration in
-
 \subsection{Future work}

### 2017-06-16 ms.tex
Added text on future work and data-pipeline figures

--- 2017-06-16 ms.tex
@@
 live visualization, and live plotting of computed quantities.
-These will be described in detail in the following paragraphs.
 In addition, Atomify comes packaged with multiple examples,
@@
 These examples are easily explored within Atomify.
-
-% TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features
-
-\subsection{Script editor}
 
@@
 
-\subsection{Visualization}
-
 Atomify provides live visualization of particles in a simulation in its 3D view. 
@@
 
-\subsection{Dashboard}
-
 It is possible to organize particles in groups and regions in LAMMPS.
@@
 
-Parameters for rendering, such as the light strength and color,
-can be modified in the Rendering tab of the dashboard.
+Parameters for rendering, such as the light strength,
+attenuation, and color can be modified in the Rendering tab of the dashboard.
 See the above section about the script editor for information about how to
@@
 
-\subsection{Live plotting}
-TODO: Histogram over per atom quantities \\
 TODO: Time evolution of quantity \\
@@
 interactions between the atoms.
+These can be plotted as a function of time and visualized while the 
+simulation is running.
+Quantities that are measured per atom can be plotted in a histogram.
 
@@
 \subsection{Future work}
-Atomify is far from finished.\\
-A web version of Atomify is in development using WebGL and Emscripten. \\
-Geometry shaders \\
-Improved script editor with auto completion \\
-Moltemplate interface \\
+
+Atomify continues in heavy development and we have several features planned for
+future versions.
+A web version of Atomify using WebGL and WebAssembly will make it easy to test
+scripts in the browser.
+This is useful in educational settings where teachers wish to introduce students
+to LAMMPS without installing additional software.
+It will also serve as a nice demonstration of the full desktop application of
+Atomify.
+
+Performance improvements are planned by for instance using geometry shaders to
+generate periodic copies.
+Currently this is partially done on the CPU,
+which  reduces performance drastically.
+We also aim to include more backends, both using the CPU and GPU,
+in addition to running simulations on computing clusters while visualizing them
+on the users own computer.
+
+The script editor will get features such as autocompletion of LAMMPS commands
+and easy access to the online documentation by hovering or selecting specific
+commands.
+
+We are also working on including Moltemplate and other programs that generate
+systems to make it easier for users to get started with more complex
+simulations.
 
 \section{Availability}
+
+Atomify is availabe on Linux, MacOS and Windows and can be downloaded from
+\href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
+A lightweight version of the desktop application is also available for mobile
+devices running Android or iOS.
 

### 2017-06-16 ms.tex
Reordering figures

@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{flowchart.png}
-	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
-a) A LAMMPS script is written using a text editor.
-b) Simulation is performed from the terminal.
-c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
-Atomify simplifies the workflow by combining all steps into a single application.
-}
-	\label{fig:flowchart}
-\end{figure}
-
 Atomify solves combines script editing, simulation,
@@
     Overview of the Graphical User Interface (GUI) in Atomify.
-    The toolbar (1) provides changing
-    between editing, viewing and analyzing the running simulation,
+    The toolbar (1) is used to change between the different modes, such as 
+    editing, viewing and analyzing the running simulation, 
     in addition to playback controls.
@@
 \end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{flowchart.png}
+	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
+a) A LAMMPS script is written using a text editor.
+b) Simulation is performed from the terminal.
+c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
+Atomify simplifies the workflow by combining all steps into a single application.
+}
+	\label{fig:flowchart}
+\end{figure*}
+
 \section{Features}
@@
 
-Performance improvements are planned by for instance using geometry shaders to
-generate periodic copies.
-Currently this is partially done on the CPU,
-which  reduces performance drastically.
-We also aim to include more backends, both using the CPU and GPU,
-in addition to running simulations on computing clusters while visualizing them
-on the users own computer.
+Performance improvements are planned by for instance using geometry shaders in
+the rendering pipeline.
+This allows a fourfold reduction in the number of vertices passed from the CPU
+to the GPU.
+Further, geometry shaders can be used for certain modifiers,
+such as the periodic copies, which are currently performed on the CPU.
+
+% TODO Reference to KOKKOS
+We also aim to include more LAMMPS backends, such as KOKKOS, and running
+simulations on computing clusters while visualizing them on the users own
+computer.
 

### 2017-06-16 ms.tex
Added info on plotting and dashboard

@@
 
-Any operations that is applied to the system in a LAMMPS timestep or
-minimization step is called a ``fix''.
+Any operation that is applied to the system in a LAMMPS timestep or minimization
+step is called a ``fix''.
 These fixes are defined in the LAMMPS script using the ``fix'' keyword.
 Atomify registers all defined fixes and lists these in the dashboard.
-
-TODO: Time evolution of quantity \\
-TODO: 2d ave/chunk binning \\
 
@@
 interactions between the atoms.
-These can be plotted as a function of time and visualized while the 
-simulation is running.
-Quantities that are measured per atom can be plotted in a histogram.
-
-Atomify provides live visualization of the compute values using various plotting
-techniques.
-For instance, the temperature of the simulated system can be plotted as a
-function of time as seen in figure TODO.
-% TODO add figure
+Computes and variables are shown in the Atomify dashboard,
+along with information about the regions, groups and fixes as shown in figure
+\ref{fig:dashboard}.
 
@@
 
+Computes can be plotted as a function of time and visualized while the 
+simulation is running.
+Quantities that are measured per atom can be plotted in a histogram or a 2D
+average for each region.
+Atomify provides live visualization of the compute values using various plotting
+techniques.
+For instance, the temperature of the simulated system can be plotted as a
+function of time as seen in figure \ref{fig:temperature}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/temperature.png}
+	\caption{Atomify can visualize computes defined in LAMMPS. 
+    Here the temperature is plotted as a function of time.}
+	\label{fig:temperature}
+\end{figure}
+
 \section{Implementation}
 
-Atomify is built upon Qt.
-All GUI is defined in QML whereas the backend of the program communicating with
-LAMMPS is written in C++.
-High-performance visualization is achieved by implementing billboards in Qt3D.
-Simply put, Atomify runs an instance of a LAMMPS object enabling the user to
-visualize the current state of LAMMPS and interact with LAMMPS while the
-simulation is running.
+Atomify runs a LAMMPS instance in the background that the user can issue 
+commands to and visualizes the current atom positions and the LAMMPS state.
+The user can interact with LAMMPS while the simulation is running.
+Atomify is written in C++ and QML using the Qt framework.
+The GUI is developed in QML and LAMMPS communication,
+computations, and rendering is mostly defined in C++.
+High-performance visualization is implemented as billboards in Qt3D.
 
@@
 A common technique to overcome this problem is to use billboards.
-This significantly reduces the number of vertices sent from the CPU to the GPU,
-which in turn improves rendering performance.
+
+Billboards are plane objects that are always facing the camera (their normal
+vector always points from the billboard center towards the camera center).
+Drawing a filled circle on the billboard is a simple approximation to rendering
+spheres, but this approach suffers from unrealistic distortions from the field
+of view and does not make it possible to render realistic lighting.
+The more robust approach, which we have chosen,
+is to cast rays from the camera to the plane and calculate the sphere
+intersection of each ray.
+The normal vector can then be found by subtracting the intersection point from
+the sphere center.
+
+The technique of using billboards with only four vertices instead of a mesh
+approximating a sphere with many more vertices is often referred to as
+\emph{imposter spheres} in the literature.
+% TODO add reference to literature explaining the details of rendering spheres with imposter billboards
+This technique significantly reduces the number of vertices sent from the CPU to
+the GPU, which in turn improves rendering performance.
 A sphere may consist of an arbitrary number of vertices,
@@
 \section{Case study (Anders)}
-% Rerun on large dataset
+
+% TODO Write about case study
 

### 2017-06-16 ms.tex
Restructure implementation intro

@@
 
-Atomify runs a LAMMPS instance in the background that the user can issue 
-commands to and visualizes the current atom positions and the LAMMPS state.
-The user can interact with LAMMPS while the simulation is running.
+Atomify runs a LAMMPS instance in the background that it issues commands to.
+The current state and atom positions are extracted from this instance for
+visualization.
+This setup makes it possible for the user to interact with LAMMPS while the
+simulation is running.
 Atomify is written in C++ and QML using the Qt framework.
-The GUI is developed in QML and LAMMPS communication,
-computations, and rendering is mostly defined in C++.
+The GUI is written in QML, while LAMMPS communication,
+computations, and rendering is written in C++.
 High-performance visualization is implemented as billboards in Qt3D.

### 2018-05-30 ms.tex
Specification to availability
bleh

@@
 
-\title{Atomify - a live LAMMPS visualizer}
+\title{Increased productivity using Atomify - a real-time LAMMPS visualizer}
 \author{Anders Hafreager$^1$}
@@
 %
-The typical LAMMPS workflow includes working with a text editor to modify
-scripts, the terminal to run simulations, and programs like VMD or Ovito to
-visualize trajectories.
-If physical quantities are computed, the data is often plotted with MATLAB or
-Python, where additional scripts must be used.
-This is a tedious process, especially for teaching purposes and for people who
-are new to LAMMPS.
-We here introduce Atomify;
-a high performance live visualizer for LAMMPS simulations,
-with stunning graphics able to simulate and render more than 250,000 atoms with
-excellent frame rate on modern hardware.
-Atomify supports OpenMP and GPU acceleration, live plotting of LAMMPS variables
-and computes, and an easy-to-use code editor in one single program.
-Direct access to the powerful machinery already built into LAMMPS allows easy
-access to advanced physical quantities.
+The typical workflow when running atomistic simulations includes working with several programs.
+A text editor is needed to create and modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
+If physical quantities are computed, the data is often plotted with MATLAB or Python, where additional scripts must be used.
+This is a tedious process, especially for teaching purposes and for people who are new in the field.
+We here introduce Atomify; a high performance real-time visualizer for atomistic simulations that can simulate and render more than one million atoms with excellent frame rate on modern hardware.
+Atomify supports OpenMP acceleration, GPU acceleration, real-time plotting of physical quantities, and an easy-to-use code editor in one single application.
+It currently uses LAMMPS as physics engine, but it can be extended to support other codes like Gromacs, NAMD or OpenMM.
 Atomify is open-source software (GPL) written in C++ using the Qt framework.
@@
 %
-Molecular dynamics (MD) is a common technique for simulating the motion of atoms, molecules and larger particles in a broad range of fields such as physics, chemistry and biology \cite{flerefelt}.
+Molecular dynamics (MD) is a common technique for simulating the motion of atoms,
+molecules and larger particles in a broad range of fields such as physics, chemistry and biology \citep{van2001reaxff, allen2017computer, }.
 % TODO does MD also include larger particles?
@@
 available\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
-Some packages, such as LAMMPS\cite{Plimpton1995Fast}, GROMACS\cite{Pronk2013}
-and NAMD\cite{Phillips2005Scalable} have been developed for more than two decades 
+Some packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}
+and NAMD\citep{Phillips2005Scalable} have been developed for more than two decades 
 and contain more than one million lines of code each.
@@
 Particle trajectories can be saved to a file and visualized by tools such as
-VMD\cite{Humphrey1996Vmd} or OVITO\cite{Stukowski2009Visualization}.
+VMD\citep{Humphrey1996Vmd} or OVITO\citep{Stukowski2009Visualization}.
 The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the web page:
@@
 
-Atomify solves combines script editing, simulation,
-visualization, and analysis in one single software application.
+Atomify combines script editing, simulation,
+visualization, and analysis in one single application.
 It uses LAMMPS as a library and synchronizes after each timestep,
@@
 For a full list of the available commands, see the Atomify
-documentation\cite{atomifydocumentation}.
+documentation\citep{atomifydocumentation}.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.45\textwidth]{figures/temperature.png}
-	\caption{Atomify can visualize computes defined in LAMMPS. 
-    Here the temperature is plotted as a function of time.}
-	\label{fig:temperature}
-\end{figure}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.45\textwidth]{figures/temperature.png}
+% 	\caption{Atomify can visualize computes defined in LAMMPS. 
+%     Here the temperature is plotted as a function of time.}
+% 	\label{fig:temperature}
+% \end{figure}
 
@@
 the cross sectional area of the sphere of interest.
-This is illustrated in figure \ref{fig:billboards}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{spherebillboards.png}
-	\caption{Illustration of billboards.
-The circles are shown in the figure to show our target rendering.
-a) all 4 vertices are at the center of the sphere.
-b) the vertex shader moves each vertex so that the plane covers a larger cross sectional area than the sphere.
-c) the orientation of the plane is such that the normal vector of the plane is parallel to the view vector.
-}
-	\label{fig:billboards}
-\end{figure}
 
@@
 future versions.
-A web version of Atomify using WebGL and WebAssembly will make it easy to test
-scripts in the browser.
-This is useful in educational settings where teachers wish to introduce students
+We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
+This makes it easy to test scripts in the browser with all simple functionalities available.
+This is especially useful in educational settings where teachers wish to introduce students
 to LAMMPS without installing additional software.
@@
 simulations on computing clusters while visualizing them on the users own
-computer.
+computers.
 
@@
 \href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
-A lightweight version of the desktop application is also available for mobile
-devices running Android or iOS.
+A lightweight version of Atomify is also available for mobile devices running
+Android or iOS.
 

### 2018-06-01 ms.tex
Wrote more intro

@@
 \usepackage{menukeys}
-
+\usepackage{siunitx}
 \begin{document}
@@
 \section{Introduction}
-%
-Molecular dynamics (MD) is a common technique for simulating the motion of atoms,
-molecules and larger particles in a broad range of fields such as physics, chemistry and biology \citep{van2001reaxff, allen2017computer, }.
-% TODO does MD also include larger particles?
-% TODO which fields?
+Our nature is a very complex system with complicated rules that determine how and where mass, energy and momentum is transferred.
+Many macroscopic observable effects result from microscopic details on the atomic level such as melting of ice, and even life.
+Understanding the world from a bottom-up perspective requires us to be able to model a physical system from the atomic scale where the timescale is of order femtoseconds.
+Many physical and chemical processes happen on nanosecond timescales, some even during a few picoseconds, which means thousands or millions of timesteps of \SI{1}{\femto\second} need to be calculated.
+Much has happened since the first molecular dynamics simulation of hard spheres in the 1950s\citep{alder1957phase,alder1959studies}, and later, in 1964, a more realistic system with the Lennard Jones potential studying diffusion in argon\citep{rahman1964correlations}.
+The computing power has seen a tremendous increase from the CDC 3600 used in \citep{rahman1964correlations}, which performed less than 1 million instructions per second whereas modern 3 Ghz processors in typical laptops can do about 100 billion instructions per seconds.
+With this rapidly increase of computing power, the lengthscales and timescales achievable in numeriments\footnote{Numeriment is a numerical experiment, or a simulation on the computer.} is finally catching up with some experiments (ref).
+
+In molecular dynamics, a set of atoms is integrated using Newton's second law in a classical force field so the full phase space is known at all times and statistical properties can be calculated from averages assuming ergodicity.
+It has been prooved successful in reproducing and explaining multiple phenomenon such as mechanical properties \citep{jiang2009young, campbell1999structural, ning2012mechanical}, chemical reactions \citep{van2001reaxff, brenner2002second}, liquid properties\citep{allen2017computer}.
+Also in biology, molecular dynamics is useful blabla.
+
 Over the years, increasingly sophisticated methods have been developed.
-% TODO what methods?
-With the large number of force fields, advanced techniques and GPU acceleration,
-implementing a good molecular dynamics simulation is a challenging task.
-There are many software packages for molecular modelling
-available\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
-Some packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}
-and NAMD\citep{Phillips2005Scalable} have been developed for more than two decades 
-and contain more than one million lines of code each.
+For instance, a non-equilibrium method to measure thermal conductivity using heat exchange, was recently improved\citep{wirnsberger2015enhanced} to conserve energy better.
+To study first order phase transitions, methods like the generalized replica exchange method (gREM)\citep{kim2010generalized} can be used and nudge elastic band (NEB)\citep{henkelman2000climbing, henkelman2000improved} is often used to study energy barriers in for instance chemical reactions.
+In addition, a huge amount of force fields exists, each being good at different things.
+New hardware and a sea of optimization tricks makes implementing a good molecular dynamics code a challenging task, not to mention maintaining it over time on new arcitechtures.
+Each new feature or technique like the ones metioned above, may take days, if not weeks, to develop, preventing researchers to work on their scientific projects.
+
+Thanksfully, there already exists several software packages for atomistic simulations, many of which have been developed for more than two decades\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
+Some of these packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}, NAMD\citep{Phillips2005Scalable} and CHARMM\citep{brooks2009charmm}, are open source and being actively developed with hundreds of contributers.
+%After the rise of powerful graphical processing units (GPU's), most of these codes eventually added support of using accelerators\citep{brown2011implementing}.
 
 The work in this paper is focused on LAMMPS.
-Although the software is well-documented and enables the user to perform
+Although the software is well-documented\footnote{The documentation of LAMMPS is known for being very detailed precise.} and enables the user to perform
 advanced simulations, it can be demanding to learn how to use it well.
-A LAMMPS simulation is performed by a series of commands which are executed one by
-one.
-Physical quantities such as energy, temperature and stress can be measured by
-adding \textit{computes}.
+LAMMPS has a huge list of implemented features which makes it very flexible with its own scripting language.
+A LAMMPS simulation is performed by a series of commands which are executed one by one.
+
+Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
 The time evolution of these quantities can in turn be saved to file for plotting
@@
 \section{Features}
-
 The main features of Atomify are script editing,

### 2018-06-03 ms.tex
Wrote more intro

@@
 \documentclass[aps,pre,twocolumn,letterpaper,floatfix,nofootinbib]{revtex4}
+	% for \code color
+\usepackage[dvipsnames]{xcolor}
 \usepackage{graphicx} 
@@
 \usepackage{siunitx}
+\usepackage{listings}
+% Pretty formating of c++ (see \cpp command)
+\usepackage{xspace}
+\newcommand*{\cpp}{C\ensuremath{++}\xspace}
+
+\lstdefinelanguage{LAMMPS}{
+    morekeywords={units,atom_style,lattice,region,create_box,create_atoms,pair_style,pair_coeff,neigh_modify,mass,velocity,fix,run},
+    sensitive=false, % keywords are not case-sensitive
+    morecomment=[l]{//}, % l is for line comment
+    morecomment=[s]{/*}{*/}, % s is for start and end delimiter
+    morestring=[b]" % defines that strings are enclosed in double quotes
+}
+
+\lstset{
+numbers=left, 
+numberstyle=\small, 
+numbersep=8pt, 
+frame = single, 
+language=LAMMPS, 
+framexleftmargin=15pt,
+xleftmargin=0.65cm,
+xrightmargin=0.1cm}
+
+% Highlighte inline code
+\definecolor{light-gray}{gray}{0.95}
+%\newcommand{\code}[1]{\mbox {\texttt{#1}}}
+\newcommand{\code}[1]{\colorbox{light-gray}{\color{RawSienna}\texttt{#1}}}
+
 \begin{document}
@@
 \section{Introduction}
-Our nature is a very complex system with complicated rules that determine how and where mass, energy and momentum is transferred.
+Our nature is a very complex system with complicated rules that determine how, and where mass, energy and momentum is transferred.
 Many macroscopic observable effects result from microscopic details on the atomic level such as melting of ice, and even life.
@@
 
+\lstinputlisting[language=LAMMPS,caption={A minimal LAMMPS input script that simulates a Lennard Jones solid at reduced temperature $T^* = 1.0$ with a reduced density of $\rho^* = 0.8442$.},label={lst:simple.in}]{simple.in}
+
 The work in this paper is focused on LAMMPS.
-Although the software is well-documented\footnote{The documentation of LAMMPS is known for being very detailed precise.} and enables the user to perform
-advanced simulations, it can be demanding to learn how to use it well.
-LAMMPS has a huge list of implemented features which makes it very flexible with its own scripting language.
-A LAMMPS simulation is performed by a series of commands which are executed one by one.
+Although the software is well-documented\footnote{The LAMMPS documentation is known for being very detailed and precise.} and enables the user to perform advanced simulations, it can be demanding to learn how to use it well.
+The core principles of molecular dynamics is so simple that high school students can easily understand the concepts, but even undergraduate students may have problems with the terminology of statistical mechanics which is used in several of the commands.
+For instance, to simulate an \textit{NVE} simulation (constant number of particles $N$, volume $V$ and energy $E$), we use the \code{fix nve} command.
 
-Physical quantities such as energy, temperature and stress can be measured by adding \textit{computes}.
-The time evolution of these quantities can in turn be saved to file for plotting
-and further analysis.
-Particle trajectories can be saved to a file and visualized by tools such as
-VMD\citep{Humphrey1996Vmd} or OVITO\citep{Stukowski2009Visualization}.
-The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the web page:
-\url{http://lammps.sandia.gov/non_features.html}.} makes the workflow somewhat
-complicated, see figure \ref{fig:flowchart}.
+A LAMMPS simulation is performed by a series of commands, which are executed one by one.
+LAMMPS has a huge list of implemented features which makes it very flexible, especially with its own, powerful scripting language.
+In listing \ref{lst:simple.in}, we show an example of a minimalistic LAMMPS script that simulates 4000 Lennard Jones atoms in an FCC lattice with reduced temperature $T^*=1.0$ and reduced density $\rho^* = 0.8442$.
+This simulation does not print much thermodynamic data, but it creates a file \code{trajectory.bin} which containes the trajectory of all atoms at every timestep.
+Other programs such as VMD\citep{Humphrey1996Vmd} or OVITO\citep{Stukowski2009Visualization} can be used to visualize the file as a postprocessing step.
 
-Atomify combines script editing, simulation,
-visualization, and analysis in one single application.
-It uses LAMMPS as a library and synchronizes after each timestep,
-copying the relevant information from LAMMPS to the graphics processing unit
-(GPU) for visualization and data plotting.
-The visualization is optimized for high performance by raytracing billboards.
-This allows visualization of millions of atoms with good framerate on desktop
-computers. Atomify is designed with simplicity as main goal.
+If we want to measure physical quantities such as energy, temperature and stress, they can be accessed through a series of commands called \textit{computes}.
+For instance, the commands \code{compute ke} and \code{compute pe} measures the kinetic and the potential energy.
+Using \textit{fixes}, we can create time averages and save these quantities to one or more files for plotting and further analysis.
+We also often put atoms in different \textit{groups}, either by their position being in a \textit{region}, or their atom type or more advanced criteria.
+Performing different operations on different groups, or just measuring physical quantities on a specific group is then easily done since almost all commands have \code{group} as an input parameter.
 
-A simplified version of Atomify is made available for mobile platforms (Android
-and iOS).
-This version of Atomify provides access to some of the examples and is intended
-for exploration of molecular dynamics simulations by students.
-It also works as a demonstration of the visualization capabilities of the
-desktop version of the software.
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{flowchart.png}
+	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
+a) A LAMMPS script is written using a text editor.
+b) Simulation is performed from the terminal.
+c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
+Atomify simplifies the workflow by combining all steps into a single application.}
+	\label{fig:flowchart}
+\end{figure*}
+
+The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the LAMMPS web page: \url{http://lammps.sandia.gov/non_features.html}.}
+makes the workflow complicated, see figure \ref{fig:flowchart}.
+A simulation with full analysis usually involves writing the script in a text editor, running the simulation using the terminal before analysis is done with a visualization program and additional scripts written in MATLAB or Python.
+When creating a new simulation, the initial state (system box, positions of all particles, groups and regions) can be tricky to set up right, especially since groups and regions are not automatically written to the output file through the \code{dump} command.
+The time from an idea to a visual feedback can then be destructive for the creativity where immediate feedback would be ideal.
+
+We have solved this problem by creating Atomify, a real-time LAMMPS visualizer that combines script editing, simulation, visualization, and analysis in one single application.
+It uses LAMMPS as a library and hooks into the LAMMPS simulation cycle so synchronization of atom positions and physical quantities can be performed as often as every timestep.
+Most features of LAMMPS are automatically supported, except a few due to technical reasons discussed in section \ref{sec:future}.
+
+The visualization is performed using the powerful Qt3D library where advanced rendering techniques such as billboard raytracing is used to achieve maximum performance.
+This allows visualization of millions of atoms with good framerate on modern desktop computers.
+Atomify is designed with simplicity as its main goal.
+
+Since we have used the Qt framework to develop Atomify, and LAMMPS is written in object oriented \cpp, a simplified version is also made available on mobile platforms (Android and iOS).
+This version of Atomify provides access to some of the example simulations and is intended for exploration of molecular dynamics simulations by students and scientific outreach.
+It also works as a demonstration of the visualization capabilities of the desktop version of the software.
 The authors are optimistic that teachers can use the visualizations provided by
@@
 as thermodynamics, geophysics, and biology.
+
 \begin{figure*}
 	\centering
-	\includegraphics[width=0.95\textwidth]{gui.png}
+	\includegraphics[width=0.9\textwidth]{gui.png}
 	\caption{%
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{flowchart.png}
-	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
-a) A LAMMPS script is written using a text editor.
-b) Simulation is performed from the terminal.
-c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
-Atomify simplifies the workflow by combining all steps into a single application.
-}
-	\label{fig:flowchart}
-\end{figure*}
+In this paper we will go through a case study, an example simulation, where we
+use many of the useful features Atomify provides.
+We start by discussing the GUI in section \ref{sec:features} where the main features are summarized.
+In section \ref{sec:casestudy}, the case study is introduced where we go through a typical example
+of a simulation that uses regions and groups to perform different integration on different atoms.
+Details about how Atomify runs LAMMPS is found in section \ref{sec:implementation} where the data flow and the threading model is explained.
+Finally, we summarize the work in our paper in section \ref{sec:conclusion} with some thoughts about future outlooks in section \ref{sec:future}.
 
-\section{Features}
-The main features of Atomify are script editing,
-live visualization, and live plotting of computed quantities.
-In addition, Atomify comes packaged with multiple examples,
+\section{\label{sec:features}Summary of features}
+The main features of Atomify is summarized as script editing,
+real-time visualization and plotting of physical quantities.
+In addition, Atomify comes with multiple examples,
 many of which have been made by members of the LAMMPS community.
-These examples are easily explored within Atomify.
+It provides a lightweight script editor with syntax highlighting and line numbers.
 
-Atomify provides a lightweight script editor with syntax highlighting and line
-numbers.
-% TODO add built-in help and autocompletion to Atomify and mention here
 Multiple files can be open at the same time and the state persist across working sessions.
@@
 the default shortcut (\keys{Ctrl+R} in Windows and Linux or \keys{\cmd+R} in macOS).
-This enables you to quickly do changes in the script and see the changes immediately.
+This enables the user to get immediate visual feedback on changes in the script.
 
-Certain Atomify-commands can be added to the comments of a regular LAMMPS script
-to modify properties of the GUI.
-All these start with \keys{\texttt{\#}} so that LAMMPS ignores them as they are
-interpreted as comments.
-For instance, the color and size of the atoms can be set based on the type by
-the command \keys{\texttt{\#/atom}}.
-To set the color to white and radius to 2.0 for particle type 1,
-the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}.
-Certain built-in atom types have default values and can be accessed with
-\keys{\texttt{\#/atom 1 oxygen}} for simplicity.
-The initial camera position can also be set similarily.
-For a full list of the available commands, see the Atomify
-documentation\citep{atomifydocumentation}.
+\section{\label{sec:casestudy}Case study: flow through nanoporous media}
+Fluid flow is often characterized with permeability, the inverse flow resistance of a material.
+The permeability can be measured using Darcy's law when applying a pressure gradient.
 
-Atomify provides live visualization of particles in a simulation in its 3D view. 
-The particles can be colored based on any produced per-atom quantity in LAMMPS such as
-atom type, velocity, force or a variable formula.
-The coloring scheme can be changed while the simulation is running by hovering
-the mouse cursor over groups in the dashboard.
-Light colors and strength can also be changed in the dashboard.
-This will be described in further detail in the following section.
+Humans use an enormous amount of energy, most of which comes from chemical reactons in burning hydrocarbons.
+\todo{Short motivation about flow in nanoporous media}
 
-It is possible to organize particles in groups and regions in LAMMPS.
-These are shown in the dashboard in Atomify, which also provides controls to
-highlight or hide specific groups or regions.
-To highlight a group or region, the user only needs to hover the name in the
-dashboard.
-The visibility icon can be clicked to hide a group or region.
-
-Parameters for rendering, such as the light strength,
-attenuation, and color can be modified in the Rendering tab of the dashboard.
-See the above section about the script editor for information about how to
-modify the color of the particles.
-
-In LAMMPS, computes are computations performed on a group of atoms.
-Variables are user defined expressions which can be used to combine values in
-calculations.
-Once defined in a LAMMPS script, these can be plotted as a function of time in
-Atomify.
-This is done by clicking the name of the variable or compute in the simulation
-tab.
-We will explore plots in further detail in the following section.
-
-Any operation that is applied to the system in a LAMMPS timestep or minimization
-step is called a ``fix''.
-These fixes are defined in the LAMMPS script using the ``fix'' keyword.
-Atomify registers all defined fixes and lists these in the dashboard.
-
-In LAMMPS, computes are physical quantities calculated based on the running
-simulation, such as energy, temperature and stress.
-% TODO better word for measures?
-These are typically macroscopic measures derived from the microscopic
-interactions between the atoms.
-Computes and variables are shown in the Atomify dashboard,
-along with information about the regions, groups and fixes as shown in figure
-\ref{fig:dashboard}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.3\textwidth]{dashboard.png}
-	\caption{Dashboard}
-	\label{fig:dashboard}
-\end{figure}
-
-Computes can be plotted as a function of time and visualized while the 
-simulation is running.
-Quantities that are measured per atom can be plotted in a histogram or a 2D
-average for each region.
-Atomify provides live visualization of the compute values using various plotting
-techniques.
-For instance, the temperature of the simulated system can be plotted as a
-function of time as seen in figure \ref{fig:temperature}.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.45\textwidth]{figures/temperature.png}
-% 	\caption{Atomify can visualize computes defined in LAMMPS. 
-%     Here the temperature is plotted as a function of time.}
-% 	\label{fig:temperature}
-% \end{figure}
-
-\section{Implementation}
+\section{\label{sec:implementation}Implementation}
 
@@
 
-\section{Conclusion}
+\section{\label{sec:conclusion}Conclusion}
 %
@@
 
-\subsection{Future work}
+\section{\label{sec:future}Future work}
 

### 2018-06-03 old_features.tex
Wrote more intro

Certain Atomify-commands can be added to the comments of a regular LAMMPS script
to modify properties of the GUI.
All these start with \keys{\texttt{\#}} so that LAMMPS ignores them as they are
interpreted as comments.
For instance, the color and size of the atoms can be set based on the type by
the command \keys{\texttt{\#/atom}}.
To set the color to white and radius to 2.0 for particle type 1,
the user can apply the command \keys{\texttt{\#/atom 1 2.0 \#ffffff}}.
Certain built-in atom types have default values and can be accessed with
\keys{\texttt{\#/atom 1 oxygen}} for simplicity.
The initial camera position can also be set similarily.
For a full list of the available commands, see the Atomify
documentation\citep{atomifydocumentation}.

Atomify provides live visualization of particles in a simulation in its 3D view. 
The particles can be colored based on any produced per-atom quantity in LAMMPS such as
atom type, velocity, force or a variable formula.
The coloring scheme can be changed while the simulation is running by hovering
the mouse cursor over groups in the dashboard.
Light colors and strength can also be changed in the dashboard.
This will be described in further detail in the following section.

It is possible to organize particles in groups and regions in LAMMPS.
These are shown in the dashboard in Atomify, which also provides controls to
highlight or hide specific groups or regions.
To highlight a group or region, the user only needs to hover the name in the
dashboard.
The visibility icon can be clicked to hide a group or region.

Parameters for rendering, such as the light strength,
attenuation, and color can be modified in the Rendering tab of the dashboard.
See the above section about the script editor for information about how to
modify the color of the particles.

In LAMMPS, computes are computations performed on a group of atoms.
Variables are user defined expressions which can be used to combine values in
calculations.
Once defined in a LAMMPS script, these can be plotted as a function of time in
Atomify.
This is done by clicking the name of the variable or compute in the simulation
tab.
We will explore plots in further detail in the following section.

Any operation that is applied to the system in a LAMMPS timestep or minimization
step is called a ``fix''.
These fixes are defined in the LAMMPS script using the ``fix'' keyword.
Atomify registers all defined fixes and lists these in the dashboard.

In LAMMPS, computes are physical quantities calculated based on the running
simulation, such as energy, temperature and stress.
% TODO better word for measures?
These are typically macroscopic measures derived from the microscopic
interactions between the atoms.
Computes and variables are shown in the Atomify dashboard,
along with information about the regions, groups and fixes as shown in figure
\ref{fig:dashboard}.

\begin{figure}
	\centering
	\includegraphics[width=0.3\textwidth]{dashboard.png}
	\caption{Dashboard}
	\label{fig:dashboard}
\end{figure}

Computes can be plotted as a function of time and visualized while the 
simulation is running.
Quantities that are measured per atom can be plotted in a histogram or a 2D
average for each region.
Atomify provides live visualization of the compute values using various plotting
techniques.
For instance, the temperature of the simulated system can be plotted as a
function of time as seen in figure \ref{fig:temperature}.

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.45\textwidth]{figures/temperature.png}
% 	\caption{Atomify can visualize computes defined in LAMMPS. 
%     Here the temperature is plotted as a function of time.}
% 	\label{fig:temperature}
% \end{figure}

### 2018-06-03 ms.tex
Wrote a bit about case study

@@
 \definecolor{light-gray}{gray}{0.95}
+\definecolor{atomify-red}{rgb}{0.90196078 , 0.09803922, 0.29411765}
+\definecolor{atomify-green}{rgb}{0.23529412 , 0.70588235, 0.29411765}
+\definecolor{atomify-yellow}{rgb}{0.8,  0.70588235,  0.07843138}
+\definecolor{atomify-blue}{rgb}{0.00000000 , 0.50980392, 0.78431373}
 %\newcommand{\code}[1]{\mbox {\texttt{#1}}}
@@
 of a simulation that uses regions and groups to perform different integration on different atoms.
+Common pitfalls which are easily picked up with Atomify are shown.
 Details about how Atomify runs LAMMPS is found in section \ref{sec:implementation} where the data flow and the threading model is explained.
@@
 \section{\label{sec:casestudy}Case study: flow through nanoporous media}
+\todo{Short motivation about flow in nanoporous media with references}
 Fluid flow is often characterized with permeability, the inverse flow resistance of a material.
 The permeability can be measured using Darcy's law when applying a pressure gradient.
+However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel.
+This is a good approximation for liquids in large pores, but if the channel diameter $L$ is similar or smaller than the mean free path of the fluid $\lambda$, this is no longer the case.
+The Knudsen number, $\text{Kn} = \lambda / L$ quantifies this and can be used with the Klinkenberg correction to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
 
-Humans use an enormous amount of energy, most of which comes from chemical reactons in burning hydrocarbons.
-\todo{Short motivation about flow in nanoporous media}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
+	\caption{
+		Initial configuration in our case study simulation.
+		A periodic box consisting of $(40\times20\times20)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder of 5 unit cell radius.
+		The different colors indicate the regions of which different integration rules apply.
+		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
+		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
+		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} atoms (gas atoms) have an applied constant acceleration representing the pressure gradient.
+		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
+    }
+	\label{fig:cylinder_simulation}
+\end{figure}
+
+In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas with varying density to observe the slip velocity effect at low densities.
+We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
+Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$
+\begin{align}
+	a = \frac{\nabla P}{\rho_m},
+\end{align}
+where $\rho_m$ is the mass density of the gas atoms.
+Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
+We want to couple the solid to an external heat bath so the added energy can be transferred out through a thermostat.
+Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
+We therefore freeze the outmost atoms.
+To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:
+
+\begin{itemize}  
+	\item $r \leq 5$: applied pressure gradient
+	\item $5 < r \leq 9$: regular time integration
+	\item $9 < r \leq 12$: Dissipative Langevin thermostat
+	\item $12 < r$: frozen.
+\end{itemize}
 

### 2018-06-03 ms.tex
Some more?

@@
 		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
-		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} atoms (gas atoms) have an applied constant acceleration representing the pressure gradient.
+		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
 		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
@@
 We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
-Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$
+Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
 \begin{align}
@@
 \end{itemize}
+
+\subsection{Creating the initial geometry}
+We create a new script in Atomify using \keys{\cmd+R}, and save it (\keys{\cmd+S}) as \code{run.in}.
+Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times20\times20)$ unit cells.
+Then, to define the inner cylinder, we first specify the radius and the center before the region command:
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	variable R equal $(ly*0.25)
+	variable c equal $(ly*0.5)
+	region cylinder1 cylinder x $c $c $R EDGE EDGE
+\end{lstlisting}
+which gives
 

### 2018-06-05 ms.tex
Wrote more case study

@@
 \usepackage{epstopdf}
-\usepackage{todo}
+\usepackage{todonotes}
 \usepackage{menukeys}
@@
 To study first order phase transitions, methods like the generalized replica exchange method (gREM)\citep{kim2010generalized} can be used and nudge elastic band (NEB)\citep{henkelman2000climbing, henkelman2000improved} is often used to study energy barriers in for instance chemical reactions.
-In addition, a huge amount of force fields exists, each being good at different things.
+In addition, a huge amount of force fields exists, each being good at different properties\footnote{Some force fields are good at reproducing mechanical properties while others may be good at chemical reactions.
+This usually depends on what properties the force field was fitted to.}.
 New hardware and a sea of optimization tricks makes implementing a good molecular dynamics code a challenging task, not to mention maintaining it over time on new arcitechtures.
@@
 
-Thanksfully, there already exists several software packages for atomistic simulations, many of which have been developed for more than two decades\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
+Thankfully, there already exists several software packages for atomistic simulations, many of which have been developed for more than two decades\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
 Some of these packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}, NAMD\citep{Phillips2005Scalable} and CHARMM\citep{brooks2009charmm}, are open source and being actively developed with hundreds of contributers.
@@
 \section{\label{sec:features}Summary of features}
-The main features of Atomify is summarized as script editing,
+The main features of Atomify can be summarized as script editing,
 real-time visualization and plotting of physical quantities.
+This turns out to improve the workflow substantially.
 In addition, Atomify comes with multiple examples,
 many of which have been made by members of the LAMMPS community.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/rightbar.pdf}
+	\caption{
+		The rightbar is a powerful feature in Atomify where relevant
+		properties from LAMMPS is presented real-time.
+		In a), a list of all groups defined is shown with the current atom count.
+		b) shows all defined regions. Each group and region can be hovered so that atoms
+		are colored after what group / region they are in. If an atom is in multiple
+		groups or regions, they will get the color of the latest one defined.
+		The color boxes can be clicked which will either always highlight the atoms in a certain group or region,
+		or if clicked again, hide all of them.
+		In c) and d), a list of all variables and computes is shown. If a variable or compute
+		produces a scalar, the current value is shown as can be seen with all the variables.
+		By clicking the name, a plot will show up showing the time evolution of that quantity.
+		If a per-atom variable or compute is hovered, all atoms will be colored according to their
+		current scalar value and a histogram over these values is shown if clicked.
+		The result of hovering atoms defined by the groups in our case study is shown in figure \ref{fig:cylinder_simulation}.
+    }
+	\label{fig:rightbar}
+\end{figure}
+
 It provides a lightweight script editor with syntax highlighting and line numbers.
-
 Multiple files can be open at the same time and the state persist across working sessions.
@@
 \todo{Short motivation about flow in nanoporous media with references}
-Fluid flow is often characterized with permeability, the inverse flow resistance of a material.
+Fluid flow in porous media is often characterized with permeability, the inverse flow resistance of a material.
 The permeability can be measured using Darcy's law when applying a pressure gradient.
-However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel.
+However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel. (ref)
 This is a good approximation for liquids in large pores, but if the channel diameter $L$ is similar or smaller than the mean free path of the fluid $\lambda$, this is no longer the case.
@@
 
-In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas with varying density to observe the slip velocity effect at low densities.
-We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
+In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas inside a nanotube with varying density to observe the slip velocity effect at low densities.
+We will create the nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
 Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
@@
 \subsection{Creating the initial geometry}
-We create a new script in Atomify using \keys{\cmd+R}, and save it (\keys{\cmd+S}) as \code{run.in}.
+We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
 Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times20\times20)$ unit cells.
-Then, to define the inner cylinder, we first specify the radius and the center before the region command:
+Then, to define the inner cylinder, we first specify the radius and the center before using the region command:
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 \end{lstlisting}
-which gives
+The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
+As shown in figure \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
+When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in figure \ref{fig:initial_configuration}a.
+The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
+Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command which gives the desired result in figure  \ref{fig:initial_configuration}b.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/initial_configuration.pdf}
+	\caption{
+		Several snapshots of the process of creating the simulation in our case study.
+		The wrongly placed cylinder is shown in a) whereas it is placed correctly in b).
+    }
+	\label{fig:initial_configuration}
+\end{figure}
+
+We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in lammps with \code{variable V equal PI*v\_R*v\_R*lx}.
+In these units, we have chosen that the atomic mass is 1 so number density $\rho$ equals the mass density $\rho_m$.
+The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed}, where we need to specify the fraction of the existing atoms in that region we want to delete.
+To count the number of atoms inside a region, we first create a group containing all the atoms in the region and then create a variable that counts them.
+Assuming a density $\rho = 0.05$, we can calculate the expected number inside the cylinder as $N = V\rho$.
+The atoms inside the region can now be deleted. These steps can be done in LAMMPS like this
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	group cylinder1 region cylinder1
+	variable N_cyl equal count(cylinder1)
+	variable V equal PI*v_R*v_R*lx
+	variable rho equal 0.1
+	variable N_wanted equal $V*${rho}
+	variable delete_fraction equal (${N_cyl}-${N_wanted})/${N_cyl}
+	delete_atoms porosity cylinder1 ${delete_fraction} 1234
+\end{lstlisting}
+and the result is shown in figure \ref{fig:initial_configuration}c.
+
+The next step now is to create the larger cylinder, containing the red atoms in figure \ref{fig:cylinder_simulation} where regular time integration will take place.
 

### 2018-06-05 ms.tex
Wrote more case study

@@
 \lstdefinelanguage{LAMMPS}{
-    morekeywords={units,atom_style,lattice,region,create_box,create_atoms,pair_style,pair_coeff,neigh_modify,mass,velocity,fix,run},
+    morekeywords={units,atom_style,lattice,region,create_box,create_atoms,pair_style,pair_coeff,neigh_modify,mass,velocity,fix,run, group every, equal, count, porosity, EDGE},
     sensitive=false, % keywords are not case-sensitive
@@
 		Several snapshots of the process of creating the simulation in our case study.
+		This shows how one typically generate a geometry step by step where the immediate
+		feedback is very useful to quickly discover mistakes.
 		The wrongly placed cylinder is shown in a) whereas it is placed correctly in b).
+		c) shows how the system looks after deleting atoms to obtain $\rho = 0.01$. The next cylinder $C_2$ is shown in d),
+		and all regions (placed in groups) are shown in e). Here we have uniquely defined the purple shell which should have a dissipative thermostat.
+		In f), the list of all groups defined in this system is shown with colors matching those of e). All figures are rendered with Atomify.
     }
@@
 \end{figure}
-
 We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in lammps with \code{variable V equal PI*v\_R*v\_R*lx}.
@@
 
-The next step now is to create the larger cylinder, containing the red atoms in figure \ref{fig:cylinder_simulation} where regular time integration will take place.
+The next step now is to create a larger cylinder, the one containing the red atoms in figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
+This cylinder should have a slightly bigger radius as stated above and can be created with another region command:
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	region cylinder2 cylinder x $c $c $(v_R+4) EDGE EDGE
+\end{lstlisting}
+The expected result as can be seen in figure \ref{fig:initial_configuration}d.
+Now we have the inner cylinder with the gas atoms defined as a region and the next cylinder shell (including the gas atoms) defined as another region.
+We now want to create another shell, the one with the dissipative thermostat.
+All the atoms with the dissipative thermostat, the inner shell and the gas will be integrated with the \code{fix nve} integrator.
+Therefore, we create a slightly larger cylinder which will be the one defining the group for \code{fix nve}.
+We can also define the groups with these cylinders
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	region cylinder3 cylinder x $c $c $(v_R+7) EDGE EDGE
+	group cylinder1 region cylinder1
+	group cylinder2 region cylinder2
+	group cylinder3 region cylinder3
+	group nve region cylinder3
+\end{lstlisting}
+where we also have created the group \code{nve} for clarity.
+
+The dissipative thermostat will be \code{fix langevin}\citep{schneider1978molecular}, but it should only be applied on the outer shell defined by $C_3 \setminus C_2$,
+where $C_i$ is the set containing the atoms inside cylinder $i$.
+We can obtain this with the command
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	group langevin subtract cylinder3 cylinder2
+	group frozen subtract all cylinder3
+	group gas dynamic all region cylinder1 every 1
+\end{lstlisting}
+which will contain only the outer shell. 
+We here also created the group \code{frozen}, which is the outmost atoms, and the group \code{gas} which is dynamic since atoms may switch places and we want to only apply a force on the ones in the inner cylinder at any point in time.
+The frozen atoms will not move at all and make sure that the system does not start moving due to momentum transfer from the gas particles through the solid.
+All these groups are highlighted in figure \ref{fig:initial_configuration}e by hovering the box containing all the groups. in Atomify as shown in figure \ref{fig:initial_configuration}f.
+The colors of the atoms matches the group color next to the group name in figure \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
+Therefore we see no green atoms (\code{cylinder1}) since all of these are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas}.
 

### 2018-06-05 ms.tex
Wrote even more case study

@@
 The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the LAMMPS web page: \url{http://lammps.sandia.gov/non_features.html}.}
-makes the workflow complicated, see figure \ref{fig:flowchart}.
+makes the workflow complicated, see Fig. \ref{fig:flowchart}.
 A simulation with full analysis usually involves writing the script in a text editor, running the simulation using the terminal before analysis is done with a visualization program and additional scripts written in MATLAB or Python.
@@
 		current scalar value and a histogram over these values is shown if clicked.
-		The result of hovering atoms defined by the groups in our case study is shown in figure \ref{fig:cylinder_simulation}.
+		The result of hovering atoms defined by the groups in our case study is shown in Fig. \ref{fig:cylinder_simulation}.
     }
@@
 This is a good approximation for liquids in large pores, but if the channel diameter $L$ is similar or smaller than the mean free path of the fluid $\lambda$, this is no longer the case.
-The Knudsen number, $\text{Kn} = \lambda / L$ quantifies this and can be used with the Klinkenberg correction to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
+The Knudsen number, $\text{Kn} = \lambda / L$ quantifies this and can be used with the Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
 
@@
 In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas inside a nanotube with varying density to observe the slip velocity effect at low densities.
-We will create the nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
+We will create the nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see Fig.
+\ref{fig:cylinder_simulation}.
 Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
@@
 Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times20\times20)$ unit cells.
-Then, to define the inner cylinder, we first specify the radius and the center before using the region command:
+Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later anyway).
+We will modify this script to achieve what we described above, so we need to make sure that these commands happen \textit{before} the \code{run 1000} command in the script.
+If not, LAMMPS will not execute them before we start visualizing.
+To define the inner cylinder, we first specify the radius and the center before using the region command
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
-As shown in figure \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
-When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in figure \ref{fig:initial_configuration}a.
+We now press \keys{\cmd+R} to run the simulation to see how it looks.
+As shown in Fig. \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
+When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in Fig. \ref{fig:initial_configuration}a.
 The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
-Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command which gives the desired result in figure  \ref{fig:initial_configuration}b.
+To discover mistakes like this is quickly done with Atomify.
+Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command, rerun the simulation with \keys{\cmd+R} which gives the desired result in figure  \ref{fig:initial_configuration}b.
 
@@
 \end{lstlisting}
-and the result is shown in figure \ref{fig:initial_configuration}c.
+and the result is shown after rerunning again with \keys{\cmd+R}, see Fig. \ref{fig:initial_configuration}c.
+This is a powerful workflow Atomify enables where very quick changes can be tested with immediate feedback.
+Every time we add a new command, we just rerun with \keys{\cmd+R} to see what happens.
 
-The next step now is to create a larger cylinder, the one containing the red atoms in figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
+The next step now is to create a larger cylinder, the one containing the red atoms in Fig. \ref{fig:cylinder_simulation}, where regular time integration will take place.
 This cylinder should have a slightly bigger radius as stated above and can be created with another region command:
@@
 \end{lstlisting}
-The expected result as can be seen in figure \ref{fig:initial_configuration}d.
+Again press \keys{\cmd+R} and see the expected result in Fig. \ref{fig:initial_configuration}d.
+
 Now we have the inner cylinder with the gas atoms defined as a region and the next cylinder shell (including the gas atoms) defined as another region.
@@
 We can obtain this with the command
+
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 \end{lstlisting}
+
 which will contain only the outer shell. 
@@
 The frozen atoms will not move at all and make sure that the system does not start moving due to momentum transfer from the gas particles through the solid.
-All these groups are highlighted in figure \ref{fig:initial_configuration}e by hovering the box containing all the groups. in Atomify as shown in figure \ref{fig:initial_configuration}f.
-The colors of the atoms matches the group color next to the group name in figure \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
-Therefore we see no green atoms (\code{cylinder1}) since all of these are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas}.
+All these groups are highlighted in Fig. \ref{fig:initial_configuration}e by hovering the box containing all the groups. in Atomify as shown in Fig. \ref{fig:initial_configuration}f.
+The colors of the atoms matches the group color next to the group name in Fig. \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
+We there don't any green atoms (\code{cylinder1}) since all of these are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas}.
+
+\subsection{Physical setup}
+Now that we have achieved to set up the system geometrically, that is, all the different groups of atoms are defined.
+We only need to apply the different actions, or fixes, on them.
+First, we apply the time integration \code{fix nve} which should happen on all atoms within $C_3$, then the thermostat \code{fix langevin}
+
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	fix nve nve nve
+	fix langevin langevin langevin 1.0 1.0 1.0 12345
+	compute displacement all displace/atom
+\end{lstlisting}
+
+The syntax for fixes is \code{fix ID groupID style args}, so the above fixes has the same name as both the groups and the fix style.
+\code{fix langevin} takes at least 4 arguments \textit{Tstart, Tstop, Tdamp, seed}, i.e.
+the temperature in the beginning of a simulation, the temperature at the end (timesteps in between get a linearly interpolated temperature between these values), a damping parameter which controls how strongly the thermal bath interacts with the system.
+It also needs a random seed due to the random nature of the Langevin thermostat, see \citep{schneider1978molecular} for details.
+Finally, we have added another compute that measures the displacement per atom.
+Hovering this compute in the list will color each atom according to their displacement since $t=0$.
+
+By rerunning again (\keys{\cmd+R}), we can confirm that the system behaves as expected.
+In Fig. \ref{fig:moving_atoms}, we see that the outmost atoms are completely frozen (dark blue), the ones in the solid are also blue, but brighter, since they vibrate thermally in the lattice.
+The inner cylinder contains gas atoms which move more freely, as seen from the colors being in the upper part of the color map.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{lj_flow/07_moving.png}
+	\caption{
+		We see the expected moving atoms inside the $C_3$ cylinder.
+		The atoms are colored based on their displacement (measured in reduced length units).
+		We confirm that the outmost atoms are frozen, which we read from dark blue color mapping to 0 displacement.
+		The moving atoms in the solid are blue, but brighter than the frozen ones which is expected due to their thermal vibrations.
+		Inside the inner cylinder we see that the gas moves more freely since these atoms are not bounded.
+    }
+	\label{fig:moving_atoms}
+\end{figure}
+
+The only remaining part now is to set up the commands that will measure the physical quantities like the radial velocity profile.
+
+\subsection{Measurement setup}
+We will use the built-in binning feature in LAMMPS called chunks, a very general concept where you assign a \code{chunkID} to each atom
+based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
+In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc), but also the binsize in the length direction and how many radial bins we want.
+We only want one bin in the flow direction since we will measure the radial velocity profile only.
+The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line.}
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	compute chunk all chunk/atom bin/cylinder x lower &
+	$(lx) $c $c 0 $R 30 units box
+\end{lstlisting}
+See the documentation for details about this command, but note that the binsize in the length direction is equal to the system length so we only get one bin.
+It will create 30 radial bins for $r\in (0, R)$, where $R$ is the radius of the inner cylinder.
+The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
+To obtain this, we simply use
+\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+	fix vx all ave/chunk 10 10 100 chunk vx ave running
+\end{lstlisting}
+Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a large histogram.
+This fix will appear in the list of fixes in the rightbar just as groups, regions, computes and variables.
+When we click it, we will get the figure shown in Fig. \ref{fig:velocity_profile1}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{lj_flow/08_velocity_profile1.png}
+	\caption{
+		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 8.7 (reduced units).
+		Since the wall also is made of Lennard Jones atoms, some of the wall atoms 
+		This figure is made using the Atomify real-time plotter which can show any scalar value defined in LAMMPS
+		as compute, fix or variable.
+    }
+	\label{fig:velocity_profile1}
+\end{figure}
+
+\subsection{Results}
+
+\begin{figure}
+	\centering
+	% \includegraphics[width=0.5\textwidth]{lj_flow/07_moving.png}
+	\caption{
+		Velocity profiles for different densities.
+		The step flow shape is evident for low density gases with a high non-zero slip velocity.
+		When the density increases, the slip velocity goes to zero as expected.
+    }
+	\label{fig:velocity_profiles}
+\end{figure}
+
+We conclude this case study with a series of simulations of the system described above for different densities.
+Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in Fig. \ref{fig:velocity_profile1}.
+All these plots are now merged into a final figure which is shown in Fig. \ref{fig:velocity_profiles}.
+It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
+As mentioned earlier, this is called the Klinkenberg effect \citep{klinkenberg1941permeability}.
 
@@
 By doing proper shading, the billboards can mimick the spheres and cylinders so
-they look realistic, see Figure \ref{fig:final_billboards}.
+they look realistic, see Fig. \ref{fig:final_billboards}.
 

### 2018-06-05 ms.tex
Fixed intro stuff

@@
 
-In molecular dynamics, a set of atoms is integrated using Newton's second law in a classical force field so the full phase space is known at all times and statistical properties can be calculated from averages assuming ergodicity.
-It has been prooved successful in reproducing and explaining multiple phenomenon such as mechanical properties \citep{jiang2009young, campbell1999structural, ning2012mechanical}, chemical reactions \citep{van2001reaxff, brenner2002second}, liquid properties\citep{allen2017computer}.
-Also in biology, molecular dynamics is useful blabla.
+In molecular dynamics, a set of atoms is integrated using Newton's second law in a classical force field so the full coordinate in the phase space is known at all times, and statistical properties can be calculated from averages assuming ergodicity\citep{martyna1994constant}.
+The model has been proved successful in reproducing and explaining many phenomenon such as mechanical properties \citep{jiang2009young, campbell1999structural, ning2012mechanical}, chemical reactions \citep{van2001reaxff, brenner2002second}, liquid properties\citep{allen2017computer}.
+Also in biology, molecular dynamics is useful blabla. \todo{Add more nice references here}
 
 Over the years, increasingly sophisticated methods have been developed.
-For instance, a non-equilibrium method to measure thermal conductivity using heat exchange, was recently improved\citep{wirnsberger2015enhanced} to conserve energy better.
-To study first order phase transitions, methods like the generalized replica exchange method (gREM)\citep{kim2010generalized} can be used and nudge elastic band (NEB)\citep{henkelman2000climbing, henkelman2000improved} is often used to study energy barriers in for instance chemical reactions.
+For instance, a non-equilibrium method to measure thermal conductivity using heat exchange, was recently improved\citep{wirnsberger2015enhanced} to conserve energy better than the previous method\citep{ikeshoji1994non}.
+To study first order phase transitions, methods like the generalized replica exchange method (gREM)\citep{kim2010generalized} can be used, and nudge elastic band (NEB)\citep{henkelman2000climbing, henkelman2000improved} is often used to study energy barriers in for instance chemical reactions.
 In addition, a huge amount of force fields exists, each being good at different properties\footnote{Some force fields are good at reproducing mechanical properties while others may be good at chemical reactions.
 This usually depends on what properties the force field was fitted to.}.
-New hardware and a sea of optimization tricks makes implementing a good molecular dynamics code a challenging task, not to mention maintaining it over time on new arcitechtures.
-Each new feature or technique like the ones metioned above, may take days, if not weeks, to develop, preventing researchers to work on their scientific projects.
+New hardware and a sea of optimization tricks makes implementing a good molecular dynamics code a challenging task, not to mention maintaining it over time when new arcitechtures are being released.
+Each new feature or technique may take days, if not weeks, to develop, preventing researchers to work on their scientific projects.
 

### 2018-06-05 ms.tex
Fixed simulation and intro language

@@
 Thankfully, there already exists several software packages for atomistic simulations, many of which have been developed for more than two decades\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
-Some of these packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}, NAMD\citep{Phillips2005Scalable} and CHARMM\citep{brooks2009charmm}, are open source and being actively developed with hundreds of contributers.
+Some of these packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}, NAMD\citep{Phillips2005Scalable} and CHARMM\citep{brooks2009charmm}, are open source and being actively developed with hundreds of contributers\footnote{See their repositories on i.e.
+GitHub for an overview of contributers.}.
 %After the rise of powerful graphical processing units (GPU's), most of these codes eventually added support of using accelerators\citep{brown2011implementing}.
@@
 The work in this paper is focused on LAMMPS.
-Although the software is well-documented\footnote{The LAMMPS documentation is known for being very detailed and precise.} and enables the user to perform advanced simulations, it can be demanding to learn how to use it well.
+Although the software is well-documented\footnote{The LAMMPS documentation is known for being very detailed and precise.}, and enables the user to perform advanced simulations, it can be a demanding task to learn how to use it well.
 The core principles of molecular dynamics is so simple that high school students can easily understand the concepts, but even undergraduate students may have problems with the terminology of statistical mechanics which is used in several of the commands.
-For instance, to simulate an \textit{NVE} simulation (constant number of particles $N$, volume $V$ and energy $E$), we use the \code{fix nve} command.
+For instance, to simulate an \textit{NVE} simulation (constant number of particles $N$, volume $V$ and energy $E$), we use the \code{fix nve} command which defines the time integration.
 
@@
 
-If we want to measure physical quantities such as energy, temperature and stress, they can be accessed through a series of commands called \textit{computes}.
+If we want to measure physical quantities such as energy, temperature and stress, they can be accessed through commands called \textit{computes}.
 For instance, the commands \code{compute ke} and \code{compute pe} measures the kinetic and the potential energy.
-Using \textit{fixes}, we can create time averages and save these quantities to one or more files for plotting and further analysis.
+Using \textit{fixes}, we can create time averages and save them to one or more files for plotting and further analysis.
 We also often put atoms in different \textit{groups}, either by their position being in a \textit{region}, or their atom type or more advanced criteria.
 Performing different operations on different groups, or just measuring physical quantities on a specific group is then easily done since almost all commands have \code{group} as an input parameter.
+With this flexibility, it may be difficult to do everything right immediately.
+Complicated regions and group defines are often necessary to perform the intended simulation, and a lot of time can be spent in the prototyping process, especially since information about groups and regions are not automatically written to a trajectory file.
+A simulation typically involves writing the LAMMPS script in a text editor before the simulation is performed in the terminal for a while before the trajectories and time series are studied to verify the correctness which often turn out to be bad.
+Plotting of time series also requires the user to write a script in i.e. Python or MATLAB which does the plotting, but these steps are often performed manually.
 
@@
 The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the LAMMPS web page: \url{http://lammps.sandia.gov/non_features.html}.}
-makes the workflow complicated, see Fig. \ref{fig:flowchart}.
-A simulation with full analysis usually involves writing the script in a text editor, running the simulation using the terminal before analysis is done with a visualization program and additional scripts written in MATLAB or Python.
-When creating a new simulation, the initial state (system box, positions of all particles, groups and regions) can be tricky to set up right, especially since groups and regions are not automatically written to the output file through the \code{dump} command.
+makes this workflow complicated, see Fig. \ref{fig:flowchart}.
 The time from an idea to a visual feedback can then be destructive for the creativity where immediate feedback would be ideal.
@@
 
-The visualization is performed using the powerful Qt3D library where advanced rendering techniques such as billboard raytracing is used to achieve maximum performance.
+The visualization is performed using the powerful Qt3D library where we have implemented advanced rendering techniques such as billboard raytracing to achieve maximum performance.
 This allows visualization of millions of atoms with good framerate on modern desktop computers.
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{gui.png}
+	\includegraphics[width=\textwidth]{gui.png}
 	\caption{%
@@
 \section{\label{sec:casestudy}Case study: flow through nanoporous media}
-\todo{Short motivation about flow in nanoporous media with references}
+The features of Atomify is best presented through a case study where many of the features are useful to be productive in the script development.
+We have chosen to create a system with fluid flow inside a tight nanochannel.
+This involves creating a somewhat complicated initial geometry with multiple regions where we apply different tricks such as dissipative thermostats, constant force mimicking applied pressure gradient and frozen atoms to avoid net momentum of the solid.
+
 Fluid flow in porous media is often characterized with permeability, the inverse flow resistance of a material.
@@
 However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel. (ref)
-This is a good approximation for liquids in large pores, but if the channel diameter $L$ is similar or smaller than the mean free path of the fluid $\lambda$, this is no longer the case.
-The Knudsen number, $\text{Kn} = \lambda / L$ quantifies this and can be used with the Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
+This is a good approximation for liquids in larger pores, but if the channel size $R$ is of the same order, or larger, as the mean free path $\lambda$ of the fluid, this is no longer true. (ref)
+The Knudsen number, $\text{Kn} = \lambda / R$ quantifies this and can be used to apply Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
 
@@
 		Initial configuration in our case study simulation.
-		A periodic box consisting of $(40\times20\times20)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder of 5 unit cell radius.
+		A periodic box consisting of $(40\times25\times25)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 10 (reduced length).
 		The different colors indicate the regions of which different integration rules apply.
@@
 In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas inside a nanotube with varying density to observe the slip velocity effect at low densities.
-We will create the nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see Fig.
+We will create the nanotube inside a Lennard Jones solid of size  $(40\times25\times25)$ unit cells with reduced density $\rho^* = 0.8442$.
+The fluid in the nanochannel, or cylinder, will flow due to an induced pressure gradient, see Fig.
 \ref{fig:cylinder_simulation}.
@@
 Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
-We want to couple the solid to an external heat bath so the added energy can be transferred out through a thermostat.
+To avoid this, we will couple the solid to an external heat bath so the added energy can be transferred away from the system through a thermostat.
 Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
-We therefore freeze the outmost atoms.
+We therefore freeze the outmost atoms (blue in Fig \ref{fig:cylinder_simulation}).
 To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:
@@
 \begin{itemize}  
-	\item $r \leq 5$: applied pressure gradient
-	\item $5 < r \leq 9$: regular time integration
+	\item $r \leq 10$: applied pressure gradient
+	\item $5 < r \leq 4$: regular time integration
 	\item $9 < r \leq 12$: Dissipative Langevin thermostat
@@
 \end{itemize}
+The different radii are in reduced Lennard Jones units.
 
@@
 We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
-Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times20\times20)$ unit cells.
+Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times25\times25)$ unit cells.
 Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later anyway).

### 2018-06-05 ms.tex
Some more fixes

@@
 		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
-		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
+		Setting up and verifying the system is simple using Atomify due to i.e. the real-time coloring of groups and regions.
     }
@@
 	\item $r \leq 10$: applied pressure gradient
-	\item $5 < r \leq 4$: regular time integration
-	\item $9 < r \leq 12$: Dissipative Langevin thermostat
-	\item $12 < r$: frozen.
+	\item $r \leq 17$: regular time integration
+	\item $14 < r \leq 17$: Dissipative Langevin thermostat
+	\item $17 < r$: frozen.
 \end{itemize}
@@
 Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times25\times25)$ unit cells.
-Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later anyway).
-We will modify this script to achieve what we described above, so we need to make sure that these commands happen \textit{before} the \code{run 1000} command in the script.
-If not, LAMMPS will not execute them before we start visualizing.
+Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later).
+We will modify this script to achieve what we described above.
+To make sure LAMMPS executes our modifiction before visualization is started, we need to make sure that these commands happen \textit{before} the \code{run 1000} command.
+If we don't, LAMMPS will run 1000 timesteps before our modifications.
+
 To define the inner cylinder, we first specify the radius and the center before using the region command

### 2018-06-08 ms.tex
Removed intro and implementation section

@@
 \author{Svenn-Arne Dragly$^{1}$} 
-\author{Anders Malthe-S\o renssen$^1$}
+%\author{Anders Malthe-S\o renssen$^1$}
 \affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
@@
 \section{Introduction}
-Our nature is a very complex system with complicated rules that determine how, and where mass, energy and momentum is transferred.
-Many macroscopic observable effects result from microscopic details on the atomic level such as melting of ice, and even life.
-Understanding the world from a bottom-up perspective requires us to be able to model a physical system from the atomic scale where the timescale is of order femtoseconds.
-Many physical and chemical processes happen on nanosecond timescales, some even during a few picoseconds, which means thousands or millions of timesteps of \SI{1}{\femto\second} need to be calculated.
-Much has happened since the first molecular dynamics simulation of hard spheres in the 1950s\citep{alder1957phase,alder1959studies}, and later, in 1964, a more realistic system with the Lennard Jones potential studying diffusion in argon\citep{rahman1964correlations}.
-The computing power has seen a tremendous increase from the CDC 3600 used in \citep{rahman1964correlations}, which performed less than 1 million instructions per second whereas modern 3 Ghz processors in typical laptops can do about 100 billion instructions per seconds.
-With this rapidly increase of computing power, the lengthscales and timescales achievable in numeriments\footnote{Numeriment is a numerical experiment, or a simulation on the computer.} is finally catching up with some experiments (ref).
-
-In molecular dynamics, a set of atoms is integrated using Newton's second law in a classical force field so the full coordinate in the phase space is known at all times, and statistical properties can be calculated from averages assuming ergodicity\citep{martyna1994constant}.
-The model has been proved successful in reproducing and explaining many phenomenon such as mechanical properties \citep{jiang2009young, campbell1999structural, ning2012mechanical}, chemical reactions \citep{van2001reaxff, brenner2002second}, liquid properties\citep{allen2017computer}.
-Also in biology, molecular dynamics is useful blabla. \todo{Add more nice references here}
-
-Over the years, increasingly sophisticated methods have been developed.
-For instance, a non-equilibrium method to measure thermal conductivity using heat exchange, was recently improved\citep{wirnsberger2015enhanced} to conserve energy better than the previous method\citep{ikeshoji1994non}.
-To study first order phase transitions, methods like the generalized replica exchange method (gREM)\citep{kim2010generalized} can be used, and nudge elastic band (NEB)\citep{henkelman2000climbing, henkelman2000improved} is often used to study energy barriers in for instance chemical reactions.
-In addition, a huge amount of force fields exists, each being good at different properties\footnote{Some force fields are good at reproducing mechanical properties while others may be good at chemical reactions.
-This usually depends on what properties the force field was fitted to.}.
-New hardware and a sea of optimization tricks makes implementing a good molecular dynamics code a challenging task, not to mention maintaining it over time when new arcitechtures are being released.
-Each new feature or technique may take days, if not weeks, to develop, preventing researchers to work on their scientific projects.
-
-Thankfully, there already exists several software packages for atomistic simulations, many of which have been developed for more than two decades\footnote{\url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling} compares different softwares for molecular modeling.}.
-Some of these packages, such as LAMMPS\citep{Plimpton1995Fast}, Gromacs\citep{berendsen1995gromacs}, NAMD\citep{Phillips2005Scalable} and CHARMM\citep{brooks2009charmm}, are open source and being actively developed with hundreds of contributers\footnote{See their repositories on i.e.
-GitHub for an overview of contributers.}.
-%After the rise of powerful graphical processing units (GPU's), most of these codes eventually added support of using accelerators\citep{brown2011implementing}.
-
-\lstinputlisting[language=LAMMPS,caption={A minimal LAMMPS input script that simulates a Lennard Jones solid at reduced temperature $T^* = 1.0$ with a reduced density of $\rho^* = 0.8442$.},label={lst:simple.in}]{simple.in}
-
-The work in this paper is focused on LAMMPS.
-Although the software is well-documented\footnote{The LAMMPS documentation is known for being very detailed and precise.}, and enables the user to perform advanced simulations, it can be a demanding task to learn how to use it well.
-The core principles of molecular dynamics is so simple that high school students can easily understand the concepts, but even undergraduate students may have problems with the terminology of statistical mechanics which is used in several of the commands.
-For instance, to simulate an \textit{NVE} simulation (constant number of particles $N$, volume $V$ and energy $E$), we use the \code{fix nve} command which defines the time integration.
-
-A LAMMPS simulation is performed by a series of commands, which are executed one by one.
-LAMMPS has a huge list of implemented features which makes it very flexible, especially with its own, powerful scripting language.
-In listing \ref{lst:simple.in}, we show an example of a minimalistic LAMMPS script that simulates 4000 Lennard Jones atoms in an FCC lattice with reduced temperature $T^*=1.0$ and reduced density $\rho^* = 0.8442$.
-This simulation does not print much thermodynamic data, but it creates a file \code{trajectory.bin} which containes the trajectory of all atoms at every timestep.
-Other programs such as VMD\citep{Humphrey1996Vmd} or OVITO\citep{Stukowski2009Visualization} can be used to visualize the file as a postprocessing step.
-
-If we want to measure physical quantities such as energy, temperature and stress, they can be accessed through commands called \textit{computes}.
-For instance, the commands \code{compute ke} and \code{compute pe} measures the kinetic and the potential energy.
-Using \textit{fixes}, we can create time averages and save them to one or more files for plotting and further analysis.
-We also often put atoms in different \textit{groups}, either by their position being in a \textit{region}, or their atom type or more advanced criteria.
-Performing different operations on different groups, or just measuring physical quantities on a specific group is then easily done since almost all commands have \code{group} as an input parameter.
-With this flexibility, it may be difficult to do everything right immediately.
-Complicated regions and group defines are often necessary to perform the intended simulation, and a lot of time can be spent in the prototyping process, especially since information about groups and regions are not automatically written to a trajectory file.
-A simulation typically involves writing the LAMMPS script in a text editor before the simulation is performed in the terminal for a while before the trajectories and time series are studied to verify the correctness which often turn out to be bad.
-Plotting of time series also requires the user to write a script in i.e. Python or MATLAB which does the plotting, but these steps are often performed manually.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{flowchart.png}
-	\caption{The typical workflow when using LAMMPS consists of multiple steps using several applications.
-	a) A LAMMPS script is written using a text editor.
-	b) Simulation is performed from the terminal.
-	c) and d) visualization and analysis is performed using Ovito and \url{http://bit.ly/logplotter}.
-	Atomify simplifies the workflow by combining all steps into a single application.}
-	\label{fig:flowchart}
-\end{figure*}
-
-The lack of an intuitive GUI and visualization\footnote{GUI is listed as a non-feature on the LAMMPS web page: \url{http://lammps.sandia.gov/non_features.html}.}
-makes this workflow complicated, see Fig. \ref{fig:flowchart}.
-The time from an idea to a visual feedback can then be destructive for the creativity where immediate feedback would be ideal.
-
-We have solved this problem by creating Atomify, a real-time LAMMPS visualizer that combines script editing, simulation, visualization, and analysis in one single application.
-It uses LAMMPS as a library and hooks into the LAMMPS simulation cycle so synchronization of atom positions and physical quantities can be performed as often as every timestep.
-Most features of LAMMPS are automatically supported, except a few due to technical reasons discussed in section \ref{sec:future}.
-
-The visualization is performed using the powerful Qt3D library where we have implemented advanced rendering techniques such as billboard raytracing to achieve maximum performance.
-This allows visualization of millions of atoms with good framerate on modern desktop computers.
-Atomify is designed with simplicity as its main goal.
-
-Since we have used the Qt framework to develop Atomify, and LAMMPS is written in object oriented \cpp, a simplified version is also made available on mobile platforms (Android and iOS).
-This version of Atomify provides access to some of the example simulations and is intended for exploration of molecular dynamics simulations by students and scientific outreach.
-It also works as a demonstration of the visualization capabilities of the desktop version of the software.
-The authors are optimistic that teachers can use the visualizations provided by
-Atomify to explain microscopic interactions underlying concepts in topics such
-as thermodynamics, geophysics, and biology.
 
@@
 
-\section{\label{sec:implementation}Implementation}
-
-Atomify runs a LAMMPS instance in the background that it issues commands to.
-The current state and atom positions are extracted from this instance for
-visualization.
-This setup makes it possible for the user to interact with LAMMPS while the
-simulation is running.
-Atomify is written in C++ and QML using the Qt framework.
-The GUI is written in QML, while LAMMPS communication,
-computations, and rendering is written in C++.
-High-performance visualization is implemented as billboards in Qt3D.
-
-\subsection{Communicating with LAMMPS}
-
-LAMMPS can be compiled as a library with most of its contents being accessable
-through either the library interface or public variables in all classes.
-LAMMPS provides a C++ API that can be used to access parts of the internal data
-in the simulation as well as for issuing commands to LAMMPS.
-Further, direct access to raw data in LAMMPS is available through the individual
-C++ classes.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/data-pipeline.pdf}
-	\caption{Rendering in Atomify is based on modifying the data from LAMMPS
-    by coloring, producing periodic images, and generating bonds between atoms.
-    The data is extracted from LAMMPS using the library API and by accessing
-    the core classes.}
-	\label{fig:data-pipeline}
-\end{figure}
-
-The data pipeline from LAMMPS to rendering in Atomify is illustrated in figure
-\ref{fig:data-pipeline}.
-When rendering one often wants to modify the data from LAMMPS before it is
-visualized.
-Examples are periodic images of the simulation,
-slicing and coloring.
-We have been inspired by the pipeline used in Ovito where the data flows through
-several \textit{modifiers}, each modifying the visualization data before the
-data is converted to a format for the GPU.
-
-\subsection{Rendering techniques}
-
-Simulations of atoms are often visualized using spheres as atoms and cylinders.
-The spheres represent the atoms while the cylinders represent the bonds between
-the atoms.
-This way, the molecular structure is easy to understand and interpret.
-In many visualization tools, the spheres and cylinders are built up by many
-triangles connected so they form the geometrical object of interest.
-One problem with this rendering technique is that each sphere needs many,
-often hundreds, of triangles in order to look spherical.
-A common technique to overcome this problem is to use billboards.
-
-Billboards are plane objects that are always facing the camera (their normal
-vector always points from the billboard center towards the camera center).
-Drawing a filled circle on the billboard is a simple approximation to rendering
-spheres, but this approach suffers from unrealistic distortions from the field
-of view and does not make it possible to render realistic lighting.
-The more robust approach, which we have chosen,
-is to cast rays from the camera to the plane and calculate the sphere
-intersection of each ray.
-The normal vector can then be found by subtracting the intersection point from
-the sphere center.
-
-The technique of using billboards with only four vertices instead of a mesh
-approximating a sphere with many more vertices is often referred to as
-\emph{imposter spheres} in the literature.
-% TODO add reference to literature explaining the details of rendering spheres with imposter billboards
-This technique significantly reduces the number of vertices sent from the CPU to
-the GPU, which in turn improves rendering performance.
-A sphere may consist of an arbitrary number of vertices,
-depending on the level of detail needed.
-A billboard will on the other hand consist of only 4 vertices and can be
-represented as a point on the CPU which is then expanded on the GPU using shader
-programming.
-By doing proper shading, the billboards can mimick the spheres and cylinders so
-they look realistic, see Fig. \ref{fig:final_billboards}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Billboards can produce pixel perfect rendering of molecules. Here we see a water molecule being rendererd with two light sources showing specular reflection and diffuse light effects.}
-	\label{fig:final_billboards}
-\end{figure}
-
-\subsection{Sphere billboards}
-
-Each sphere is visualized as two triangles making up a square large enough to
-cover all pixels the sphere needs.
-To reduce the CPU workload, all 4 corner vertices of the square are placed at
-the exact position of the sphere.
-The radius and a vertex id is specified, so that the vertex shader can move the
-4 vertices so that the plane is orthogonal to the view vector and is larger than
-the cross sectional area of the sphere of interest.
-
-\subsection{Cylinder billboards}
-%
-% TODO should we use the other terminology here rather than billboards, something about imposter visualization?
-To render bonds in the molecular structure, we have implemented a method that
-visualizes realistic cylinder shapes with billboards.
-Cylinders are more complicated to visualize with billboards because they have a
-more complex geometry.
-While spheres obviously are spherically symmetric and can be rendered the same
-way regardless of viewing angle, we need to take this into account when
-rendering cylinders.
-Furhter, the bonds need to intersect with the sphere surface in a way that
-needs to be handled by the cylinder rendering technique.
-
-The basic principle is however the same as for the spheres.
-We define the vertices needed on the CPU with the same position and add the
-necessary information about the cylinder to the vertex attributes.
-This information is then used in the vertex shader to draw the triangles of
-the billboard.
-Finally, ray tracing is used to draw the final cylinder shape based on top
-of this billboard.
-
-% TODO mention issue with end caps if this is relevant for the overlapping parts
-
-% TODO explain the details about billboard rendering?
-
-\section{Case study (Anders)}
-
-% TODO Write about case study
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{final_billboard.png}
-	\caption{Case study result}
-	\label{fig:gui}
-\end{figure}
-
-\section{\label{sec:conclusion}Conclusion}
-%
-We have presented Atomify, a software for live visualization of molecular
-dynamics simulations in LAMMPS.
-Atomify simplifies the workflow of researchers by combining script development,
-analysis and visualization in an intuitive user interface.
-The software can also be used to improve training of students using LAMMPS by
-providing immediate, visual feedback to script changes.
-
-The simple case study showed how Atomify can be used for quick iteration in
-
 \section{\label{sec:future}Future work}

### 2018-06-08 ms.tex
Words

@@
 \section{Introduction}
+Atomistic simulations insight blabla
+Important blabla
+
+Tools like, script editors, simulators, Ovito VMD defines the workflow.
 
@@
 Common pitfalls which are easily picked up with Atomify are shown.
-Details about how Atomify runs LAMMPS is found in section \ref{sec:implementation} where the data flow and the threading model is explained.
-Finally, we summarize the work in our paper in section \ref{sec:conclusion} with some thoughts about future outlooks in section \ref{sec:future}.
 

### 2018-06-08 ms.tex
Make introduction about status quo and how Atomify improves on it

@@
 \section{Introduction}
-Atomistic simulations insight blabla
-Important blabla
 
-Tools like, script editors, simulators, Ovito VMD defines the workflow.
+Atomistic simulations are used in to materials modeling to provide insight into ...
+
+Over the past decades, users of LAMMPS and other molecular dynamics simulators have
+typically written scripts in a text editor and run the scripts by passing them to the simulator
+on the command line.
+The simulator in turn writes the results to disk and the user analyzes the results
+by reading the files manually or passing them to other programs.
+With the arrival of software like VMD,
+it become easy to both visualize the trajectories and certain physical quantities.
+VMD came with support both for reading the results from file or attaching to a
+running process of supported simulators.
+Later, modern visualization tools like Ovito has made both visualization and analysis more
+accessible to new users.
+In addition, the results can be loaded into common programming languages like MATLAB and Python
+to produce publication-ready figures.
+
+In combination, the text editors, the simulators, the visualization software, and the programming
+languages like MATLAB and Python define the workflow of a typical researcher in computational
+materials science.
+While this is a powerful workflow in well-established simulations,
+it is tedious for prototyping new ideas.
+The workflow requires a fairly large amount of context switching,
+moving from the text editor to the terminal to run the simulation,
+waiting for the results, and then finally being able to study them using the analysis
+and visualization tools.
+
+Here, we present Atomify, a software that integrates script editing,
+visualization and analysis into one tool.
+Atomify has detailed knowledge about the inner workings of LAMMPS,
+which makes it capable not only of visualizing the simulation results,
+but also how the simulation is defined in terms of different groups and regions.
 

### 2018-06-08 ms.tex
Remove unnecessary sentence at beginning of introduction
Add more paragraphs, fix up typos

@@
 A text editor is needed to create and modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
-If physical quantities are computed, the data is often plotted with MATLAB or Python, where additional scripts must be used.
+If physical quantities are computed, the data is often plotted using programming languages like MATLAB or Python,
+where additional scripts must be used.
 This is a tedious process, especially for teaching purposes and for people who are new in the field.
@@
 \section{Introduction}
-
-Atomistic simulations are used in to materials modeling to provide insight into ...
 
@@
 
-Fluid flow in porous media is often characterized with permeability, the inverse flow resistance of a material.
+Fluid flow in porous media is often characterized with permeability,
+which is the inverse flow resistance of a material.
 The permeability can be measured using Darcy's law when applying a pressure gradient.
-However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel. (ref)
-This is a good approximation for liquids in larger pores, but if the channel size $R$ is of the same order, or larger, as the mean free path $\lambda$ of the fluid, this is no longer true. (ref)
-The Knudsen number, $\text{Kn} = \lambda / R$ quantifies this and can be used to apply Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
+However, the derivation of Darcy's law assume no-slip boundary conditions,
+which means that the fluid velocity is zero at the boundary of a channel. (ref)
+\todo[inline]{no-slip eller non-slip?}
+A no-slip boundary conditions is a good approximation for liquids in larger pores,
+but if the channel size $R$ is of the same order,
+or larger, as the mean free path $\lambda$ of the fluid, this condition is no longer true. (ref)
+The Knudsen number, $\text{Kn} = \lambda / R$ quantifies this relation and can be used to apply Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
 
@@
 In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas inside a nanotube with varying density to observe the slip velocity effect at low densities.
-We will create the nanotube inside a Lennard Jones solid of size  $(40\times25\times25)$ unit cells with reduced density $\rho^* = 0.8442$.
-The fluid in the nanochannel, or cylinder, will flow due to an induced pressure gradient, see Fig.
-\ref{fig:cylinder_simulation}.
+
+We create the nanotube inside a Lennard Jones solid of size  $(40\times25\times25)$ unit cells with reduced density $\rho^* = 0.8442$.
+The fluid in the nanochannel, or cylinder, will flow due to an induced pressure gradient, see Fig. \ref{fig:cylinder_simulation}.
 Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
@@
 where $\rho_m$ is the mass density of the gas atoms.
+
 Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
 To avoid this, we will couple the solid to an external heat bath so the added energy can be transferred away from the system through a thermostat.
+
 Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
@@
 Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later).
+
 We will modify this script to achieve what we described above.
@@
 The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
+
 We now press \keys{\cmd+R} to run the simulation to see how it looks.
 As shown in Fig. \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
+
 When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in Fig. \ref{fig:initial_configuration}a.
@@
 \end{figure}
-We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in lammps with \code{variable V equal PI*v\_R*v\_R*lx}.
+We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in LAMMPS with \code{variable V equal PI*v\_R*v\_R*lx}.
 In these units, we have chosen that the atomic mass is 1 so number density $\rho$ equals the mass density $\rho_m$.
@@
 and the result is shown after rerunning again with \keys{\cmd+R}, see Fig. \ref{fig:initial_configuration}c.
+
 This is a powerful workflow Atomify enables where very quick changes can be tested with immediate feedback.
@@
 The frozen atoms will not move at all and make sure that the system does not start moving due to momentum transfer from the gas particles through the solid.
+
 All these groups are highlighted in Fig. \ref{fig:initial_configuration}e by hovering the box containing all the groups. in Atomify as shown in Fig. \ref{fig:initial_configuration}f.

### 2018-06-10 ms.tex
Fixed more text and initial configuration figure

@@
 
-Over the past decades, users of LAMMPS and other molecular dynamics simulators have
+Over the past decades, users of LAMMPS\citep{Plimpton1995Fast} and other molecular dynamics simulators such as GROMACS, NAMD and CHARMM\citep{berendsen1995gromacs, Phillips2005Scalable, brooks2009charmm} have
 typically written scripts in a text editor and run the scripts by passing them to the simulator
@@
 by reading the files manually or passing them to other programs.
-With the arrival of software like VMD,
+With the arrival of software like VMD,\citep{Humphrey1996Vmd}
 it become easy to both visualize the trajectories and certain physical quantities.
@@
 running process of supported simulators.
-Later, modern visualization tools like Ovito has made both visualization and analysis more
-accessible to new users.
+Later, modern visualization tools like Ovito\citep{Stukowski2009Visualization} has made both visualization and analysis more
+accessible to new users through its powerful scriptable modifier pipeline.
 In addition, the results can be loaded into common programming languages like MATLAB and Python
@@
 but also how the simulation is defined in terms of different groups and regions.
+
+It is especially useful during development of new scripts, but can be used
+to run full, publication-ready simulations with minimal simulation overhead.
 
@@
 \section{\label{sec:features}Summary of features}
-The main features of Atomify can be summarized as script editing,
+Atomify was designed to improve workflow with reduced number of
+context switches and mouse clicks to obtain immediate results from a simulation.
+Its main features can be summarized as script editing,
 real-time visualization and plotting of physical quantities.
@@
 	\caption{
-		The rightbar is a powerful feature in Atomify where relevant
+		The \textit{Simulation summary} is a powerful feature in Atomify where relevant
 		properties from LAMMPS is presented real-time.
@@
 
-\section{\label{sec:casestudy}Case study: flow through nanoporous media}
-The features of Atomify is best presented through a case study where many of the features are useful to be productive in the script development.
+\section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
+The features of Atomify is best demonstrated through a case study where many of the features are useful to be productive in the script development.
 We have chosen to create a system with fluid flow inside a tight nanochannel.
-This involves creating a somewhat complicated initial geometry with multiple regions where we apply different tricks such as dissipative thermostats, constant force mimicking applied pressure gradient and frozen atoms to avoid net momentum of the solid.
+This involves creating a somewhat complicated initial geometry with multiple regions where we apply different rules such as a dissipative thermostat, constant force mimicking applied pressure gradient and frozen atoms to avoid net momentum of the solid.
 
-Fluid flow in porous media is often characterized with permeability,
-which is the inverse flow resistance of a material.
+Fluid flow in porous media is often characterized with its permeability - the inverse flow resistance of a material.
 The permeability can be measured using Darcy's law when applying a pressure gradient.
-However, the derivation of Darcy's law assume no-slip boundary conditions,
-which means that the fluid velocity is zero at the boundary of a channel. (ref)
-\todo[inline]{no-slip eller non-slip?}
-A no-slip boundary conditions is a good approximation for liquids in larger pores,
+In Darcy's law, the permeability is assumed to only depend on the material and its geometry.
+However, this turns out not being the case for dilute
+gases where the measured permeability changes as a function of pressure\citep{klinkenberg1941permeability}.
+This effect is called the Klinkenberg effect.
+
+The discrepancy is explained by the fact that at low pressures, the fluid velocity
+at the boundary is non-zero, a non-slip boundary condition.
+A non-slip boundary condition is a good approximation for liquids in larger pores,
 but if the channel size $R$ is of the same order,
-or larger, as the mean free path $\lambda$ of the fluid, this condition is no longer true. (ref)
-The Knudsen number, $\text{Kn} = \lambda / R$ quantifies this relation and can be used to apply Klinkenberg correction\citep{klinkenberg1941permeability} to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.
+or larger, as the mean free path $\lambda$ of the fluid, this is no longer true.
+The ratio between the mean free path and the channel size is quantified through
+the Knudsen number, $\text{Kn} = \lambda / R$, and can be used to apply the Klinkenberg correction\citep{klinkenberg1941permeability}
+to correctly describe the \textit{effective permeability} as a function of pressure in the high Knudsen number limit.
 
@@
 		The different colors indicate the regions of which different integration rules apply.
-		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
-		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
-		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
+		Blue atoms are fixed and do not move at all,
+		whereas the yellow atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
+		The red and the green atoms are integrated normally, except the green gas atoms have an applied constant acceleration representing the pressure gradient.
 		Setting up and verifying the system is simple using Atomify due to i.e. the real-time coloring of groups and regions.
@@
 
-In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas inside a nanotube with varying density to observe the slip velocity effect at low densities.
+In this case study, we will use Atomify to measure the velocity profile of a
+Lennard Jones gas inside a nanotube with varying density to observe
+the slip velocity effect at low densities.
 
@@
 Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
-To avoid this, we will couple the solid to an external heat bath so the added energy can be transferred away from the system through a thermostat.
+To avoid this, we will couple the solid to an external heat bath so the added energy can be transferred out from the system through a dissipative thermostat.
 
-Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
+Even though we only apply a pressure gradient on the gas atoms, the induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
 We therefore freeze the outmost atoms (blue in Fig \ref{fig:cylinder_simulation}).
-To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:
+To obtain a system like this, we divide the atoms into multiple regions, which are integrated differently:
 
@@
 \end{itemize}
-The different radii are in reduced Lennard Jones units.
+The different radii are specified in reduced Lennard Jones units.
 
@@
 We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
-Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times25\times25)$ unit cells.
-Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later).
+Start from the following input script
+\lstinputlisting[language=LAMMPS]{simple.in}
+we will modify it part by part.
+Here, we have a Lennard Jones solid with reduced density
+$\rho^* = 0.8442$, reduced mass $m^* = 1.0$ with $(40\times25\times25)$
+FCC unit cells and a cutoff of $2.5\sigma$ where $\sigma$ is 1.0 in the reduced units.
 
-We will modify this script to achieve what we described above.
-To make sure LAMMPS executes our modifiction before visualization is started, we need to make sure that these commands happen \textit{before} the \code{run 1000} command.
-If we don't, LAMMPS will run 1000 timesteps before our modifications.
+To make sure LAMMPS executes our modifiction before visualization is started,
+we need to make sure that additional commands happen \textit{before} the \code{run 1000} command.
+If not, LAMMPS will run 1000 timesteps before getting to our modifications.
 
@@
 \end{lstlisting}
-The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
+The region command will create a cylinder $C_1$ in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
 
@@
 The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
-To discover mistakes like this is quickly done with Atomify.
-Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command, rerun the simulation with \keys{\cmd+R} which gives the desired result in figure  \ref{fig:initial_configuration}b.
+Discovering mistakes like this is very easy using Atomify.
+The problem here is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
+Since we used \code{\$(0.5*lx)} - which is in the actual lenght units - we need to specify \code{units box} in the region command.
+We then rerun the simulation with \keys{\cmd+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
 
@@
 We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in LAMMPS with \code{variable V equal PI*v\_R*v\_R*lx}.
-In these units, we have chosen that the atomic mass is 1 so number density $\rho$ equals the mass density $\rho_m$.
-The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed}, where we need to specify the fraction of the existing atoms in that region we want to delete.
-To count the number of atoms inside a region, we first create a group containing all the atoms in the region and then create a variable that counts them.
-Assuming a density $\rho = 0.05$, we can calculate the expected number inside the cylinder as $N = V\rho$.
-The atoms inside the region can now be deleted. These steps can be done in LAMMPS like this
+We have chosen reduced mass units so the mass of our atoms is 1. The number density $\rho$ then equals the mass density $\rho_m$.
+The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed}, where we need to specify the fraction of the existing atoms in that region we want to delete, and a random seed which can be any positive number.
+Since we want to specify a certain density, we need to figure out how many atoms we should delete which depends on the current number of atoms inside the region.
+
+To count the number of atoms inside a region, we first create a group containing all the atoms in it, and then create a variable that counts them.
+Assuming density $\rho = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho$.
+The atoms inside the region can now be deleted with the following commands
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 
-This is a powerful workflow Atomify enables where very quick changes can be tested with immediate feedback.
-Every time we add a new command, we just rerun with \keys{\cmd+R} to see what happens.
+This is a powerful workflow with Atomify where quick changes can be tested with immediate feedback.
+Each time we add or change a command, we just rerun with \keys{\cmd+R} to see how it looks like.
 
-The next step now is to create a larger cylinder, the one containing the red atoms in Fig. \ref{fig:cylinder_simulation}, where regular time integration will take place.
-This cylinder should have a slightly bigger radius as stated above and can be created with another region command:
+The next step now is to create a larger cylinder $C_2$, the one containing the red atoms in Fig. \ref{fig:cylinder_simulation}, where regular time integration will take place.
+This cylinder should have a slightly bigger radius and can be created with another region command:
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 All the atoms with the dissipative thermostat, the inner shell and the gas will be integrated with the \code{fix nve} integrator.
-Therefore, we create a slightly larger cylinder which will be the one defining the group for \code{fix nve}.
-We can also define the groups with these cylinders
+We therefore create a larger cylinder $C_3$ with $r=17$ which will be the one defining the group for \code{fix nve}.
+With all three regions defined, we can also create groups which can be used in fixes
 \begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
@@
 
-The dissipative thermostat will be \code{fix langevin}\citep{schneider1978molecular}, but it should only be applied on the outer shell defined by $C_3 \setminus C_2$,
-where $C_i$ is the set containing the atoms inside cylinder $i$.
-We can obtain this with the command
+The dissipative thermostat will be \code{fix langevin}\citep{schneider1978molecular}, but it should only be applied on the outer shell defined by atoms being in $C_3$, but not in $C_2$.
+Groups define sets on which we can apply regular set operations like union, intersection and subtraction.
+We can obtain the outer shell with the command
 
@@
 
-which will contain only the outer shell.
-We here also created the group \code{frozen}, which is the outmost atoms, and the group \code{gas} which is dynamic since atoms may switch places and we want to only apply a force on the ones in the inner cylinder at any point in time.
-The frozen atoms will not move at all and make sure that the system does not start moving due to momentum transfer from the gas particles through the solid.
+We here also created the group \code{frozen}, which contains only the outmost atoms,
+and the group \code{gas} which is dynamic since atoms may go in and out, and we want
+to only apply a force on the ones in the inner cylinder $C_1$ at any point in time.
+The frozen atoms will not move at all and make sure that the system does not start 
+moving due to momentum transfer from the gas particles through the solid.
 
-All these groups are highlighted in Fig. \ref{fig:initial_configuration}e by hovering the box containing all the groups. in Atomify as shown in Fig. \ref{fig:initial_configuration}f.
-The colors of the atoms matches the group color next to the group name in Fig. \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
-We there don't any green atoms (\code{cylinder1}) since all of these are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas}.
+These groups are highlighted in Fig. \ref{fig:initial_configuration}e by hovering the box containing all the groups in Atomify as shown in Fig. \ref{fig:initial_configuration}f.
+The colors of the atoms matches those in the group name in Fig. \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
+Although one group is colored green, we don't see any green atoms (\code{cylinder1}) since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
+so the color is overrided.
 
@@
 
-The syntax for fixes is \code{fix ID groupID style args}, so the above fixes has the same name as both the groups and the fix style.
+The syntax for fixes is \code{fix ID groupID style args}, so the above fixes have the same name as both the groups and the fix style.
 \code{fix langevin} takes at least 4 arguments \textit{Tstart, Tstop, Tdamp, seed}, i.e.
 the temperature in the beginning of a simulation, the temperature at the end (timesteps in between get a linearly interpolated temperature between these values), a damping parameter which controls how strongly the thermal bath interacts with the system.
-It also needs a random seed due to the random nature of the Langevin thermostat, see \citep{schneider1978molecular} for details.
+It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \citep{schneider1978molecular}.
 Finally, we have added another compute that measures the displacement per atom.
@@
 
-The only remaining part now is to set up the commands that will measure the physical quantities like the radial velocity profile.
+The only remaining part now is to set up the commands that will apply the pressure gradient and measure the radial velocity profile.
 
 \subsection{Measurement setup}
-We will use the built-in binning feature in LAMMPS called chunks, a very general concept where you assign a \code{chunkID} to each atom
+We will use the built-in binning feature in LAMMPS called \textit{chunks}, a very general concept where you assign a \code{chunkID} to each atom
 based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
@@
 Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a large histogram.
-This fix will appear in the list of fixes in the rightbar just as groups, regions, computes and variables.
+This fix will appear in the list of fixes in the Simulation summary just as groups, regions, computes and variables.
 When we click it, we will get the figure shown in Fig. \ref{fig:velocity_profile1}.

### 2018-06-10 ms.tex
Yeah

@@
 
-We conclude this case study with a series of simulations of the system described above for different densities.
+We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
 Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in Fig. \ref{fig:velocity_profile1}.
@@
 It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
-As mentioned earlier, this is called the Klinkenberg effect \citep{klinkenberg1941permeability}.
+This is, as mentioned earlier, called the Klinkenberg effect\citep{klinkenberg1941permeability}.
+
+\section{\label{sec:discussion}Discussion}
+In this paper we have presented Atomify, an application that reduces the large amount of context switches and mouse clicks
+when creating new simulation scripts.
+As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
+due our general implementation with no assumpetion about the underlying code except atom positions.
+The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.
 
 \section{\label{sec:future}Future work}
-
-Atomify continues in heavy development and we have several features planned for
-future versions.
+Atomify continues in heavy development and we have several features planned for future versions.
 We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
@@
 to LAMMPS without installing additional software.
-It will also serve as a nice demonstration of the full desktop application of
-Atomify.
-
-Performance improvements are planned by for instance using geometry shaders in
-the rendering pipeline.
-This allows a fourfold reduction in the number of vertices passed from the CPU
-to the GPU.
-Further, geometry shaders can be used for certain modifiers,
-such as the periodic copies, which are currently performed on the CPU.
-
-% TODO Reference to KOKKOS
-We also aim to include more LAMMPS backends, such as KOKKOS, and running
-simulations on computing clusters while visualizing them on the users own
-computers.
-
-The script editor will get features such as autocompletion of LAMMPS commands
-and easy access to the online documentation by hovering or selecting specific
-commands.
-
-We are also working on including Moltemplate and other programs that generate
-systems to make it easier for users to get started with more complex
-simulations.
+It will also serve as a nice demonstration of the full desktop application of Atomify.
 
 \section{Availability}
-
 Atomify is availabe on Linux, MacOS and Windows and can be downloaded from

### 2018-06-12 ms.tex
Updated figure to reflect new script

@@
 \section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
-The features of Atomify is best demonstrated through a case study where many of the features are useful to be productive in the script development.
+The features of Atomify is best demonstrated through a case study where many of
+them are useful to obtain a productive workflow during script development.
 We have chosen to create a system with fluid flow inside a tight nanochannel.
-This involves creating a somewhat complicated initial geometry with multiple regions where we apply different rules such as a dissipative thermostat, constant force mimicking applied pressure gradient and frozen atoms to avoid net momentum of the solid.
+This involves creating a somewhat complicated initial geometry with multiple regions
+where we apply different rules such as a dissipative thermostat, constant force mimicking
+applied pressure gradient and frozen atoms to avoid net momentum of the solid.
 

### 2018-06-13 IOPLaTeX.tex
Switched to IOP

--- 2018-06-12 ms.tex
@@
-\documentclass[aps,pre,twocolumn,letterpaper,floatfix,nofootinbib]{revtex4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%    INSTITUTE OF PHYSICS PUBLISHING                                   %
+%                                                                      %
+%   `Preparing an article for publication in an Institute of Physics   %
+%    Publishing journal using LaTeX'                                   %
+%                                                                      %
+%    LaTeX source code `ioplau2e.tex' used to generate `author         %
+%    guidelines', the documentation explaining and demonstrating use   %
+%    of the Institute of Physics Publishing LaTeX preprint files       %
+%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
+%                                                                      %
+%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
+%                                                                      %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+% First we have a character check
+%
+% ! exclamation mark    " double quote  
+% # hash                ` opening quote (grave)
+% & ampersand           ' closing quote (acute)
+% $ dollar              % percent       
+% ( open parenthesis    ) close paren.  
+% - hyphen              = equals sign
+% | vertical bar        ~ tilde         
+% @ at sign             _ underscore
+% { open curly brace    } close curly   
+% [ open square         ] close square bracket
+% + plus sign           ; semi-colon    
+% * asterisk            : colon
+% < open angle bracket  > close angle   
+% , comma               . full stop
+% ? question mark       / forward slash 
+% \ backslash           ^ circumflex
+%
+% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
+% abcdefghijklmnopqrstuvwxyz 
+% 1234567890
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%%novalidate
+
+\documentclass[12pt,a4paper,final]{iopart}
+\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
+%Uncomment next line if AMS fonts required
+\usepackage{iopams}
+\usepackage{graphicx}
+\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
+
+% Custom for this paper
+\bibliographystyle{iopart-num}
+%\usepackage{amsmath,amssymb,amsfonts}
+%\usepackage{mathtools}
 % for \code color
 \usepackage[dvipsnames]{xcolor}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{pdfpages}
-\usepackage{afterpage}
-\usepackage[hidelinks]{hyperref}
-\usepackage{epstopdf}
 \usepackage{todonotes}
@@
 \lstset{
-numbers=left,
-numberstyle=\small,
-numbersep=8pt,
+basicstyle=\small,
 frame = single,
@@
 \title{Increased productivity using Atomify - a real-time LAMMPS visualizer}
-\author{Anders Hafreager$^1$}
+
+\author[cor1]{Anders Hafreager$^{1}$}
+\address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}
+\eads{\mailto{anderhaf@fys.uio.no}, \mailto{andershaf@gmail.com}}
+
 \author{Svenn-Arne Dragly$^{1}$}
-%\author{Anders Malthe-S\o renssen$^1$}
-\affiliation{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway }
-\date{\today}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ead{s.a.dragly@fys.uio.no}
 
 \begin{abstract}
-%
 The typical workflow when running atomistic simulations includes working with several programs.
@@
 Atomify is open-source software (GPL) written in C++ using the Qt framework.
-%
 \end{abstract}
 
-\maketitle
+%Uncomment for PACS numbers title message
+\pacs{00.00, 20.00, 42.10}
+% Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
+\vspace{2pc}
+\noindent{\it Keywords}: Article preparation, IOP journals
+% Uncomment for Submitted to journal title message
+\submitto{\JPA}
+% Comment out if separate title page not required
+%\maketitle
 
@@
 
-Over the past decades, users of LAMMPS\citep{Plimpton1995Fast} and other molecular dynamics simulators such as GROMACS, NAMD and CHARMM\citep{berendsen1995gromacs, Phillips2005Scalable, brooks2009charmm} have
+Over the past decades, users of LAMMPS\cite{Plimpton1995Fast} and other molecular dynamics simulators such as GROMACS, NAMD and CHARMM\cite{berendsen1995gromacs, Phillips2005Scalable, brooks2009charmm} have
 typically written scripts in a text editor and run the scripts by passing them to the simulator
@@
 by reading the files manually or passing them to other programs.
-With the arrival of software like VMD,\citep{Humphrey1996Vmd}
-it become easy to both visualize the trajectories and certain physical quantities.
+With the arrival of software like VMD,\cite{Humphrey1996Vmd}
+it became easy to both visualize the trajectories and certain 
+physical quantities such as the radial distribution function.
 VMD came with support both for reading the results from file or attaching to a
 running process of supported simulators.
-Later, modern visualization tools like Ovito\citep{Stukowski2009Visualization} has made both visualization and analysis more
+\todo[inline]{Why is Ovito more modern than VMD?}
+Later, modern visualization tools like Ovito\cite{Stukowski2009Visualization} has made both visualization and analysis more
 accessible to new users through its powerful scriptable modifier pipeline.
@@
 it is tedious for prototyping new ideas.
-The workflow requires a fairly large amount of context switching,
+This workflow requires a fairly large amount of context switching,
 moving from the text editor to the terminal to run the simulation,
@@
 to run full, publication-ready simulations with minimal simulation overhead.
+The current implementation only supports LAMMPS, but is written in a general
+way so integrating other codes is a simple task.
 
-\begin{figure*}
+\begin{figure}
 	\centering
@@
 	\label{fig:gui}
-\end{figure*}
+\end{figure}
 
@@
 
-\section{\label{sec:features}Summary of features}
-Atomify was designed to improve workflow with reduced number of
-context switches and mouse clicks to obtain immediate results from a simulation.
-Its main features can be summarized as script editing,
-real-time visualization and plotting of physical quantities.
-This turns out to improve the workflow substantially.
-In addition, Atomify comes with multiple examples,
-many of which have been made by members of the LAMMPS community.
-
-\begin{figure}
+\begin{figure}[htp!]
 	\centering
@@
 		current scalar value and a histogram over these values is shown if clicked.
-		The result of hovering atoms defined by the groups in our case study is shown in Fig. \ref{fig:cylinder_simulation}.
+		The result of hovering atoms defined by the groups in our case study is shown in figure \ref{fig:cylinder_simulation}.
     }
@@
 
-It provides a lightweight script editor with syntax highlighting and line numbers.
-Multiple files can be open at the same time and the state persist across working sessions.
-The script can easily be restarted by clicking the button in the GUI or using
-the default shortcut (\keys{Ctrl+R} in Windows and Linux or \keys{\cmd+R} in macOS).
-This enables the user to get immediate visual feedback on changes in the script.
+\section{\label{sec:features}Summary of features}
+Atomify was designed to improve the workflow by reducing the number of
+context switches and mouse clicks to obtain immediate results from a simulation.
+It has a script editor, visualization window and a summary panel so all relevant parts
+of a simulation can be on the screen at the same time.
+
+Any changes to the script like defining regions or groups,
+testing temperatures, size of simulation box or inserting atoms can
+quickly be verified since visualization is real-time.
+Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{cmd+R} on macOS).
+
+How the pressure, radial distribution function or some other
+complicated variable evolves over time is easily understood
+since these can be plotted real-time with a simple click.
+Bonds between atoms in a molecule is automatically extracted from
+the internals of LAMMPS, or can be defined as a distance threshold
+between atom types.
+
+The Atomify GUI is shown in figure \ref{fig:gui} where \todo{short summary of GUI}.
+
+This turns out to improve the workflow substantially.
+In addition, Atomify comes with multiple examples,
+many of which have been made by members of the LAMMPS community.
 
@@
 where we apply different rules such as a dissipative thermostat, constant force mimicking
-applied pressure gradient and frozen atoms to avoid net momentum of the solid.
+applied pressure gradient, and frozen atoms to avoid net momentum of the solid.
+We will create two different atom types so we can have a gas phase and a solid phase at the same temperature.
 
 Fluid flow in porous media is often characterized with its permeability - the inverse flow resistance of a material.
-The permeability can be measured using Darcy's law when applying a pressure gradient.
+The permeability can be measured using Darcy's law when applying a pressure gradient $\nabla P$.
 In Darcy's law, the permeability is assumed to only depend on the material and its geometry.
 However, this turns out not being the case for dilute
-gases where the measured permeability changes as a function of pressure\citep{klinkenberg1941permeability}.
-This effect is called the Klinkenberg effect.
+gases where the measured permeability changes as a function of pressure\cite{klinkenberg1941permeability}.
+This is called the Klinkenberg effect.
 
 The discrepancy is explained by the fact that at low pressures, the fluid velocity
-at the boundary is non-zero, a non-slip boundary condition.
+at the boundary is non-zero, i.e. we have a non-slip boundary condition.
 A non-slip boundary condition is a good approximation for liquids in larger pores,
 but if the channel size $R$ is of the same order,
-or larger, as the mean free path $\lambda$ of the fluid, this is no longer true.
+or larger, as the mean free path $\lambda$ of the fluid, it is no longer true.
+
 The ratio between the mean free path and the channel size is quantified through
-the Knudsen number, $\text{Kn} = \lambda / R$, and can be used to apply the Klinkenberg correction\citep{klinkenberg1941permeability}
+the Knudsen number, $\text{Kn} = \lambda / R$, and can be used to apply the Klinkenberg correction\cite{klinkenberg1941permeability}
 to correctly describe the \textit{effective permeability} as a function of pressure in the high Knudsen number limit.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
+	\includegraphics[width=0.75\textwidth]{lj_flow/configuration.png}
 	\caption{
@@
 		The different colors indicate the regions of which different integration rules apply.
-		Blue atoms are fixed and do not move at all,
-		whereas the yellow atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
-		The red and the green atoms are integrated normally, except the green gas atoms have an applied constant acceleration representing the pressure gradient.
+		Cyan atoms are fixed and do not move at all,
+		whereas the purple atoms are thermalized with a Langevin\cite{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
+		The orange and the yellow atoms are integrated normally, but the yellow gas atoms also have an applied constant acceleration representing the pressure gradient.
 		Setting up and verifying the system is simple using Atomify due to i.e. the real-time coloring of groups and regions.
@@
 In this case study, we will use Atomify to measure the velocity profile of a
-Lennard Jones gas inside a nanotube with varying density to observe
+gas inside a nanotube with varying density to observe
 the slip velocity effect at low densities.
+We will use the Lennard Jones potential with two different atom types.
 
-We create the nanotube inside a Lennard Jones solid of size  $(40\times25\times25)$ unit cells with reduced density $\rho^* = 0.8442$.
-The fluid in the nanochannel, or cylinder, will flow due to an induced pressure gradient, see Fig. \ref{fig:cylinder_simulation}.
+We create the nanotube inside a solid with  $(60\times30\times30)$ FCC unit cells and reduced density $\rho^* = 0.975$.
+This density was chosen so that the two atom types with the Lennard Jones coefficients specified below will coexist in different phases.
+The fluid in the nanotube, or cylinder, will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
 Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
-\begin{align}
+\[
     a = \frac{\nabla P}{\rho_m},
-\end{align}
-where $\rho_m$ is the mass density of the gas atoms.
+\]
+where $\rho_m$ is the mass density of the gas atoms and $\nabla P$ is the desired pressure gradient.
+This represents a pressure difference $\Delta P$ over a small volume element $\Delta x$ on a cross-sectional area $\Delta y\Delta z$.
 
-Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
-To avoid this, we will couple the solid to an external heat bath so the added energy can be transferred out from the system through a dissipative thermostat.
+Applying an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
+To avoid this, we couple the solid to an external heat bath so the added energy can be transferred out from the system through a dissipative thermostat.
 
-Even though we only apply a pressure gradient on the gas atoms, the induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
-We therefore freeze the outmost atoms (blue in Fig \ref{fig:cylinder_simulation}).
-To obtain a system like this, we divide the atoms into multiple regions, which are integrated differently:
+Even though we only apply a pressure gradient on the gas atoms, the induced momentum will be transferred
+to the solid atoms which eventually will start moving in the positive $x$-direction, which is not desired.
+The solid should be at rest since it is only the relative velocity between the gas and the solid that defines
+the flow. We therefore freeze the outmost atoms (colored cyan in Fig \ref{fig:cylinder_simulation}).
+To obtain this system, we divide the atoms into multiple cylindrical regions, which are integrated differently:
 
 \begin{itemize}
-	\item $r \leq 10$: applied pressure gradient
-	\item $r \leq 17$: regular time integration
-	\item $14 < r \leq 17$: Dissipative Langevin thermostat
-	\item $17 < r$: frozen.
+	\item $r \leq 12$: applied pressure gradient
+	\item $r \leq 23$: regular time integration
+	\item $18 < r \leq 23$: dissipative Langevin thermostat
+	\item $23 < r$: frozen.
 \end{itemize}
@@
 We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
-Start from the following input script
+Copy the following input script
+
+\todo[inline]{Should we remove line numbers?}
 \lstinputlisting[language=LAMMPS]{simple.in}
@@
 Here, we have a Lennard Jones solid with reduced density
-$\rho^* = 0.8442$, reduced mass $m^* = 1.0$ with $(40\times25\times25)$
-FCC unit cells and a cutoff of $2.5\sigma$ where $\sigma$ is 1.0 in the reduced units.
+$\rho^* = 0.975$, reduced masses $m_1^* = 4.0$, $m_2^* = 0.5$ with $(60\times30\times30)$
+FCC unit cells and a cutoff of $2.5$. 
+The force field parameters are chosen so that atoms of type 1
+are in the solid phase with type 2 atoms being gas at reduced temperature $T^*=0.5$.
+The two atom types are weakly coupled (small $\epsilon_{ij}$)so the gas atoms don't
+stick too much to the surface which would prevent flow.
 
 To make sure LAMMPS executes our modifiction before visualization is started,
-we need to make sure that additional commands happen \textit{before} the \code{run 1000} command.
-If not, LAMMPS will run 1000 timesteps before getting to our modifications.
+we need to make sure that following additional commands happen \textit{before} the \code{run 1000} command.
+If not, LAMMPS will run 1000 timesteps before getting to our changes.
 
 To define the inner cylinder, we first specify the radius and the center before using the region command
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
-	variable R equal $(ly*0.25)
+\begin{lstlisting}
+variable R equal 12
 variable c equal $(ly*0.5)
 region cylinder1 cylinder x $c $c $R EDGE EDGE
+set region cylinder1 type 2
 \end{lstlisting}
-The region command will create a cylinder $C_1$ in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
+The region command will create a cylinder $C_1$ in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the system in the $x$-direction specified when using \code{EDGE}.
+Atoms inside the region will also be changed to type 2 since these will be the gas atoms.
 
 We now press \keys{\cmd+R} to run the simulation to see how it looks.
-As shown in Fig. \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
-
-When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in Fig. \ref{fig:initial_configuration}a.
-The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
-Discovering mistakes like this is very easy using Atomify.
-The problem here is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
-Since we used \code{\$(0.5*lx)} - which is in the actual lenght units - we need to specify \code{units box} in the region command.
-We then rerun the simulation with \keys{\cmd+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
+As shown in figure \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in it.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{figures/initial_configuration.pdf}
+	\includegraphics[width=0.8\textwidth]{figures/initial_configuration.pdf}
 	\caption{
@@
 \end{figure}
-We now want to delete atoms so that we have a certain density. The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in LAMMPS with \code{variable V equal PI*v\_R*v\_R*lx}.
-We have chosen reduced mass units so the mass of our atoms is 1. The number density $\rho$ then equals the mass density $\rho_m$.
-The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed}, where we need to specify the fraction of the existing atoms in that region we want to delete, and a random seed which can be any positive number.
-Since we want to specify a certain density, we need to figure out how many atoms we should delete which depends on the current number of atoms inside the region.
+
+When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in figure \ref{fig:initial_configuration}a.
+The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
+Discovering mistakes like this is very easy using Atomify.
+
+The problem here is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
+Since we used \code{\$(0.5*lx)}, which gives the system length in actual lenght units, we need to specify \code{units box} in the region command.
+We then rerun the simulation with \keys{\cmd+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
+
+Now that the region looks like we expect, we want to delete atoms to control the density.
+The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in LAMMPS with \code{variable V equal PI*v\_R*v\_R*lx}.
+The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed},
+where we need to specify the fraction of the existing atoms in that region we want to delete, and a random seed which can be any positive number.
+Since we want to specify a certain density, we need to figure out how many atoms we
+should delete which depends on the current number of atoms inside the region.
 
 To count the number of atoms inside a region, we first create a group containing all the atoms in it, and then create a variable that counts them.
-Assuming density $\rho = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho$.
+Assuming density $\rho_m = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho_m/m$,
+where $V$ is the volume of the cylinder and $m$ is the mass of type 2 atoms.
 The atoms inside the region can now be deleted with the following commands
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+\begin{lstlisting}
 group cylinder1 region cylinder1
@@
 variable V equal PI*v_R*v_R*lx
-	variable rho equal 0.1
-	variable N_wanted equal $V*${rho}
+variable rho_m equal 0.1
+variable N_wanted equal $V*${rho_m}/0.5
 variable delete_fraction equal (${N_cyl}-${N_wanted})/${N_cyl}
@@
 \end{lstlisting}
-and the result is shown after rerunning again with \keys{\cmd+R}, see Fig. \ref{fig:initial_configuration}c.
+where we see the result by rerunning with \keys{\cmd+R} in figure \ref{fig:initial_configuration}c.
 
-This is a powerful workflow with Atomify where quick changes can be tested with immediate feedback.
+This is a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
 Each time we add or change a command, we just rerun with \keys{\cmd+R} to see how it looks like.
 
-The next step now is to create a larger cylinder $C_2$, the one containing the red atoms in Fig. \ref{fig:cylinder_simulation}, where regular time integration will take place.
+The next step now is to create a larger cylinder $C_2$, the one containing the orange atoms in
+figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
 This cylinder should have a slightly bigger radius and can be created with another region command:
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
-	region cylinder2 cylinder x $c $c $(v_R+4) EDGE EDGE
+\begin{lstlisting}
+region cylinder2 cylinder x $c $c $(v_R+6) EDGE EDGE units box
 \end{lstlisting}
-Again press \keys{\cmd+R} and see the expected result in Fig. \ref{fig:initial_configuration}d.
+Again press \keys{\cmd+R} to see the expected result in figure \ref{fig:initial_configuration}d.
 
@@
 All the atoms with the dissipative thermostat, the inner shell and the gas will be integrated with the \code{fix nve} integrator.
-We therefore create a larger cylinder $C_3$ with $r=17$ which will be the one defining the group for \code{fix nve}.
-With all three regions defined, we can also create groups which can be used in fixes
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
-	region cylinder3 cylinder x $c $c $(v_R+7) EDGE EDGE
+We therefore create a larger cylinder $C_3$ with $r=23$ which will be the one defining the group for \code{fix nve}.
+With all three regions defined, we also create groups which will be used in fixes
+\begin{lstlisting}
+region cylinder3 cylinder x $c $c $(v_R+11) EDGE EDGE units box
 group cylinder1 region cylinder1
@@
 
-The dissipative thermostat will be \code{fix langevin}\citep{schneider1978molecular}, but it should only be applied on the outer shell defined by atoms being in $C_3$, but not in $C_2$.
+We will use \code{fix langevin}\cite{schneider1978molecular} as the dissipative thermostat,
+but it should only be applied on the outer shell defined by atoms being in $C_3$, but not in $C_2$.
 Groups define sets on which we can apply regular set operations like union, intersection and subtraction.
@@
 
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+\begin{lstlisting}
 group langevin subtract cylinder3 cylinder2
@@
 The frozen atoms will not move at all and make sure that the system does not start 
-moving due to momentum transfer from the gas particles through the solid.
+moving due to momentum transfer from the gas particles.
 
-These groups are highlighted in Fig. \ref{fig:initial_configuration}e by hovering the box containing all the groups in Atomify as shown in Fig. \ref{fig:initial_configuration}f.
-The colors of the atoms matches those in the group name in Fig. \ref{fig:initial_configuration}f, where the order of coloring is the same as they were defined in the script.
-Although one group is colored green, we don't see any green atoms (\code{cylinder1}) since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
-so the color is overrided.
+These groups are highlighted in figure \ref{fig:initial_configuration}e by hovering the
+box containing all the groups in Atomify as shown in figure \ref{fig:initial_configuration}f.
+The colors of the atoms match the group list in figure \ref{fig:initial_configuration}f,
+where the order of coloring is the same as they were defined in the script.
+Although one group is colored green, we don't see any green atoms (\code{cylinder1})
+since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
+which overrides the color.
 
 \subsection{Physical setup}
-Now that we have achieved to set up the system geometrically, that is, all the different groups of atoms are defined.
-We only need to apply the different actions, or fixes, on them.
-First, we apply the time integration \code{fix nve} which should happen on all atoms within $C_3$, then the thermostat \code{fix langevin}
+Now that we have managed to set up the system geometrically, 
+we need to apply different actions, or fixes, on them.
+First, we apply the time integration \code{fix nve} which
+should happen on all atoms within $C_3$ (remember that we created the group \code{nve} for this)
+, then the thermostat \code{fix langevin}
 
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+\begin{lstlisting}
 fix nve nve nve
@@
 \code{fix langevin} takes at least 4 arguments \textit{Tstart, Tstop, Tdamp, seed}, i.e.
-the temperature in the beginning of a simulation, the temperature at the end (timesteps in between get a linearly interpolated temperature between these values), a damping parameter which controls how strongly the thermal bath interacts with the system.
-It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \citep{schneider1978molecular}.
+the temperature in the beginning of a simulation, the temperature at the end (timesteps in between get a linearly
+interpolated temperature between these values), a damping parameter which controls how strongly the thermal bath interacts with the system.
+It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \cite{schneider1978molecular}.
 Finally, we have added another compute that measures the displacement per atom.
-Hovering this compute in the list will color each atom according to their displacement since $t=0$.
-
-By rerunning again (\keys{\cmd+R}), we can confirm that the system behaves as expected.
-In Fig. \ref{fig:moving_atoms}, we see that the outmost atoms are completely frozen (dark blue), the ones in the solid are also blue, but brighter, since they vibrate thermally in the lattice.
-The inner cylinder contains gas atoms which move more freely, as seen from the colors being in the upper part of the color map.
+In Atomify, we can hover this compute in the list of computes which will color each atom according to their displacement since $t=0$.
+This works for any \textit{per-atom} compute or variable.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{lj_flow/07_moving.png}
+	\includegraphics[width=0.8\textwidth]{lj_flow/07_moving.png}
 	\caption{
@@
 
+By rerunning again (\keys{\cmd+R}), we can confirm that the system behaves as expected.
+In figure \ref{fig:moving_atoms}, we see that the outmost atoms are completely frozen (dark blue represents zero displacement),
+the ones in the solid are also blue, but brighter, since they have moved a little bit through thermal vibrations in the lattice.
+The inner cylinder contains gas atoms which move more freely, as seen from the colors being in the upper part of the color map.
+
 The only remaining part now is to set up the commands that will apply the pressure gradient and measure the radial velocity profile.
@@
 The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line.}
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+\begin{lstlisting}
 compute chunk all chunk/atom bin/cylinder x lower &
@@
 To obtain this, we simply use
-\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
+\begin{lstlisting}
 fix vx all ave/chunk 10 10 100 chunk vx ave running
@@
 This fix will appear in the list of fixes in the Simulation summary just as groups, regions, computes and variables.
-When we click it, we will get the figure shown in Fig. \ref{fig:velocity_profile1}.
+When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{lj_flow/08_velocity_profile1.png}
+	\includegraphics[width=0.8\textwidth]{lj_flow/08_velocity_profile1.png}
 	\caption{
@@
 We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
-Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in Fig. \ref{fig:velocity_profile1}.
-All these plots are now merged into a final figure which is shown in Fig. \ref{fig:velocity_profiles}.
+Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}.
+All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profiles}.
 It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
-This is, as mentioned earlier, called the Klinkenberg effect\citep{klinkenberg1941permeability}.
+This is, as mentioned earlier, called the Klinkenberg effect\cite{klinkenberg1941permeability}.
 
@@
 
+%\section*{References}
+%\begin{thebibliography}{10}
+%\bibitem{ref1} J.~Doe, Article name, \textit{Phys. Rev. Lett.}
+
+%\bibitem{ref2} J.~Doe, J. Smith, Other article name, \textit{Phys. Rev. Lett.}
+
+%\bibitem{web} \href{http://www.google.pl}{www.google.pl}
+%\end{thebibliography}
+
 \end{document}

### 2018-06-13 IOPLaTeX.tex
Yeah, more stuff

@@
 based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
-In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc), but also the binsize in the length direction and how many radial bins we want.
-We only want one bin in the flow direction since we will measure the radial velocity profile only.
-The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line.}
+In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc.), but also the binsize in the length direction and how many radial bins we want.
+We only want one bin in the flow direction since we only want to measure the radial velocity profile.
+The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line since it is quite long.}
 \begin{lstlisting}
@@
 \end{lstlisting}
-See the documentation for details about this command, but note that the binsize in the length direction is equal to the system length so we only get one bin.
 It will create 30 radial bins for $r\in (0, R)$, where $R$ is the radius of the inner cylinder.
 The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
-To obtain this, we simply use
+To obtain this, we use
 \begin{lstlisting}
@@
 \end{lstlisting}
-Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a large histogram.
-This fix will appear in the list of fixes in the Simulation summary just as groups, regions, computes and variables.
+Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a larger histogram.
+This fix will appear in the list of fixes in the \textit{Simulation summary} just as groups, regions, computes and variables.
 When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}.
@@
 \end{figure}
-
+\todo{Create fig 6 with both one single velocity profile and MATLAB plot of all of them. Maybe W/H = 0.5?}
 \subsection{Results}
-
-\begin{figure}
-	\centering
-	% \includegraphics[width=0.5\textwidth]{lj_flow/07_moving.png}
-	\caption{
-		Velocity profiles for different densities.
-		The step flow shape is evident for low density gases with a high non-zero slip velocity.
-		When the density increases, the slip velocity goes to zero as expected.
-    }
-	\label{fig:velocity_profiles}
-\end{figure}
-
 We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
@@
 \section{\label{sec:discussion}Discussion}
-In this paper we have presented Atomify, an application that reduces the large amount of context switches and mouse clicks
-when creating new simulation scripts.
+In this paper we have presented Atomify, an new software that reduces the amount of context switches and mouse clicks
+when developing new simulation scripts.
 As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
@@
 The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.
-
-\section{\label{sec:future}Future work}
-Atomify continues in heavy development and we have several features planned for future versions.
-We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
-This makes it easy to test scripts in the browser with all simple functionalities available.
-This is especially useful in educational settings where teachers wish to introduce students
-to LAMMPS without installing additional software.
-It will also serve as a nice demonstration of the full desktop application of Atomify.
 
@@
 \section{Acknowledgments}
+Statoil etc.
 
-\section{Disclosure}
-
-Svenn-Arne Dragly is employed part-time by The Qt Company.
-
+\section*{References}
 \bibliography{Remote}
 
-%\section*{References}
+%
 %\begin{thebibliography}{10}

### 2018-06-14 IOPLaTeX.tex
Fixed availability
Improved intro and feature summary

@@
 \author[cor1]{Anders Hafreager$^{1}$}
-\address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}
 \eads{\mailto{anderhaf@fys.uio.no}, \mailto{andershaf@gmail.com}}
@@
 \ead{s.a.dragly@fys.uio.no}
+\address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}
 
@@
 Atomify supports OpenMP acceleration, GPU acceleration, real-time plotting of physical quantities, and an easy-to-use code editor in one single application.
-It currently uses LAMMPS as physics engine, but it can be extended to support other codes like Gromacs, NAMD or OpenMM.
-Atomify is open-source software (GPL) written in C++ using the Qt framework.
+It currently uses LAMMPS as physics engine, but it can be extended to support other codes like GROMACS, NAMD or CHARMM.
+Atomify is open-source software (GPL) written in C++ using the Qt framework and can be downloaded from \url{https://github.com/ovilab/atomify}.
 \end{abstract}
@@
 \vspace{2pc}
-\noindent{\it Keywords}: Article preparation, IOP journals
-% Uncomment for Submitted to journal title message
-\submitto{\JPA}
 % Comment out if separate title page not required
@@
 
-Over the past decades, users of LAMMPS\cite{Plimpton1995Fast} and other molecular dynamics simulators such as GROMACS, NAMD and CHARMM\cite{berendsen1995gromacs, Phillips2005Scalable, brooks2009charmm} have
-typically written scripts in a text editor and run the scripts by passing them to the simulator
-on the command line.
+Over the past decades, users of LAMMPS\cite{Plimpton1995Fast} and other molecular dynamics simulators such
+as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} have
+typically written scripts in a text editor and run the scripts by passing them to the simulator on the command line.
 The simulator in turn writes the results to disk and the user analyzes the results
 by reading the files manually or passing them to other programs.
-With the arrival of software like VMD,\cite{Humphrey1996Vmd}
-it became easy to both visualize the trajectories and certain 
-physical quantities such as the radial distribution function.
-VMD came with support both for reading the results from file or attaching to a
-running process of supported simulators.
-\todo[inline]{Why is Ovito more modern than VMD?}
-Later, modern visualization tools like Ovito\cite{Stukowski2009Visualization} has made both visualization and analysis more
-accessible to new users through its powerful scriptable modifier pipeline.
-In addition, the results can be loaded into common programming languages like MATLAB and Python
-to produce publication-ready figures.
+
+With the arrival of software like Rasmol\cite{sayle1995rasmol} and VMD\cite{Humphrey1996Vmd},
+it became easy to both visualize the trajectories and analyze physical quantities such as the radial distribution function.
+VMD came with support both for reading trajectories from file and attaching to a
+running process using MDComm\cite{nelson1995mdscope} and a supported simulator such as NAMD\cite{nelson1996namd}.
+Although this enabled real-time visualization, the workflow still involved using all these different programs which is still a problem today.
+
+Analysis of simulations is often done as a postprocessing step where the trajectories and other per-atom quantities (velocity, stress etc.)
+are loaded into an analysis tool written by researchers themselves. About 10 years ago, a new visualization tool called OVITO was released \cite{Stukowski2009Visualization},
+with a powerful modifier pipeline where input data can be processed and manipulated as a series of building blocks.
+These building blocks can be used to calculate new properties and atoms can be colored thereafter.
+
+Scalar quantities such as temperature, pressure and number of atoms in a specific state are often printed to a
+text file. Researchers often write their own plotting scripts in languages like MATLAB or Python
+to see how these quantities evolve with time.
 
@@
 to run full, publication-ready simulations with minimal simulation overhead.
-The current implementation only supports LAMMPS, but is written in a general
+The current implementation only supports LAMMPS as a simulator, but is written in a general
 way so integrating other codes is a simple task.
@@
 \section{\label{sec:features}Summary of features}
-Atomify was designed to improve the workflow by reducing the number of
-context switches and mouse clicks to obtain immediate results from a simulation.
+Atomify was designed to improve the workflow as its main goal.
+Focusing on minimizing the number of context switches and mouse clicks reduces
+the overhead between creativity and immediate results from a simulation.
 It has a script editor, visualization window and a summary panel so all relevant parts
@@
 testing temperatures, size of simulation box or inserting atoms can
-quickly be verified since visualization is real-time.
+quickly be verified since the visualization shows the real-time state of the simulator.
 Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{cmd+R} on macOS).
@@
 complicated variable evolves over time is easily understood
-since these can be plotted real-time with a simple click.
-Bonds between atoms in a molecule is automatically extracted from
-the internals of LAMMPS, or can be defined as a distance threshold
-between atom types.
+since these can be plotted real-time with a simple click in the list of variables.
+Bonds between atoms in a molecule is automatically extracted from LAMMPS, or can
+be defined as a distance threshold between atom types.
+Regions and groups can be highlighted or hidden which is useful to focus on some parts of a system.
+Rendering periodic copies can be done to study features near a periodic boundary condition.
+
+Per-atom scalar quantities can be used to color each atom based its value.
+For instance, \code{compute cna/atom}\cite{faken1994systematic, tsuzuki2007structural} can be used to identify the crystal structure an atom is a part of.
+It gives each atom an integer value in the range [1,5] representing FCC, HCP, BCC, Icosohedral or unknown crystal structure.
+\code{compute displace/atom} can be used to see how far each atom has moved and \code{compute stress/atom} gives the local stress in the system.
+These values can be used as input to \code{fix ave/atom} to get time averaged values to reduce noise.
+Coloring each atom based on these values can give great insight when it is available with a single mouse click.
+
+Although LAMMPS is mostly used to study molecular dynamics, it can also be used to
+study monte carlo simulations\cite{frenkel2001understanding} and granular
+materials\cite{brilliantov1996model, silbert2001granular, zhang2005jamming},
+both of which work very well in Atomify since they are particle based simulations.
+
+Atomify supports rendering of spheres and cylinders representing atoms and bonds.
+It is done using the powerful Qt3D engine with custom visualization techniques such as
+billboard raytracing\cite{tarini2006ambient} and screen space ambient occlusion\cite{bavoil2008screen}
+for improved dynamic depth perception. This allows a large amount of atoms and molecules being rendered with excellent framerate.
+The liming factor is the simulation itself since force calculation is a heavy task.
 
 The Atomify GUI is shown in figure \ref{fig:gui} where \todo{short summary of GUI}.
-
 This turns out to improve the workflow substantially.
@@
 \section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
+\todo[inline]{More references in here?}
 The features of Atomify is best demonstrated through a case study where many of
@@
 \section{Availability}
-Atomify is availabe on Linux, MacOS and Windows and can be downloaded from
+Atomify is available on Linux and MacOS and can be downloaded from
 \href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
@@
 Android or iOS.
+
+\todo[inline]{Potentially future work, emscripten, webassembly? emscripten has a proceedings paper.}
 

### 2018-06-14 IOPLaTeX.tex
Fixed more

@@
 \section{Introduction}
-
-Over the past decades, users of LAMMPS\cite{Plimpton1995Fast} and other molecular dynamics simulators such
-as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} have
-typically written scripts in a text editor and run the scripts by passing them to the simulator on the command line.
+Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
+Users of LAMMPS\cite{Plimpton1995Fast} and other codes such
+as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} typically write
+scripts in a text editor and run the scripts by passing them to the simulator on the command line.
 The simulator in turn writes the results to disk and the user analyzes the results
@@
 VMD came with support both for reading trajectories from file and attaching to a
-running process using MDComm\cite{nelson1995mdscope} and a supported simulator such as NAMD\cite{nelson1996namd}.
+running process using MDComm\cite{nelson1995mdscope} and a supported simulator such as NAMD.
+
+\todo{Also mention MDDriver and GROMACS+Megamol (delalande2009complex, grottel2015megamol)}
 Although this enabled real-time visualization, the workflow still involved using all these different programs which is still a problem today.
 
-Analysis of simulations is often done as a postprocessing step where the trajectories and other per-atom quantities (velocity, stress etc.)
-are loaded into an analysis tool written by researchers themselves. About 10 years ago, a new visualization tool called OVITO was released \cite{Stukowski2009Visualization},
-with a powerful modifier pipeline where input data can be processed and manipulated as a series of building blocks.
+Analysis of simulations is often done as a postprocessing step where the trajectories and other 
+per-atom quantities, such as velocity and stress, are loaded into an analysis tool written by researchers themselves.
+About 10 years ago, a new visualization tool called OVITO was released \cite{Stukowski2009Visualization},
+with a powerful modifier pipeline where input data can be processed and manipulated as a series of scriptable building blocks.
 These building blocks can be used to calculate new properties and atoms can be colored thereafter.
@@
 Scalar quantities such as temperature, pressure and number of atoms in a specific state are often printed to a
-text file. Researchers often write their own plotting scripts in languages like MATLAB or Python
-to see how these quantities evolve with time.
+text file. Researchers then write their own plotting scripts in languages like MATLAB or Python
+to plot the time evolution of these quantities.
 
@@
 
-It is especially useful during development of new scripts, but can be used
+This is especially useful during development of new scripts, but can be used
 to run full, publication-ready simulations with minimal simulation overhead.
@@
 	\centering
-	\includegraphics[width=\textwidth]{gui.png}
+	\includegraphics[width=\textwidth]{figures/gui.png}
 	\caption{%
@@
 	\caption{
-		The \textit{Simulation summary} is a powerful feature in Atomify where relevant
+		The \textit{Simulation} panel is a powerful feature in Atomify where relevant
 		properties from LAMMPS is presented real-time.
@@
 \section{\label{sec:features}Summary of features}
-Atomify was designed to improve the workflow as its main goal.
+Atomify was designed with one main goal: improve the workflow.
 Focusing on minimizing the number of context switches and mouse clicks reduces
-the overhead between creativity and immediate results from a simulation.
+the overhead between creativity and results from a simulation.
 It has a script editor, visualization window and a summary panel so all relevant parts
@@
 Any changes to the script like defining regions or groups,
-testing temperatures, size of simulation box or inserting atoms can
+changing temperatures, size of simulation box or inserting atoms can
 quickly be verified since the visualization shows the real-time state of the simulator.
@@
 How the pressure, radial distribution function or some other
-complicated variable evolves over time is easily understood
+complicated variable evolves over time is easily found
 since these can be plotted real-time with a simple click in the list of variables.
-Bonds between atoms in a molecule is automatically extracted from LAMMPS, or can
-be defined as a distance threshold between atom types.
-Regions and groups can be highlighted or hidden which is useful to focus on some parts of a system.
-Rendering periodic copies can be done to study features near a periodic boundary condition.
+Bonds between atoms in a molecule are automatically extracted from LAMMPS, or can
+be specified as a distance threshold between atom types.
+Regions and groups can be highlighted or hidden, which is useful to focus on some parts of a system.
+Rendering of periodic copies helps studying features near a periodic boundary.
 
-Per-atom scalar quantities can be used to color each atom based its value.
+When the simulation produces per-atom scalar quantities, Atomify can color each atom based the value.
 For instance, \code{compute cna/atom}\cite{faken1994systematic, tsuzuki2007structural} can be used to identify the crystal structure an atom is a part of.
@@
 \code{compute displace/atom} can be used to see how far each atom has moved and \code{compute stress/atom} gives the local stress in the system.
-These values can be used as input to \code{fix ave/atom} to get time averaged values to reduce noise.
-Coloring each atom based on these values can give great insight when it is available with a single mouse click.
+More complicated variables using per-atom data can be defined due to the general scripting language in LAMMPS.
+If desired, these values can be time averaged using \code{fix ave/atom} and used to color each atom according to the value.
 
@@
 It is done using the powerful Qt3D engine with custom visualization techniques such as
-billboard raytracing\cite{tarini2006ambient} and screen space ambient occlusion\cite{bavoil2008screen}
+billboard raycasting\cite{gumhold2003splatting, sigg2006gpu, tarini2006ambient} and screen space ambient occlusion\cite{bavoil2008screen}
 for improved dynamic depth perception. This allows a large amount of atoms and molecules being rendered with excellent framerate.
-The liming factor is the simulation itself since force calculation is a heavy task.
+The liming factor is the simulation itself, since force calculation is a heavy task.
 
@@
 \section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
-\todo[inline]{More references in here?}
-The features of Atomify is best demonstrated through a case study where many of
-them are useful to obtain a productive workflow during script development.
+Atomify is best demonstrated with a case study where many of
+the useful features are used to obtain a productive workflow during script development.
 We have chosen to create a system with fluid flow inside a tight nanochannel.
@@
 
-Fluid flow in porous media is often characterized with its permeability - the inverse flow resistance of a material.
+Fluid flow is often characterized with its permeability - the inverse flow resistance of a material.
 The permeability can be measured using Darcy's law when applying a pressure gradient $\nabla P$.
@@
 at the boundary is non-zero, i.e. we have a non-slip boundary condition.
+Darcy's law was found as an empirical law using water and sand.
 A non-slip boundary condition is a good approximation for liquids in larger pores,
@@
 		Initial configuration in our case study simulation.
-		A periodic box consisting of $(40\times25\times25)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 10 (reduced length).
+		A periodic box consisting of $(60\times30\times30)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 12.
 		The different colors indicate the regions of which different integration rules apply.
@@
 
-We create the nanotube inside a solid with  $(60\times30\times30)$ FCC unit cells and reduced density $\rho^* = 0.975$.
+We create a nanotube inside a solid with  $(60\times30\times30)$ FCC unit cells and reduced density $\rho^* = 0.975$.
 This density was chosen so that the two atom types with the Lennard Jones coefficients specified below will coexist in different phases.
@@
 
-Applying an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
+Applying an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system or make it move.
 To avoid this, we couple the solid to an external heat bath so the added energy can be transferred out from the system through a dissipative thermostat.
@@
 Even though we only apply a pressure gradient on the gas atoms, the induced momentum will be transferred
-to the solid atoms which eventually will start moving in the positive $x$-direction, which is not desired.
-The solid should be at rest since it is only the relative velocity between the gas and the solid that defines
+to the solid atoms which eventually will start moving in the positive $x$-direction.
+We want the solid to be at rest since it is only the relative velocity between the gas and the solid that defines
 the flow. We therefore freeze the outmost atoms (colored cyan in Fig \ref{fig:cylinder_simulation}).
@@
 \begin{itemize}
-	\item $r \leq 12$: applied pressure gradient
+	\item $r \leq 12$: gas atoms with applied pressure gradient
+	\item $18 < r \leq 23$: dissipative Langevin thermostat
 	\item $r \leq 23$: regular time integration
-	\item $18 < r \leq 23$: dissipative Langevin thermostat
 	\item $23 < r$: frozen.
@@
 \subsection{Creating the initial geometry}
-We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
+We create a new script in Atomify using \keys{\ctrl+N}, and save it (\keys{\ctrl+S}) as \code{run.in}.
 Copy the following input script
@@
 \todo[inline]{Should we remove line numbers?}
-\lstinputlisting[language=LAMMPS]{simple.in}
 we will modify it part by part.
@@
 The force field parameters are chosen so that atoms of type 1
-are in the solid phase with type 2 atoms being gas at reduced temperature $T^*=0.5$.
-The two atom types are weakly coupled (small $\epsilon_{ij}$)so the gas atoms don't
-stick too much to the surface which would prevent flow.
+are in the solid phase while type 2 atoms are gas at reduced temperature $T^*=0.5$.
+The two atom types are weakly coupled (small $\epsilon_{ij}$) so the gas atoms won't
+stick too easily to the surface since this would prevent flow.
 
@@
 \end{lstlisting}
-The region command will create a cylinder $C_1$ in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the system in the $x$-direction specified when using \code{EDGE}.
-Atoms inside the region will also be changed to type 2 since these will be the gas atoms.
+The region command will create a cylinder $C_1$ in the $x$-direction, with $(y,z)$-coordinates at the 
+system center \code{\$c} with radius \code{\$R} using the full length of the system in the $x$-direction specified with \code{EDGE}.
+We also change the atoms inside the region to type 2 since are the gas atoms.
 
@@
 		and all regions (placed in groups) are shown in e). Here we have uniquely defined the purple shell which should have a dissipative thermostat.
-		In f), the list of all groups defined in this system is shown with colors matching those of e). All figures are rendered with Atomify.
+		In f), the list of all groups defined in this system is shown with colors matching those of e).
+		Although one group is colored green, we don't see any green atoms (\code{cylinder1})
+		since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
+		which all override the color. The color of an atom is determined by the last defined group it is member of.
+		All figures are rendered with Atomify.
     }
@@
 The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
-Discovering mistakes like this is very easy using Atomify.
+Discovering mistakes like this is easy using Atomify.
 
-The problem here is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
+The problem is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
 Since we used \code{\$(0.5*lx)}, which gives the system length in actual lenght units, we need to specify \code{units box} in the region command.
@@
 
-Now that the region looks like we expect, we want to delete atoms to control the density.
+Now that the region looks right, we want to delete some atoms to control the density.
 The volume of the inner cylinder is $\pi R^2 L$ which can be calculated in LAMMPS with \code{variable V equal PI*v\_R*v\_R*lx}.
@@
 Since we want to specify a certain density, we need to figure out how many atoms we
-should delete which depends on the current number of atoms inside the region.
+should delete. This depends on the current number of atoms inside the region.
 
 To count the number of atoms inside a region, we first create a group containing all the atoms in it, and then create a variable that counts them.
-Assuming density $\rho_m = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho_m/m$,
+Assuming mass density $\rho_m = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho_m/m$,
 where $V$ is the volume of the cylinder and $m$ is the mass of type 2 atoms.
+
 The atoms inside the region can now be deleted with the following commands
@@
 \end{lstlisting}
-where we see the result by rerunning with \keys{\cmd+R} in figure \ref{fig:initial_configuration}c.
+where we see the result in figure \ref{fig:initial_configuration}c by rerunning the script with \keys{\ctrl+R}.
 
-This is a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
-Each time we add or change a command, we just rerun with \keys{\cmd+R} to see how it looks like.
+This shows a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
+Each time we add or change a command, we just rerun with \keys{\ctrl+R} to see how it looks like.
 
@@
 \end{lstlisting}
-Again press \keys{\cmd+R} to see the expected result in figure \ref{fig:initial_configuration}d.
+Again press \keys{\ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.
 
@@
 where we also have created the group \code{nve} for clarity.
+Note that cylinder 3 contains all atoms in cylinder 2 which contains all atoms in cylinder 1.
+\todo{Fix so cylinder 2 in fig 4 have same color on all atoms.}
 
@@
 group frozen subtract all cylinder3
-group gas dynamic all region cylinder1 every 1
+group gas type 2
 \end{lstlisting}
@@
 We here also created the group \code{frozen}, which contains only the outmost atoms,
-and the group \code{gas} which is dynamic since atoms may go in and out, and we want
-to only apply a force on the ones in the inner cylinder $C_1$ at any point in time.
+and the group \code{gas} which are all atoms of type 2.
 The frozen atoms will not move at all and make sure that the system does not start 
-moving due to momentum transfer from the gas particles.
+moving due to momentum transfer from the flowing gas atoms.
 
@@
 where the order of coloring is the same as they were defined in the script.
-Although one group is colored green, we don't see any green atoms (\code{cylinder1})
-since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
-which overrides the color.
 
@@
 fix nve nve nve
-fix langevin langevin langevin 1.0 1.0 1.0 12345
+fix langevin langevin langevin 0.5 0.5 1.0 12345
 compute displacement all displace/atom
@@
 It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \cite{schneider1978molecular}.
-Finally, we have added another compute that measures the displacement per atom.
+Finally, we have added another compute that measures the displacement per atom which we will use to see if atoms are placed stable in the crystal lattice.
 In Atomify, we can hover this compute in the list of computes which will color each atom according to their displacement since $t=0$.
@@
 	\caption{
-		We see the expected moving atoms inside the $C_3$ cylinder.
-		The atoms are colored based on their displacement (measured in reduced length units).
-		We confirm that the outmost atoms are frozen, which we read from dark blue color mapping to 0 displacement.
-		The moving atoms in the solid are blue, but brighter than the frozen ones which is expected due to their thermal vibrations.
+		Snapshot of the system after $t=2.0$ where atoms are colored by their displacements since $t=0$.
+		The outmost atoms are completely frozen as we see from the dark blue color meaning zero displacement.
+		Atoms in the solid are also blue, but brighter, since they are thermally vibrating in the lattice.
 		Inside the inner cylinder we see that the gas moves more freely since these atoms are not bounded.
@@
 
-By rerunning again (\keys{\cmd+R}), we can confirm that the system behaves as expected.
-In figure \ref{fig:moving_atoms}, we see that the outmost atoms are completely frozen (dark blue represents zero displacement),
-the ones in the solid are also blue, but brighter, since they have moved a little bit through thermal vibrations in the lattice.
-The inner cylinder contains gas atoms which move more freely, as seen from the colors being in the upper part of the color map.
-
+By rerunning again (\keys{\ctrl+R}), we confirm that the system behaves as expected as shown in figure \ref{fig:moving_atoms} where
+atoms are colored based on their displacement.
 The only remaining part now is to set up the commands that will apply the pressure gradient and measure the radial velocity profile.
@@
 \subsection{Measurement setup}
-We will use the built-in binning feature in LAMMPS called \textit{chunks}, a very general concept where you assign a \code{chunkID} to each atom
+We will use the built-in binning feature in LAMMPS called \textit{chunks}, a general concept where you assign a \code{chunkID} to each atom
 based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
 In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc.), but also the binsize in the length direction and how many radial bins we want.
-We only want one bin in the flow direction since we only want to measure the radial velocity profile.
+We use one single bin in the flow direction since we only want to measure the radial velocity profile.
 The command for giving each atom a \code{chunkID} is\footnote{The \& is used to continue the command on the next line since it is quite long.}
@@
 Here we use every 10th value to sample the velocity profile, keeping all samples to sum them into a larger histogram.
-This fix will appear in the list of fixes in the \textit{Simulation summary} just as groups, regions, computes and variables.
-When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}.
+This fix will appear in the list of fixes in the \textit{Simulation} panel just as groups, regions, computes and variables.
+When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}a.
 
@@
 We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
-Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}.
-All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profiles}.
+Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}a.
+All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profile1}b.
 It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.

### 2018-06-14 IOPLaTeX.tex
Fixed script and small stuwff

@@
 quickly be verified since the visualization shows the real-time state of the simulator.
-Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{cmd+R} on macOS).
+Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{\cmd+R} on macOS).
 
@@
 \subsection{Creating the initial geometry}
-We create a new script in Atomify using \keys{\ctrl+N}, and save it (\keys{\ctrl+S}) as \code{run.in}.
+We create a new script in Atomify using \keys{Ctrl+N}, and save it with \keys{Ctrl+S} as \code{run.in}.
 Copy the following input script
 
-\todo[inline]{Should we remove line numbers?}
-we will modify it part by part.
+\lstinputlisting[language=LAMMPS]{simple.in}
+
+We will modify this script bit by bit.
 Here, we have a Lennard Jones solid with reduced density
@@
 \end{lstlisting}
-where we see the result in figure \ref{fig:initial_configuration}c by rerunning the script with \keys{\ctrl+R}.
+where we see the result in figure \ref{fig:initial_configuration}c by rerunning the script with \keys{Ctrl+R}.
 
 This shows a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
-Each time we add or change a command, we just rerun with \keys{\ctrl+R} to see how it looks like.
+Each time we add or change a command, we just rerun with \keys{Ctrl+R} to see how it looks like.
 
@@
 \end{lstlisting}
-Again press \keys{\ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.
+Again press \keys{Ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.
 
@@
 
-By rerunning again (\keys{\ctrl+R}), we confirm that the system behaves as expected as shown in figure \ref{fig:moving_atoms} where
+By rerunning again (\keys{Ctrl+R}), we confirm that the system behaves as expected as shown in figure \ref{fig:moving_atoms} where
 atoms are colored based on their displacement.
@@
 
-\section{\label{sec:discussion}Discussion}
-In this paper we have presented Atomify, an new software that reduces the amount of context switches and mouse clicks
-when developing new simulation scripts.
-As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
-due our general implementation with no assumpetion about the underlying code except atom positions.
-The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.
-
 \section{Availability}
@@
 Android or iOS.
-
-\todo[inline]{Potentially future work, emscripten, webassembly? emscripten has a proceedings paper.}
 

### 2018-06-15 IOPLaTeX.tex
Fixed wording

@@
 \section{Introduction}
+\todo[inline]{Use the word user-friendly more!}
 Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
@@
 
-\todo{Also mention MDDriver and GROMACS+Megamol (delalande2009complex, grottel2015megamol)}
-Although this enabled real-time visualization, the workflow still involved using all these different programs which is still a problem today.
+Some 10 years later, an improved abstract communication layer called MDDriver\cite{delalande2009complex} was designed
+which is general and a small effort is needed to add support for a new simulator. MegaMol\cite{grottel2015megamol} was developed
+only a few years ago and supports real-time visualization of GROMACS through MDDriver.
+Although this enable real-time visualizations, the workflow still involves using all these different programs and is not very user friendly.
+The data is also transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex} which may introduce
+overhead in data transfer compared to a shared memory solution.
 
@@
 visualization and analysis into one tool.
-Atomify has detailed knowledge about the inner workings of LAMMPS,
-which makes it capable not only of visualizing the simulation results,
-but also how the simulation is defined in terms of different groups and regions.
+Atomify uses LAMMPS as a linked library and has shared memory access to the internals of LAMMPS,
+which maximizes the datatransfer speed and reduces latency.
+By having direct access to all the datastructures in LAMMPS, it is capable of not only of visualizing the simulation results,
+but also extra information about how the simulation is defined using groups and regions.
 

### 2018-06-17 IOPLaTeX.tex
Fixing more

@@
 \lstdefinelanguage{LAMMPS}{
-    morekeywords={units,atom_style,lattice,region,create_box,create_atoms,pair_style,pair_coeff,neigh_modify,mass,velocity,fix,run, group every, equal, count, porosity, EDGE},
+    morekeywords={units,compute,langevin,atom_style,lattice,region,create_box,create_atoms,pair_style,pair_coeff,neigh_modify,mass,velocity,fix,run, group every, equal, count, porosity, EDGE},
     sensitive=false, % keywords are not case-sensitive
@@
 
-\title{Increased productivity using Atomify - a real-time LAMMPS visualizer}
+\title{Improved workflow using Atomify - a real-time LAMMPS visualizer}
 
@@
 This is a tedious process, especially for teaching purposes and for people who are new in the field.
-We here introduce Atomify; a high performance real-time visualizer for atomistic simulations that can simulate and render more than one million atoms with excellent frame rate on modern hardware.
+We here introduce Atomify; a user-friendly high performance real-time visualizer for atomistic simulations that can simulate and render more than one million atoms with excellent frame rate on modern hardware.
 Atomify supports OpenMP acceleration, GPU acceleration, real-time plotting of physical quantities, and an easy-to-use code editor in one single application.
@@
 %Uncomment for PACS numbers title message
-\pacs{00.00, 20.00, 42.10}
+% \pacs{00.00, 20.00, 42.10}
 % Keywords required only for MST, PB, PMB, PM, JOA, JOB? 
@@
 \section{Introduction}
-\todo[inline]{Use the word user-friendly more!}
 Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
@@
 only a few years ago and supports real-time visualization of GROMACS through MDDriver.
-Although this enable real-time visualizations, the workflow still involves using all these different programs and is not very user friendly.
-The data is also transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex} which may introduce
+The data is transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex} which may introduce
 overhead in data transfer compared to a shared memory solution.
+Although this enables real-time visualizations, the workflow not very user-friendly since it still involves
+using all these different programs that need to be configured a certain way.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/gui.png}
+	\includegraphics[width=\textwidth]{figures/gui.pdf}
 	\caption{%
     Overview of the Graphical User Interface (GUI) in Atomify.
-    The toolbar (1) is used to change between the different modes, such as
-    editing, viewing and analyzing the running simulation,
-    in addition to playback controls.
-    The file browser (2) contain the list of open LAMMPS scripts or data files.
-    The text editor (3) provides code highlighting.
-    The viewport (4) shows the current simulation.
-    The simulation properties (5) shows the simulations details, gives access to
-    LAMMPS objects such as groups, regions and computes, and the rendering
-    properties (6) lets you change the viewport settings, such as lighting and
-    draw mode.
-    TODO: Add numbers to figure.
+    The toolbar a) is used to change between the different modes, such as
+    editing, viewing and analyzing the running simulation.
+    Bottom of a) contains the playback controls.
+    The script editor b) supports multiple open files and provides simple syntax highlighting.
+    The viewport c) shows the current simulation with atoms and bonds, simulation box and coordinate axes.
+    The simulation properties d) shows the simulations details, presents
+    LAMMPS objects such as groups, regions, computes, variables and fixes, and the rendering
+	properties. If one of the computes, variables or fixes with plottable data is clicked, a plot window
+	e) is shown with simple plot properties and export functions to MATLAB, Python or pure text file.
     }
@@
 We start by discussing the GUI in section \ref{sec:features} where the main features are summarized.
-In section \ref{sec:casestudy}, the case study is introduced where we go through a typical example
-of a simulation that uses regions and groups to perform different integration on different atoms.
-Common pitfalls which are easily picked up with Atomify are shown.
+In section \ref{sec:casestudy}, a case study is introduced where we go through a somewhat complicated simulation
+that uses regions and groups to perform different integration rules on different atoms.
 
@@
 \section{\label{sec:features}Summary of features}
+The Atomify graphical user interface (GUI) is shown in figure \ref{fig:gui}.
+
 Atomify was designed with one main goal: improve the workflow.
@@
 
-The Atomify GUI is shown in figure \ref{fig:gui} where \todo{short summary of GUI}.
 This turns out to improve the workflow substantially.
+
 In addition, Atomify comes with multiple examples,
@@
 		Initial configuration in our case study simulation.
-		A periodic box consisting of $(60\times30\times30)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 12.
+		A periodic box consisting of $(60\times30\times30)$ FCC unit cells with reduced density $\rho^* = 0.975$ where we will have gas flow in a cylinder with radius 12.
 		The different colors indicate the regions of which different integration rules apply.
@@
 		The wrongly placed cylinder is shown in a) whereas it is placed correctly in b).
-		c) shows how the system looks after deleting atoms to obtain $\rho = 0.01$. The next cylinder $C_2$ is shown in d),
+		c) shows how the system looks after deleting atoms to obtain $\rho_m = 0.05$. The next cylinder $C_2$ is shown in d),
 		and all regions (placed in groups) are shown in e). Here we have uniquely defined the purple shell which should have a dissipative thermostat.
@@
 To count the number of atoms inside a region, we first create a group containing all the atoms in it, and then create a variable that counts them.
-Assuming mass density $\rho_m = 0.1$, we can calculate the expected number inside the cylinder as $N = V\rho_m/m$,
+Assuming mass density $\rho_m = 0.05$, we can calculate the expected number inside the cylinder as $N = V\rho_m/m$,
 where $V$ is the volume of the cylinder and $m$ is the mass of type 2 atoms.
@@
 variable V equal PI*v_R*v_R*lx
-variable rho_m equal 0.1
+variable rho_m equal 0.05
 variable N_wanted equal $V*${rho_m}/0.5
@@
 Note that cylinder 3 contains all atoms in cylinder 2 which contains all atoms in cylinder 1.
-\todo{Fix so cylinder 2 in fig 4 have same color on all atoms.}
 
@@
 
-\subsection{Measurement setup}
-We will use the built-in binning feature in LAMMPS called \textit{chunks}, a general concept where you assign a \code{chunkID} to each atom
+\subsection{Pressure gradient and measurement}
+To obtain a pressure gradient, we will apply a constant force in the positive $x$-direction on all the gas atoms.
+A given pressure gradient must pe specified and we will use $\nabla P = 0.001$ which gives nice velocity profiles.
+In LAMMPS, we obtain this by adding the commands
+\begin{lstlisting}
+variable dP equal 0.001
+variable force equal v_dP/v_rho_m/0.5
+fix flow gas addforce v_force 0.0 0.0
+\end{lstlisting}
+To measure the velocity profile, we will use the built-in binning feature in LAMMPS called \textit{chunks},
+a general concept where you assign a \code{chunkID} to each atom
 based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{lj_flow/08_velocity_profile1.png}
+	\includegraphics[width=\textwidth]{figures/velocity_profile.pdf}
 	\caption{

### 2018-06-17 lj_flow/velocity_profile_generation/plot.py

@@ -1,0 +1,14 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+
+for rho in ["0.002", "0.005", "0.008", "0.01", "0.02", "0.05", "0.10", "0.15", "0.20", "0.30", "0.40", "0.50"]:
+	filename = "velocity.%s.txt" % rho
+	if os.path.exists(filename):
+		data = np.loadtxt(filename, skiprows=4, unpack=True)
+		r = data[1]
+		vx = data[4] / np.mean(data[4])
+		vx = data[4]
+		plt.plot(r,vx, label="rho=%s" % rho, marker='o')
+plt.legend()
+plt.show()

### 2018-06-17 lj_flow/velocity_profile_generation/plot_barrier.py

@@ -1,0 +1,13 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+
+for rho in ["0.01", "0.02", "0.05", "0.10", "0.15", "0.20", "0.30", "0.40", "0.50"]:
+	filename = "velocity.%s.txt" % rho
+	if os.path.exists(filename):
+		data = np.loadtxt(filename, skiprows=4, unpack=True)
+		r = data[1]
+		vx = data[4] / np.mean(data[4])
+		plt.plot(r,vx, label="rho=%s" % rho, marker='o')
+plt.legend()
+plt.show()

### 2018-06-17 lj_flow/velocity_profile_generation/plotprofile.m

@@ -1,0 +1,22 @@
+rho0_002 = dlmread('velocity.0.002.txt', ' ', 4, 0);
+rho0_005 = dlmread('velocity.0.005.txt', ' ', 4, 0);
+rho0_01 = dlmread('velocity.0.01.txt', ' ', 4, 0);
+rho0_1 = dlmread('velocity.0.10.txt', ' ', 4, 0);
+rho0_5 = dlmread('velocity.0.50.txt', ' ', 4, 0);
+
+hfig1 = figure;
+hax1 = axes;
+set(hfig1, 'units', 'centimeters')
+set(hax1, 'fontsize', 7)
+
+plot(rho0_002(:,4), rho0_002(:,7), 'linewidth', 1.5, 'marker', 'o');
+hold on
+plot(rho0_005(:,4), rho0_005(:,7), 'linewidth', 1.5, 'marker', '<');
+plot(rho0_01(:,4), rho0_01(:,7), 'linewidth', 1.5, 'marker', '>');
+plot(rho0_1(:,4), rho0_1(:,7), 'linewidth', 1.5, 'marker', 's');
+plot(rho0_5(:,4), rho0_5(:,7), 'linewidth', 1.5, 'marker', 'd');
+
+set(hfig1, 'position', [0 0 8.6 8.6]);
+legend({'\rho_m = 0.002', '\rho_m = 0.005', '\rho_m = 0.01', '\rho_m = 0.1', '\rho_m = 0.5'});
+xlabel('r')
+ylabel('v(r)')

### 2018-06-17 lj_flow/velocity_profile_generation/run.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+for rho in 0.01 0.02 0.04 0.08 0.16 0.32
+do
+	/lammps/lammps/src/lmp_mpi -in inner_cylinder.in -pk gpu 1 gpuID 2 2 -sf gpu -var rho $rho -e both
+	mv velocity.txt velocity.$rho.txt
+	mv trajectory.bin trajectory.$rho.bin
+	sleep 1
+done

### 2018-06-17 lj_flow/velocity_profile_generation/run_barrier.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+#for rho in 0.02 0.03 0.04 0.05 0.06 0.07 0.08 0.09 0.10 0.15 0.20 0.30 0.40 0.50 0.60 0.70 0.80 0.90 1.00
+#for rho in 0.01 0.02 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+for rho in 0.001 0.005 0.01 0.02 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+do
+	/lammps/lammps_gpu/src/lmp_mpi -in inner_cylinder.in -pk gpu 1 gpuID 0 0 -pk omp 4 -sf hybrid gpu omp -var rho $rho -e both
+	#/lammps/lammps_kokkos/src/lmp_kokkos_cuda_mpi -in inner_cylinder.in -pk kokkos newton on neigh half -sf kk -var rho $rho -e both
+	mv velocity.txt velocity.$rho.txt
+	mv trajectory.bin trajectory.$rho.bin
+	sleep 1
+done

### 2018-06-17 lj_flow/velocity_profile_generation/run_barrier1.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+#for rho in 0.02 0.03 0.04 0.05 0.06 0.07 0.08 0.09 0.10 0.15 0.20 0.30 0.40 0.50 0.60 0.70 0.80 0.90 1.00
+#for rho in 0.01 0.02 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+for rho in 0.001 0.002 0.005 0.008 0.01 0.02
+do
+	/lammps/lammps_gpu/src/lmp_mpi -in inner_cylinder.in -pk gpu 1 gpuID 0 0 -pk omp 4 -sf hybrid gpu omp -var rho $rho -e both
+	#/lammps/lammps_kokkos/src/lmp_kokkos_cuda_mpi -in inner_cylinder.in -pk kokkos newton on neigh half -sf kk -var rho $rho -e both
+	mv velocity.txt velocity.$rho.txt
+	mv trajectory.bin trajectory.$rho.bin
+	sleep 1
+done

### 2018-06-17 lj_flow/velocity_profile_generation/run_barrier_long.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#for rho in 0.02 0.03 0.04 0.05 0.06 0.07 0.08 0.09 0.10 0.15 0.20 0.30 0.40 0.50 0.60 0.70 0.80 0.90 1.00
+#for rho in 0.01 0.02 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+for rho in 0.002 0.005 0.008 0.01 0.02
+do
+	/lammps/lammps_gpu/src/lmp_mpi -in inner_cylinder_long.in -pk gpu 1 gpuID 0 0 -pk omp 4 -sf hybrid gpu omp -var rho $rho -e both
+	#/lammps/lammps_kokkos/src/lmp_kokkos_cuda_mpi -in inner_cylinder.in -pk kokkos newton on neigh half -sf kk -var rho $rho -e both
+	mv velocity_l.txt velocity.$rho.txt
+	mv trajectory_l.bin trajectory.$rho.bin
+	mv log.long log.$rho
+	sleep 1
+done

### 2018-06-17 lj_flow/velocity_profile_generation/run_barrier_short.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#for rho in 0.02 0.03 0.04 0.05 0.06 0.07 0.08 0.09 0.10 0.15 0.20 0.30 0.40 0.50 0.60 0.70 0.80 0.90 1.00
+#for rho in 0.01 0.02 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+for rho in 0.05 0.10 0.15 0.20 0.30 0.40 0.50
+do
+	/lammps/lammps_gpu/src/lmp_mpi -in inner_cylinder_short.in -pk gpu 1 gpuID 0 0 -pk omp 4 -sf hybrid gpu omp -var rho $rho -e both
+	#/lammps/lammps_kokkos/src/lmp_kokkos_cuda_mpi -in inner_cylinder.in -pk kokkos newton on neigh half -sf kk -var rho $rho -e both
+	mv velocity.txt velocity.$rho.txt
+	mv trajectory.bin trajectory.$rho.bin
+    mv log.short log.$rho
+	sleep 1
+done

### 2018-06-18 IOPLaTeX.tex
Fixing text and plots

@@
 
-Some 10 years later, an improved abstract communication layer called MDDriver\cite{delalande2009complex} was designed
-which is general and a small effort is needed to add support for a new simulator. MegaMol\cite{grottel2015megamol} was developed
+Some 10 years later, an improved abstract communication layer called MDDriver\cite{delalande2009complex} was designed.
+It is more general and a small effort is needed to add support for a new simulator. Another visualization tool MegaMol\cite{grottel2015megamol} was developed
 only a few years ago and supports real-time visualization of GROMACS through MDDriver.
@@
 Although this enables real-time visualizations, the workflow not very user-friendly since it still involves
-using all these different programs that need to be configured a certain way.
+using different programs that all need to be configured a certain way.
 
@@
 per-atom quantities, such as velocity and stress, are loaded into an analysis tool written by researchers themselves.
-About 10 years ago, a new visualization tool called OVITO was released \cite{Stukowski2009Visualization},
-with a powerful modifier pipeline where input data can be processed and manipulated as a series of scriptable building blocks.
+One of today's most popular visualization tools is called OVITO\cite{Stukowski2009Visualization},
+which introduced a powerful modifier pipeline where input data can be processed and manipulated as a series of scriptable building blocks.
 These building blocks can be used to calculate new properties and atoms can be colored thereafter.
 
-Scalar quantities such as temperature, pressure and number of atoms in a specific state are often printed to a
+Scalar quantities such as temperature, pressure or number of atoms in a specific state are often stored to a
 text file. Researchers then write their own plotting scripts in languages like MATLAB or Python
@@
 By having direct access to all the datastructures in LAMMPS, it is capable of not only of visualizing the simulation results,
-but also extra information about how the simulation is defined using groups and regions.
+but also show extra information about how the simulation is defined using groups and regions.
 
@@
 Focusing on minimizing the number of context switches and mouse clicks reduces
-the overhead between creativity and results from a simulation.
-It has a script editor, visualization window and a summary panel so all relevant parts
+the distance between creativity and simulation results.
+It has a script editor, visualization window and a simulation summary panel so all relevant parts
 of a simulation can be on the screen at the same time.
@@
 \code{compute displace/atom} can be used to see how far each atom has moved and \code{compute stress/atom} gives the local stress in the system.
-More complicated variables using per-atom data can be defined due to the general scripting language in LAMMPS.
+More complicated variables using per-atom data can be defined with the general scripting language in LAMMPS.
 If desired, these values can be time averaged using \code{fix ave/atom} and used to color each atom according to the value.
@@
 This turns out to improve the workflow substantially.
-
 In addition, Atomify comes with multiple examples,
@@
 
-We now press \keys{\cmd+R} to run the simulation to see how it looks.
+We now press \keys{Ctrl+R} to run the simulation to see how it looks.
 As shown in figure \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in it.
@@
 Since we used \code{\$(0.5*lx)}, which gives the system length in actual lenght units, we need to specify \code{units box} in the region command.
-We then rerun the simulation with \keys{\cmd+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
+We then rerun the simulation with \keys{Ctrl+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
 
@@
 variable N_cyl equal count(cylinder1)
-variable V equal PI*v_R*v_R*lx
+variable V equal PI*$R*$R*lx
 variable rho_m equal 0.05
@@
 All the atoms with the dissipative thermostat, the inner shell and the gas will be integrated with the \code{fix nve} integrator.
-We therefore create a larger cylinder $C_3$ with $r=23$ which will be the one defining the group for \code{fix nve}.
+We therefore create a larger cylinder $C_3$ with $r=21$ which will be the one defining the group for \code{fix nve}.
 With all three regions defined, we also create groups which will be used in fixes
 \begin{lstlisting}
-region cylinder3 cylinder x $c $c $(v_R+11) EDGE EDGE units box
+region cylinder3 cylinder x $c $c $(v_R+9) EDGE EDGE units box
 group cylinder1 region cylinder1
@@
 where we also have created the group \code{nve} for clarity.
-Note that cylinder 3 contains all atoms in cylinder 2 which contains all atoms in cylinder 1.
+Note that cylinder 3 contains all atoms in cylinder 2 which also contains all atoms in cylinder 1.
 
@@
 box containing all the groups in Atomify as shown in figure \ref{fig:initial_configuration}f.
-The colors of the atoms match the group list in figure \ref{fig:initial_configuration}f,
-where the order of coloring is the same as they were defined in the script.
 
@@
 First, we apply the time integration \code{fix nve} which
-should happen on all atoms within $C_3$ (remember that we created the group \code{nve} for this)
-, then the thermostat \code{fix langevin}
+should happen on all atoms within $C_3$ (remember that we created the group \code{nve} for this),
+then the thermostat \code{fix langevin}
 
@@
 \code{fix langevin} takes at least 4 arguments \textit{Tstart, Tstop, Tdamp, seed}, i.e.
-the temperature in the beginning of a simulation, the temperature at the end (timesteps in between get a linearly
-interpolated temperature between these values), a damping parameter which controls how strongly the thermal bath interacts with the system.
+the thermostat temperature in the beginning of a simulation, final thermostat temperature at the end, a damping parameter which controls how strongly the thermal bath interacts with the system.
 It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \cite{schneider1978molecular}.
@@
 variable dP equal 0.001
-variable force equal v_dP/v_rho_m/0.5
-fix flow gas addforce v_force 0.0 0.0
+variable force equal ${dP}/${rho_m}/0.5
+fix flow gas addforce ${force} 0.0 0.0
 \end{lstlisting}
 To measure the velocity profile, we will use the built-in binning feature in LAMMPS called \textit{chunks},
-a general concept where you assign a \code{chunkID} to each atom
+a general concept where a \code{chunkID} is assigned to each atom
 based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
@@
 compute chunk all chunk/atom bin/cylinder x lower &
-$(lx) $c $c 0 $R 30 units box
+$(lx) $c $c 0 $(v_R+3) 50 units box
 \end{lstlisting}
-It will create 30 radial bins for $r\in (0, R)$, where $R$ is the radius of the inner cylinder.
+It will create 50 radial bins for $r\in (0, R+3)$, where $R$ is the radius of the inner cylinder.
+We measure in a cylinder that it slightly larger than the initially defined cylinder to see where the boundary is in the plot.
 The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
@@
 	\caption{
-		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 8.7 (reduced units).
-		Since the wall also is made of Lennard Jones atoms, some of the wall atoms
-		This figure is made using the Atomify real-time plotter which can show any scalar value defined in LAMMPS
-		as compute, fix or variable.
+		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 12.
+		Atomify provides real-time plots as seen in a) and can export data to MATLAB, Python
+		or raw text, which can be used to produce publication ready figures as in b).
+		Here we have normalized the velocity profiles by the mean value so it is easier
+		to compare the profile at different densities. The higher near-boundary velocity at low densities
+		is evident from these simulations.
     }
@@
 \end{figure}
-\todo{Create fig 6 with both one single velocity profile and MATLAB plot of all of them. Maybe W/H = 0.5?}
+
 \subsection{Results}
-We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
-Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}a.
-All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profile1}b.
-It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
-This is, as mentioned earlier, called the Klinkenberg effect\cite{klinkenberg1941permeability}.
+We conclude this case study with a series of such simulations for different densities $\rho_m$.
+Each simulation runs 5000 timesteps before starting to sample for another 50000 timesteps.
+We export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}a.
+All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profile1}b, where
+we have normalized each velocity profile to its mean value so flow profiles are easier to compare.
+It is here evident that the low density velocities have a higher velocity near the boundary - i.e. so called plug flow.
+As discussed before, this is the Klinkenberg effect and explains why the permeability can be much higher for dilute gases than dense liquids.
 
@@
 Atomify is available on Linux and MacOS and can be downloaded from
-\href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
+\url{https://github.com/ovilab/atomify}
 A lightweight version of Atomify is also available for mobile devices running
-Android or iOS.
+Android or iOS. This version runs LAMMPS on the device with real-time visualization
+and supports simple interactions such as setting the temperature on thermostats.
 
 \section{Acknowledgments}
-Statoil etc.
+This work is part of the Tight Rocks research program funded by Equinor ASA at the University of Oslo.
 

### 2018-06-18 lj_flow/velocity_profile_generation/plotprofile.m

@@ -8,15 +8,16 @@ hfig1 = figure;
 hax1 = axes;
 set(hfig1, 'units', 'centimeters')
 set(hax1, 'fontsize', 7)
+stride = 3
 
-plot(rho0_002(:,4), rho0_002(:,7), 'linewidth', 1.5, 'marker', 'o');
+plot(rho0_002(1:stride:end,4), rho0_002(1:stride:end,7)/mean(rho0_002(1:3:end,7)), 'linewidth', 1.5, 'marker', 'o');
 hold on
-plot(rho0_005(:,4), rho0_005(:,7), 'linewidth', 1.5, 'marker', '<');
-plot(rho0_01(:,4), rho0_01(:,7), 'linewidth', 1.5, 'marker', '>');
-plot(rho0_1(:,4), rho0_1(:,7), 'linewidth', 1.5, 'marker', 's');
-plot(rho0_5(:,4), rho0_5(:,7), 'linewidth', 1.5, 'marker', 'd');
+plot(rho0_005(1:stride:end,4), rho0_005(1:stride:end,7)/mean(rho0_005(1:stride:end,7)), 'linewidth', 1.5, 'marker', '<');
+plot(rho0_01(1:stride:end,4), rho0_01(1:stride:end,7)/mean(rho0_01(1:stride:end,7)), 'linewidth', 1.5, 'marker', '>');
+plot(rho0_1(1:stride:end,4), rho0_1(1:stride:end,7)/mean(rho0_1(1:stride:end,7)), 'linewidth', 1.5, 'marker', 's');
+plot(rho0_5(1:stride:end,4), rho0_5(1:stride:end,7)/mean(rho0_5(1:stride:end,7)), 'linewidth', 1.5, 'marker', 'd');
 
 set(hfig1, 'position', [0 0 8.6 8.6]);
 legend({'\rho_m = 0.002', '\rho_m = 0.005', '\rho_m = 0.01', '\rho_m = 0.1', '\rho_m = 0.5'});
 xlabel('r')
-ylabel('v(r)')
+ylabel('v^*(r)')

### 2018-06-20 IOPLaTeX.tex
Notes from malthe and dragly

@@
 
-\title{Improved workflow using Atomify - a real-time LAMMPS visualizer}
+\title{Effective workflow in molecular dynamics simulations using Atomify --- a real-time LAMMPS visualizer}
 
@@
 \begin{abstract}
-The typical workflow when running atomistic simulations includes working with several programs.
-A text editor is needed to create and modify the scripts, the terminal to run the simulation, and programs like VMD or Ovito to visualize the system over time.
-If physical quantities are computed, the data is often plotted using programming languages like MATLAB or Python,
-where additional scripts must be used.
-This is a tedious process, especially for teaching purposes and for people who are new in the field.
-We here introduce Atomify; a user-friendly high performance real-time visualizer for atomistic simulations that can simulate and render more than one million atoms with excellent frame rate on modern hardware.
+A typical workflow when setting up and running atomistic simulations combines the use of several tools:
+a text editor to create and modify scripts; the terminal to run the simulation; and programs like VMD or Ovito to visualize the dynamics of the system.
+In addition, to study the behavior of physical quantities, relevant data must be computed, stored, and subsequently plotted.
+This is a cumbersome process, which limits the use of atomic simulation tools for teaching and increases the barrier of adaptation for newcomers.
+Here, we introduce Atomify to streamline the atomic simulation workflow.
+It is a user-friendly high-performance real-time visualizer for atomistic simulations that can simulate and render more than one million atoms with excellent frame rate on modern hardware.
 Atomify supports OpenMP acceleration, GPU acceleration, real-time plotting of physical quantities, and an easy-to-use code editor in one single application.
-It currently uses LAMMPS as physics engine, but it can be extended to support other codes like GROMACS, NAMD or CHARMM.
+It currently uses LAMMPS as physics engine, but it can be extended to support other underlying codes like GROMACS, NAMD or CHARMM.
 Atomify is open-source software (GPL) written in C++ using the Qt framework and can be downloaded from \url{https://github.com/ovilab/atomify}.
@@
 \section{Introduction}
-Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
-Users of LAMMPS\cite{Plimpton1995Fast} and other codes such
-as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} typically write
-scripts in a text editor and run the scripts by passing them to the simulator on the command line.
-The simulator in turn writes the results to disk and the user analyzes the results
+Atomic scale simulations using molecular dynamics simulations have become a standard tool in scientific research, development and education\cite{frenkel2001understanding,StatisticalAndThermalPhysics-Gould-2006}.
+However, the workflow to set up and run molecular dynamics simulations has remained mostly unchanged over the past decades.
+Users of LAMMPS\cite{Plimpton1995Fast}, GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} typically write
+scripts in a text editor, run the scripts by passing them to the simulator on the command line. 
+The simulator in turn writes the results to disk, and the user then analyzes the results
 by reading the files manually or passing them to other programs.
 
-With the arrival of software like Rasmol\cite{sayle1995rasmol} and VMD\cite{Humphrey1996Vmd},
-it became easy to both visualize the trajectories and analyze physical quantities such as the radial distribution function.
+With the introduction of software like Rasmol\cite{sayle1995rasmol} and VMD\cite{Humphrey1996Vmd},
+it became easy to both visualize simulation trajectories and analyze calculated quantities such as the radial distribution function within the same tool. 
 VMD came with support both for reading trajectories from file and attaching to a
@@
 Some 10 years later, an improved abstract communication layer called MDDriver\cite{delalande2009complex} was designed.
-It is more general and a small effort is needed to add support for a new simulator. Another visualization tool MegaMol\cite{grottel2015megamol} was developed
-only a few years ago and supports real-time visualization of GROMACS through MDDriver.
-The data is transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex} which may introduce
-overhead in data transfer compared to a shared memory solution.
-Although this enables real-time visualizations, the workflow not very user-friendly since it still involves
-using different programs that all need to be configured a certain way.
+Compared to MDComm it was more general and required only a small effort to add support for a new simulator.
+Another visualization tool MegaMol\cite{grottel2015megamol} was developed more recently and supported real-time visualization of GROMACS through MDDriver.
+However, data was transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex}, and this may have introduced
+overhead in the data transfer compared to a shared memory solution.
+Although this enabled real-time visualizations, the workflow was not very user-friendly since it still involved
+the use of different programs that all needed to be configured a particular way.
 
 Analysis of simulations is often done as a postprocessing step where the trajectories and other 
-per-atom quantities, such as velocity and stress, are loaded into an analysis tool written by researchers themselves.
-One of today's most popular visualization tools is called OVITO\cite{Stukowski2009Visualization},
+per-atom quantities, such as velocity and stress, are loaded into an analysis tool often written by researchers themselves.
+One of today's most popular visualization tools for atomistic simulations is OVITO\cite{Stukowski2009Visualization},
 which introduced a powerful modifier pipeline where input data can be processed and manipulated as a series of scriptable building blocks.
-These building blocks can be used to calculate new properties and atoms can be colored thereafter.
+These building blocks can be used to calculate new properties, and atoms can be colored accordingly.
 
-Scalar quantities such as temperature, pressure or number of atoms in a specific state are often stored to a
+In addition, aggregate scalar quantities such as temperature, pressure or number of atoms in a specific state are often stored to a
 text file. Researchers then write their own plotting scripts in languages like MATLAB or Python
@@
 
-In combination, the text editors, the simulators, the visualization software, and the programming
-languages like MATLAB and Python define the workflow of a typical researcher in computational
+In combination, the text editors, the simulators, the visualization software, and MATLAB or Python scripts define the workflow of a typical researcher in computational
 materials science.
-While this is a powerful workflow in well-established simulations,
+While this is a powerful workflow in well-established simulation cases,
 it is tedious for prototyping new ideas.
@@
 Atomify uses LAMMPS as a linked library and has shared memory access to the internals of LAMMPS,
-which maximizes the datatransfer speed and reduces latency.
-By having direct access to all the datastructures in LAMMPS, it is capable of not only of visualizing the simulation results,
-but also show extra information about how the simulation is defined using groups and regions.
+which maximizes the data transfer speed and reduces latency.
+By having direct access to all the data structures in LAMMPS, Atomify is capable of not only visualizing the simulation results,
+but also show additional information about how the simulation is defined using groups and regions.
 
-This is especially useful during development of new scripts, but can be used
+This is especially useful during development of new scripts, but can also be used
 to run full, publication-ready simulations with minimal simulation overhead.
-The current implementation only supports LAMMPS as a simulator, but is written in a general
+The current implementation only supports LAMMPS as a simulator, but it is written in a general
 way so integrating other codes is a simple task.
@@
 	editing, viewing and analyzing the running simulation.
-    Bottom of a) contains the playback controls.
+	The bottom of a) contains the playback controls.
 	The script editor b) supports multiple open files and provides simple syntax highlighting.
@@
 	properties. If one of the computes, variables or fixes with plottable data is clicked, a plot window
-	e) is shown with simple plot properties and export functions to MATLAB, Python or pure text file.
+	e) is shown with simple plot properties and export functions to MATLAB, Python or a text file.
 	}
@@
 
-In this paper we will go through a case study, an example simulation, where we
-use many of the useful features Atomify provides.
-We start by discussing the GUI in section \ref{sec:features} where the main features are summarized.
-In section \ref{sec:casestudy}, a case study is introduced where we go through a somewhat complicated simulation
-that uses regions and groups to perform different integration rules on different atoms.
+In this paper we will 
+introduce and demonstrate many of the useful features that Atomify provides through a case study. 
+We start by introducing the GUI in section \ref{sec:features}, which also summarizes the main features of Atomify.
+In section \ref{sec:casestudy}, the case study is introduced.
+Here, we provide a detailed walk-through of setting up, running and analyzing a non-trivial simluation that uses regions and groups to perform different integration rules on different atoms.
 
@@
 		The \textit{Simulation} panel is a powerful feature in Atomify where relevant
-		properties from LAMMPS is presented real-time.
-		In a), a list of all groups defined is shown with the current atom count.
-		b) shows all defined regions. Each group and region can be hovered so that atoms
-		are colored after what group / region they are in. If an atom is in multiple
+		properties from LAMMPS are presented real-time.
+		In a), a list of all defined groups is shown with the current atom count.
+		b) shows all defined regions. Each group and region can be hovered with the mouse so that atoms
+		are colored after what group/region they are in. If an atom is in multiple
 		groups or regions, they will get the color of the latest one defined.
-		The color boxes can be clicked which will either always highlight the atoms in a certain group or region,
+		The color boxes can be clicked to either always highlight the atoms in a certain group or region,
 		or if clicked again, hide all of them.
-		In c) and d), a list of all variables and computes is shown. If a variable or compute
-		produces a scalar, the current value is shown as can be seen with all the variables.
-		By clicking the name, a plot will show up showing the time evolution of that quantity.
+		In c) and d), a list of all variables and computes is shown. If a variable or a compute
+		produce a scalar, the current value is shown as can be seen with all the variables.
+		By clicking the name, a plot will show up with the time evolution of that quantity.
 		If a per-atom variable or compute is hovered, all atoms will be colored according to their
@@
 
-Atomify was designed with one main goal: improve the workflow.
-Focusing on minimizing the number of context switches and mouse clicks reduces
-the distance between creativity and simulation results.
-It has a script editor, visualization window and a simulation summary panel so all relevant parts
-of a simulation can be on the screen at the same time.
+Atomify was designed with one goal at mind: to improve the workflow.
+By focusing on minimizing the number of context switches and mouse clicks, 
+the distance between creativity and simulation results is reduced. 
+Atomify has a script editor, a visualization window and a simulation summary panel enabling all relevant parts
+of a simulation to be on the screen at the same time.
 
-Any changes to the script like defining regions or groups,
-changing temperatures, size of simulation box or inserting atoms can
-quickly be verified since the visualization shows the real-time state of the simulator.
+The effect of any changes to the script, such as defining regions or groups,
+changing temperatures or the size of the simulation box, or inserting atoms, can
+quickly be checked since the visualization shows the real-time state of the simulator.
 Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{\cmd+R} on macOS).
 
-How the pressure, radial distribution function or some other
-complicated variable evolves over time is easily found
-since these can be plotted real-time with a simple click in the list of variables.
+The temporal evolution of the pressure, the radial distribution function or any other
+variable can be plotted real-time with a simple click in the list of variables.
 Bonds between atoms in a molecule are automatically extracted from LAMMPS, or can
@@
 Although LAMMPS is mostly used to study molecular dynamics, it can also be used to
-study monte carlo simulations\cite{frenkel2001understanding} and granular
+model Monte Carlo simulations\cite{frenkel2001understanding} and granular
 materials\cite{brilliantov1996model, silbert2001granular, zhang2005jamming},
-both of which work very well in Atomify since they are particle based simulations.
+both of which work in Atomify since they are particle based simulations.
 
-Atomify supports rendering of spheres and cylinders representing atoms and bonds.
-It is done using the powerful Qt3D engine with custom visualization techniques such as
+Atomify supports rendering of spheres and cylinders to represent atoms and bonds.
+It is done using Qt3D with custom visualization techniques such as
 billboard raycasting\cite{gumhold2003splatting, sigg2006gpu, tarini2006ambient} and screen space ambient occlusion\cite{bavoil2008screen}
-for improved dynamic depth perception. This allows a large amount of atoms and molecules being rendered with excellent framerate.
-The liming factor is the simulation itself, since force calculation is a heavy task.
+for improved dynamic depth perception. This allows a large amount of atoms and molecules to be rendered with excellent framerate.
+The liming factor is the simulation itself, since force calculation is a computationally intensive task.
 
-This turns out to improve the workflow substantially.
-In addition, Atomify comes with multiple examples,
+In addition, Atomify comes with substantial database of examples,
 many of which have been made by members of the LAMMPS community.
@@
 \section{\label{sec:casestudy}Case study: flow through a narrow nanotube}
-Atomify is best demonstrated with a case study where many of
-the useful features are used to obtain a productive workflow during script development.
-We have chosen to create a system with fluid flow inside a tight nanochannel.
-This involves creating a somewhat complicated initial geometry with multiple regions
-where we apply different rules such as a dissipative thermostat, constant force mimicking
-applied pressure gradient, and frozen atoms to avoid net momentum of the solid.
-We will create two different atom types so we can have a gas phase and a solid phase at the same temperature.
+Atomify is best demonstrated through a case study that shows how 
+various features can be used in a productive workflow from script development to analysis.
+We have chosen to address fluid flow inside a narrow, cylindrical nanochannel, since this is a scenario that demonstrates many of the features of Atomify and its integrated workflow: The simulation involves creating an initial geometry with multiple regions
+where we apply different rules such as a dissipative thermostat, a constant force mimicking
+an applied pressure gradient, and frozen atoms to avoid net momentum of the solid.
+We introduce two different atom types in order to have a gas phase and a solid phase at the same temperature.
 
-Fluid flow is often characterized with its permeability - the inverse flow resistance of a material.
-The permeability can be measured using Darcy's law when applying a pressure gradient $\nabla P$.
+Fluid flow in porous structures is often characterized by its permeability, $k$, which describes the fluid flow conductivity of a fluid in a specific geometry.
+Darcy's law relates the average flow velocity, $U$, to the applied pressure gradient $\nabla P$: $U = (k/\mu)(-\nabla P)$, where $\mu$ is the viscosity of the fluid.
 In Darcy's law, the permeability is assumed to only depend on the material and its geometry.
-However, this turns out not being the case for dilute
-gases where the measured permeability changes as a function of pressure\cite{klinkenberg1941permeability}.
-This is called the Klinkenberg effect.
+\todo[inline]{U is the flux here, not the average velocity?}
+However, Darcy's law must be modified for dilute
+gases where the measured permeability also is found to also be a function of pressure.
+This is called the Klinkenberg effect\cite{klinkenberg1941permeability}.
 
-The discrepancy is explained by the fact that at low pressures, the fluid velocity
-at the boundary is non-zero, i.e. we have a non-slip boundary condition.
-Darcy's law was found as an empirical law using water and sand.
-A non-slip boundary condition is a good approximation for liquids in larger pores,
-but if the channel size $R$ is of the same order,
-or larger, as the mean free path $\lambda$ of the fluid, it is no longer true.
-
+The discrepancy is due to finite slip of the dilute gas along the pore walls.
+For a macroscopic fluid, the velocity of the fluid is usually assumed to be zero at the pore walls.
+This is called non-slip boundary conditions and is a good approximation for dense liquids in macroscopic pores.
+However, if the typical channel size $R$ in the pores is of the same order as the mean free path $\lambda$ of the fluid, non-slip boundary conditions are no longer a good approximation to the actual flow profile.
 The ratio between the mean free path and the channel size is quantified through
-the Knudsen number, $\text{Kn} = \lambda / R$, and can be used to apply the Klinkenberg correction\cite{klinkenberg1941permeability}
-to correctly describe the \textit{effective permeability} as a function of pressure in the high Knudsen number limit.
+the Knudsen number, $\text{Kn} = \lambda / R$ is used in the Klinkenberg correction\cite{klinkenberg1941permeability} for the \textit{effective permeability} as a function of pressure in the limit of high Knudsen numbers.
+Such a system is well suited for a molecular dynamics study because channles with small values of $R$, and hence high Knudsen numbers, may be studied in molecular systems.
 
@@
 
+\subsection{Physical description of the simulation system}
 In this case study, we will use Atomify to measure the velocity profile of a
-gas inside a nanotube with varying density to observe
-the slip velocity effect at low densities.
-We will use the Lennard Jones potential with two different atom types.
+gas inside a nanotube with varying density to directly observe
+the slip velocity at low densities.
+We will use the Lennard-Jones potential with two different atom types.
 
-We create a nanotube inside a solid with  $(60\times30\times30)$ FCC unit cells and reduced density $\rho^* = 0.975$.
-This density was chosen so that the two atom types with the Lennard Jones coefficients specified below will coexist in different phases.
-The fluid in the nanotube, or cylinder, will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
-Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$ calculated as
+We create a nanotube inside a FCC solid with $(60\times30\times30)$ unit cells and reduced density $\rho^* = 0.975$.
+The density was chosen to ensure that the two atom types with the Lennard-Jones coefficients specified below will coexist in different phases.
+We will apply a pressure gradient to the fluid inside the nanotube to induce fluid flow, see figure \ref{fig:cylinder_simulation}.
+We apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using an added force, which corresponds to an acceleration $a$ added to each atoms. The acceleration $a$ calculated as
 \[
@@
 \]
-where $\rho_m$ is the mass density of the gas atoms and $\nabla P$ is the desired pressure gradient.
+where $\rho_m$ is the mass density of the gas atoms, produces the desired pressure gradient $\nabla P$.
 This represents a pressure difference $\Delta P$ over a small volume element $\Delta x$ on a cross-sectional area $\Delta y\Delta z$.
 
-Applying an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system or make it move.
+By adding an external force to atoms in the system, energy is added to the system, which in turn will increase the temperature and eventually melt the system or make it move.
 To avoid this, we couple the solid to an external heat bath so the added energy can be transferred out from the system through a dissipative thermostat.
 
-Even though we only apply a pressure gradient on the gas atoms, the induced momentum will be transferred
-to the solid atoms which eventually will start moving in the positive $x$-direction.
-We want the solid to be at rest since it is only the relative velocity between the gas and the solid that defines
-the flow. We therefore freeze the outmost atoms (colored cyan in Fig \ref{fig:cylinder_simulation}).
+Even though we only apply a pressure gradient on the gas atoms, the induced momentum will also be transferred
+to the solid atoms, which eventually will start moving in the positive $x$-direction.
+We want the solid to be at rest, since only the relative velocity between the gas and the solid defines
+the flow. We will therefore freeze the outermost atoms (colored cyan in Fig \ref{fig:cylinder_simulation}).
+
 To obtain this system, we divide the atoms into multiple cylindrical regions, which are integrated differently:
@@
 	\item $r \leq 12$: gas atoms with applied pressure gradient
-	\item $18 < r \leq 23$: dissipative Langevin thermostat
-	\item $r \leq 23$: regular time integration
-	\item $23 < r$: frozen.
+	\item $18 < r \leq 21$: dissipative Langevin thermostat
+	\item $21 < r$: frozen.
 \end{itemize}
-The different radii are specified in reduced Lennard Jones units.
+
+The different radii are specified in reduced Lennard-Jones units.
+
+In the following we will provide a detailed description of how to set up, run and analyze this system using Atomify.
 
@@
 
-We will modify this script bit by bit.
-Here, we have a Lennard Jones solid with reduced density
+We will modify and adapt this script to bit by bit to correspond to the system we want to simulate.
+Here, we have a Lennard-Jones solid with reduced density
 $\rho^* = 0.975$, reduced masses $m_1^* = 4.0$, $m_2^* = 0.5$ with $(60\times30\times30)$
@@
 
-To make sure LAMMPS executes our modifiction before visualization is started,
+To make sure LAMMPS executes our modification before visualization is started,
 we need to make sure that following additional commands happen \textit{before} the \code{run 1000} command.
@@
 system center \code{\$c} with radius \code{\$R} using the full length of the system in the $x$-direction specified with \code{EDGE}.
-We also change the atoms inside the region to type 2 since are the gas atoms.
+We also change the atoms inside the region to type 2 since these are the gas atoms.
 
@@
 		Several snapshots of the process of creating the simulation in our case study.
-		This shows how one typically generate a geometry step by step where the immediate
+		This shows how one typically generates a geometry step by step where the immediate
 		feedback is very useful to quickly discover mistakes.
@@
 		since all of them also are in the groups \code{cylinder2}, \code{cylinder3}, \code{nve} and \code{gas},
-		which all override the color. The color of an atom is determined by the last defined group it is member of.
+		which all override the color. The color of an atom is determined by the last defined group it is a member of.
 		All figures are rendered with Atomify.
@@
 
-When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in figure \ref{fig:initial_configuration}a.
-The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
+When we hover the region, we immediately see that the cylinder is not placed at the center of the system, as shown in figure \ref{fig:initial_configuration}a.
+The reason is that LAMMPS operates with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
 Discovering mistakes like this is easy using Atomify.
 
-The problem is that LAMMPS expects the values to be in \textit{lattice} units, i.e. multiples of the lattice constant.
-Since we used \code{\$(0.5*lx)}, which gives the system length in actual lenght units, we need to specify \code{units box} in the region command.
-We then rerun the simulation with \keys{Ctrl+R} which gives the expected result in figure \ref{fig:initial_configuration}b.
+Since we used \code{\$(0.5*lx)}, which gives the system length in actual lenght units, we need to specify \code{units box} in the region command:
+\begin{lstlisting}
+	region cylinder1 cylinder x $c $c $R EDGE EDGE units box
+\end{lstlisting}
+We then rerun the simulation with \keys{Ctrl+R} and see that we get the wanted result in figure \ref{fig:initial_configuration}b.
 
@@
 The command \code{delete\_atoms} can be used: \code{delete\_atoms porosity region-ID fraction seed},
-where we need to specify the fraction of the existing atoms in that region we want to delete, and a random seed which can be any positive number.
-Since we want to specify a certain density, we need to figure out how many atoms we
+where we need to specify what fraction of the existing atoms in the region that we want to delete, and a random seed which can be any positive number.
+Since we want to specify a specific density, we need to figure out how many atoms we
 should delete. This depends on the current number of atoms inside the region.
@@
 This shows a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
-Each time we add or change a command, we just rerun with \keys{Ctrl+R} to see how it looks like.
+Each time we add or change a command, we just rerun with \keys{Ctrl+R} to see what the results look like.
 
-The next step now is to create a larger cylinder $C_2$, the one containing the orange atoms in
+The next step is to create a larger cylinder $C_2$ containing the orange atoms in
 figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
 This cylinder should have a slightly bigger radius and can be created with another region command:
+%
 \begin{lstlisting}
@@
 \end{lstlisting}
+%
 Again press \keys{Ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.
-
 Now we have the inner cylinder with the gas atoms defined as a region and the next cylinder shell (including the gas atoms) defined as another region.
@@
 All the atoms with the dissipative thermostat, the inner shell and the gas will be integrated with the \code{fix nve} integrator.
-We therefore create a larger cylinder $C_3$ with $r=21$ which will be the one defining the group for \code{fix nve}.
+We therefore create a larger cylinder $C_3$ with $r=21$, which will be the one defining the group for \code{fix nve}.
 With all three regions defined, we also create groups which will be used in fixes
@@
 
-We here also created the group \code{frozen}, which contains only the outmost atoms,
-and the group \code{gas} which are all atoms of type 2.
+We here also created the group \code{frozen}, which contains only the outermost atoms,
+and the group \code{gas}, which are all atoms of type 2.
 The frozen atoms will not move at all and make sure that the system does not start 
@@
 \code{fix langevin} takes at least 4 arguments \textit{Tstart, Tstop, Tdamp, seed}, i.e.
-the thermostat temperature in the beginning of a simulation, final thermostat temperature at the end, a damping parameter which controls how strongly the thermal bath interacts with the system.
+the thermostat temperature in the beginning of a simulation, final thermostat temperature at the end, and a damping parameter, which controls how strongly the thermal bath interacts with the system.
 It also needs a random seed due to the random nature of the Langevin thermostat as discussed in \cite{schneider1978molecular}.
-Finally, we have added another compute that measures the displacement per atom which we will use to see if atoms are placed stable in the crystal lattice.
-In Atomify, we can hover this compute in the list of computes which will color each atom according to their displacement since $t=0$.
-This works for any \textit{per-atom} compute or variable.
+Finally, we have added another compute that measures the displacement per atom which we will use to see if atoms remain stable in the crystal lattice.
+In Atomify, we can hover this compute in the list of computes to color each atom according to their displacement since $t=0$.
 
@@
 To obtain a pressure gradient, we will apply a constant force in the positive $x$-direction on all the gas atoms.
-A given pressure gradient must pe specified and we will use $\nabla P = 0.001$ which gives nice velocity profiles.
+A given pressure gradient must be specified. We will use $\nabla P = 0.001$, which was chosen so that it provides reasonable velocity profiles that demonstrate the wall slip effects.
 In LAMMPS, we obtain this by adding the commands
+%
 \begin{lstlisting}
@@
 \end{lstlisting}
+%
 To measure the velocity profile, we will use the built-in binning feature in LAMMPS called \textit{chunks},
 a general concept where a \code{chunkID} is assigned to each atom
-based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is cylinder.
+based on its position. LAMMPS supports multiple different \textit{chunk styles}, one of which is a cylinder.
 In the cylinder binning, we choose the same properties as for a cylinder region (center, length etc.), but also the binsize in the length direction and how many radial bins we want.
@@
 \end{lstlisting}
-It will create 50 radial bins for $r\in (0, R+3)$, where $R$ is the radius of the inner cylinder.
+This will create 50 radial bins for $r\in (0, R+3)$, where $R$ is the radius of the inner cylinder.
 We measure in a cylinder that it slightly larger than the initially defined cylinder to see where the boundary is in the plot.
-The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps.
-To obtain this, we use
+The final command we will use is the \code{fix ave/chunk} where we can get a smooth averaged velocity profile sampled over many timesteps
 \begin{lstlisting}
@@
 When we click it, we will get the figure shown in figure \ref{fig:velocity_profile1}a.
-
 \begin{figure}
@@
 	\caption{
-		The velocity profile for a Lennard Jones gas inside a nanochannel of radius 12.
+		The velocity profile for a Lennard-Jones gas inside a nanochannel of radius 12.
 		Atomify provides real-time plots as seen in a) and can export data to MATLAB, Python
@@
 		Here we have normalized the velocity profiles by the mean value so it is easier
-		to compare the profile at different densities. The higher near-boundary velocity at low densities
+		to compare the profile at different densities. The higher velocity near the boundaries at low densities
 		is evident from these simulations.
@@
 \subsection{Results}
-We conclude this case study with a series of such simulations for different densities $\rho_m$.
+We conclude this case study with a series of simulations for different densities $\rho_m$.
 Each simulation runs 5000 timesteps before starting to sample for another 50000 timesteps.
 We export the plots from \code{fix vx} to MATLAB using the Export function seen in figure \ref{fig:velocity_profile1}a.
+%
+% It may be a good idea also to include the MATLAB script for completeness here
+%
 All these plots are now merged into a final figure which is shown in figure \ref{fig:velocity_profile1}b, where
 we have normalized each velocity profile to its mean value so flow profiles are easier to compare.
-It is here evident that the low density velocities have a higher velocity near the boundary - i.e. so called plug flow.
-As discussed before, this is the Klinkenberg effect and explains why the permeability can be much higher for dilute gases than dense liquids.
+The figure clearly demonstrates that the gases with lower density have a higher velocity near the boundary, which is an effect called plug flow.
+As discussed before, what we observe here is the Klinkenberg effect, which explains why the permeability can be much higher for dilute gases than dense liquids.
 
@@
 \bibliography{Remote}
-
 %
@@
 %\bibitem{ref1} J.~Doe, Article name, \textit{Phys. Rev. Lett.}
-
 %\bibitem{ref2} J.~Doe, J. Smith, Other article name, \textit{Phys. Rev. Lett.}
-
 %\bibitem{web} \href{http://www.google.pl}{www.google.pl}
 %\end{thebibliography}
-
 \end{document}

### 2018-11-04 IOPLaTeX.tex
malthe is in the loop yo!
stuff

@@
 \ead{s.a.dragly@fys.uio.no}
+
+\author{Anders Malthe-S\o renssen$^{1}$}
+\ead{malthe@fys.uio.no}
 \address{$^1$Department of Physics - University of Oslo\\Sem S{\ae}lands vei 24, NO-0316, Oslo, Norway}
@@
 Fluid flow in porous structures is often characterized by its permeability, $k$, which describes the fluid flow conductivity of a fluid in a specific geometry.
-Darcy's law relates the average flow velocity, $U$, to the applied pressure gradient $\nabla P$: $U = (k/\mu)(-\nabla P)$, where $\mu$ is the viscosity of the fluid.
+Darcy's law relates the fluid flux, $q$, to the applied pressure gradient $\nabla P$: $q = (k/\mu)(-\nabla P)$, where $\mu$ is the viscosity of the fluid.
 In Darcy's law, the permeability is assumed to only depend on the material and its geometry.
